### 2019-04-05 Manuscript/Jin/Project2.tex
Initial version

 \documentclass[12pt]{article}
\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage{float}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multirow}
%
%\newtheorem*{remark}{Remark}
\usepackage[round]{natbib}
\usepackage{algorithm}
%\usepackage{setspace}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{bm}
\usepackage[pdftex,hypertexnames=false,linktocpage=true]{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,anchorcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue,bookmarksnumbered=true,pdfview=FitB}
\providecommand{\keywords}[1]{\textbf{\textit{Key words:}} #1}

\def\T{{ \mathrm{\scriptscriptstyle T} }}
\def\v{{\varepsilon}}

\def\pr{{\rm pr}}
\def\E{{\rm E}}
\def\V{{\rm Var}}

\def\0{{\bf 0}}
\def\A{{\bf A}}
\def\ua{{\bf a}}
\def\uB{{\bf B}}
\def\ub{{\bf b}}
\def\C{{\bf C}}
\def\c{{\bf c}}
\def\uD{{\bf D}}
\def\ud{{\bf d}}
\def\ue{{\bf e}}
\def\uE{{\bf E}}
\def\f{{\bf f}}
\def\h{{\bf h}}
\def\g{{\bf g}}
\def\uI{{\bf I}}
\def\K{{\bf K}}
\def\um{{\bf m}}
\def\uM{{\bf M}}
\def\r{{\bf r}}
\def\t{{\bf t}}
\def\T{{\bf T}}
\def\bO{{\bf O}}
\def\bP{{\bf P}}
\def\uQ{{\bf Q}}
\def\U{{\bf U}}
\def\uv{{\bf v}}
\def\uV{{\bf V}}
\def\uS{{\bf S}}
\def\uu{{\bf u}}
\def\uW{{\bf W}}
\def\uH{{\bf H}}
\def\uX{{\bf X}}
\def\ux{{\bf x}}

\def\uY{{\bf Y}}
\def\uy{{\bf y}}
\def\Z{{\bf Z}}
\def\uz{{\bf z}}

\def\0{{\boldsymbol 0}}
\def\1{{\boldsymbol 1}}
\def\ubeta{{\boldsymbol \beta}}
\def\btau{{\boldsymbol \tau}}
\def\bg{{\boldsymbol \gamma}}
\def\ueta{{\boldsymbol \eta}}
\def\bpi{{\boldsymbol \pi}}
\def\uxi{{\boldsymbol \xi}}
\def\ueta{{\boldsymbol \eta}}
\def\utheta{{\boldsymbol \theta}}
\def\umu{{\boldsymbol \mu}}
\def\uepsilon{{\boldsymbol \epsilon}}
\def\bOmega{{\boldsymbol\Omega}}
\def\uSigma{{\boldsymbol \Sigma}}
\def\bLam{{\bf \Lambda}}
\def\T{{ \mathrm{\scriptscriptstyle T} }}
\def\ualpha{{\boldsymbol \alpha}}
\def\usigma{{\boldsymbol \sigma}}
\def\uphi{{\boldsymbol \phi}}
\def\uepsilon{{\boldsymbol \epsilon}}
\def\nbd{{\rm nbd}}
\def\diag{{\rm diag}}

\def\T{{ \mathrm{\scriptscriptstyle T} }}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newtheorem{assumption}{Assumption}

% newcommand used in the document

%opening
\title{\LARGE\bf Bayesian selection of best subsets in high-dimensional regression}
\author{ Shiqiang Jin\thanks{Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.} \and Gyuhyeong Goh\thanks{Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.} }

\begin{document}
\baselineskip .3in
\maketitle

\begin{abstract}
With large numbers of predictors, regression analysis has faced many challenges including model fitting and prediction. As a power tool for dimension reduction, high-dimensional variable selection has drawn increasing attention in recent years. In this paper, we develop a new Bayesian approach to best subset selection that quickly identifies the best subset from a high-dimensional set of candidates via a hybrid search algorithm of deterministic local search and stochastic global search. To reduce the computational cost of evaluating many candidate subsets needed for each iteration, we propose an efficient and fast computation strategy that enables us to calculate exact posterior probabilities of all neighbor models simultaneously. The proposed Bayesian method possesses model selection consistency in the high-dimensional setting in which the number of candidate predictors is allowed to grow faster than the sample size. Simulation study and real data analysis are performed to assess and validate the proposed method.
\end{abstract}

\keywords{Bayesian subset selection}

\section{Introduction}
Variable selection plays a key role in recent regression analysis. In many statistical applications, especially in genetics studies, researchers have faced the situation in which the number of candidate predictors is extremely large but the sample size is relatively small, often referred to as a high-dimensional regression problem. The most pressing challenge in high-dimensional regression is to identify relevant predictor variables from the huge pool of candidates. In an attempt to perform high-dimensional variable selection, a lot of effort has been put into the development of penalized likelihood methods (e.g., \citealt{tibshirani1996regression, fan2001variable, zou2005regularization, zhang2010nearly}). By adding a penalty function to the likelihood criterion, a penalized likelihood method produces sparse solutions that eliminate irrelevant predictors corresponding to the zero-estimated coefficients in the regression model.

In this paper, we are interested in selecting $k$ important predictors out of $p$ candidates, called the best subset selection problem \citep{hocking1967selection}. It is well known that the best subset selection involves non-convex optimization, which is computationally intractable in high-dimensional settings (i.e., when $p$ is large). Although some penalized likelihood approaches such as Lasso, elastic net, and MCP provide a convex surrogate for the non-convex optimization problem, their applicability to the best subset selection is still limited \citep{bertsimas2016best}. Recently, a Bayesian approach to best subset selection, called Bayesian subset regression (BSR), has been proposed by \citet{liang2013bayesian}. Using an adaptive Markov chain Monte Carlo (MCMC) algorithm, called the stochastic approximation Monte Carlo \citep{liang2007stochastic}, BSR finds the best subset by performing a global search over the entire model space. However, the global stochastic search with a large number of candidate predictors often raises computational challenges including heavy computation and slow convergence. To overcome this limitation, we introduce new Bayesian subset selection algorithms that quickly identify the best subset via hybrid algorithms of deterministic local search and stochastic global search. The main attractive feature of our proposed method is that evaluating all possible candidate models for the next update, which is the most expensive part of MCMC computation, is simultaneously accomplished.

%The rest of the paper is organized as follows. In Section \ref{sec:2}, we describe the model setup and assumptions. In Section \ref{sec:3}, we extend the proposed method to variable selection. \textcolor{red}{In section \ref{sec:4}, we prove our algorithm obtains local optimization analytically but tends to target global optimized solution in numerical way.} In Section \ref{sec:5}, by using a simulation study, our proposed method is compared with some commonly used variable selection approaches including LASSO, SCAD, MCP and EMVS. The simulation result clear shows many benefits of our method. In Section \ref{sec:6}, we perform real data analysis with gene expression data. Section \ref{sec:7} concludes our paper with some remarks. The rest of the paper is organized as follows. Section 2 describes some explicit calculations to obtain a closed-form of In Section 3, we introduce a new Bayesian variable selection procedure via the ICM algorithm and discuss its important features. In Section 4, we study the performance of the newly-developed Bayesian variable method on simulated high-dimensional data. Section 6 offers some concluding remarks.

%In this paper, we denote normal distribution and inverse gamma distribution by $\mathcal{N}$ and $\mathcal{IG}$.

\section{Basic setup}\label{sec:2}
Consider a multiple linear regression model,
\begin{eqnarray}\label{eq:1}
\uy = \uX\ubeta + \uepsilon,
\end{eqnarray}
where $\uy$ is the $n$-dimensional response vector, $\uX = (\ux_1,\ldots,\ux_p)$ is the $n\times p$ design matrix, $\ubeta = (\beta_1,\ldots,\beta_p)^{\T}$ is a $p$-dimensional coefficient vector, and $\uepsilon \sim\text{Normal}(\0_n, \sigma^2\uI_n)$. As we are interested in high-dimensional problems, we assume that $p>n$ and $\ubeta$ contains many zero elements, i.e., $\ubeta$ is a high-dimensional sparse vector. We further assume that the response and predictors are standardized so that the intercept is always excluded from our regression analysis. Here, our goal is to identify the most important $k$ predictors in \eqref{eq:1}. To this end, let $\bg=(\gamma_1,\ldots,\gamma_p)$ be a vector of binary variables such that $\gamma_j=1$ if the $j^{th}$ predictor, $\ux_j$, is active and $\gamma_j=0$ otherwise for $j=1,\ldots,p$. For a given $\bg$, we can reduce the model \eqref{eq:1} to
\begin{eqnarray*}
\uy = \uX_{\bg} \ubeta_{\bg} + \uepsilon,
\end{eqnarray*}
where $\uX_{\bg}$ and $\ubeta_{\bg}$ are a sub-matrix of $\uX$ and a sub-vector of $\ubeta$ corresponding to the non-zero elements of $\bg$, respectively. Given $\bg$, we assign conjugate priors for $\ubeta_{\bg}$ and $\sigma^2$ that are most commonly used in Bayesian linear regression,
\begin{eqnarray*}
	\ubeta_{\bg}|\sigma^2,\bg &\sim&\text{Normal}(0,\tau \sigma^2 \uI_{|\bg|} ),\\
	\sigma^2 &\sim& \text{Inverse-Gamma}(a_{\sigma}/2,b_{\sigma}/2),
\end{eqnarray*} 
where $\tau$, $a_{\sigma}$, and $b_{\sigma}$ denote hyperparameters and $|\bg|=\sum_{j=1}^p\gamma_j $ indicates the number of active predictors in the reduced model. To impose the constraint $|\bg|=k$, we define the prior distribution of $\bg$ by $\pi(\bg)\propto\mathbb{I}(|\bg|=k )$, where $\mathbb{I}(\cdot)$ is an indicator function. Let $m(\uy|\bg)$ be the marginal likelihood given $\bg$. Using the kernels of normal density and inverse gamma density, the marginal likelihood can be easily calculated as
\begin{eqnarray}
\nonumber m(\uy|\bg) &=&\int f(\uy|\ubeta_{\bg},\sigma^2)\pi(\ubeta_{\bg}|\sigma^2, \bg) \pi(\sigma^2) d\ubeta d\sigma^2\\
\label{eq:2}&\propto& \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
		\uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
	\uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } },
\end{eqnarray}
where $f(\uy|\ubeta_{\bg},\sigma^2)$ denotes the likelihood given $\bg$ and $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$. By Bayes' theorem, the posterior model probability of $\bg$ is proportional to $$\pi(\bg|\uy)\propto m(\uy|\bg) \pi(\bg) \propto  \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
		\uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
	\uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } } \mathbb{I}(|\bg|=k ):=Q(\bg).$$
Therefore, our Bayesian best subset selection can be achieved by maximizing $Q(\bg)$.
\section{Best subset selection with fixed-size}
In this section, we introduce new algorithms to reach at $\hat{\bg}=\arg\max_{\bg}\pi(\bg|\uy)$ for the fixed subset size, $k$. Let $\mathcal{N}_+(\bg)$ be the set of all larger neighbors of $\bg$ obtained by adding one new predictor variable to $\bg$. Similarly, let $\mathcal{N}_-(\bg)$ be the set of all smaller neighbors of $\bg$ obtained by deleting one variable from $\bg$. Suppose that $\tilde{\bg}$ represents the current best subset of size $k$. Our main idea is to update $\tilde{\bg}$ via the following two-step procedure until convergence:
\begin{itemize}
\item[] \textbf{Addition-step:} Using the marginal likelihood, \emph{evaluate all models} in $\mathcal{N}_+(\tilde{\bg})$ \emph{simultaneously} and then find the best subset of size $k+1$, $$\tilde{\ueta}=\arg\max_{\ueta  \in \mathcal{N}_+(\tilde{\bg} ) } m(\uy|\ueta).$$
\item[] \textbf{Deletion-step:} Using the marginal likelihood, \emph{evaluate all models} in $\mathcal{N}_-(\tilde{\ueta})$ \emph{simultaneously} and then update the best subset of size $k$ as
$$\tilde{\bg}= \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\ueta} ) } m(\uy|\bg).$$
\end{itemize}
The following theorem proves the convergence of the proposed algorithm.
\begin{theorem}\label{thm:1} The proposed algorithm monotonically increases the posterior probability, $\pi(\tilde{\bg}|\uy)$. In addition, the algorithm terminates in a finite number of iterations.
\end{theorem}
The proof is given in Appendix \ref{app:01}. The great merit of our approach is that evaluating all the candidates for each step can be done simultaneously. To explain this in more details, let $\mathcal{G}_0=\{i:\tilde{\gamma}_i=0\}$ be an index set of inactive predictors associated with $\tilde{\bg}$, where $\tilde{\gamma}_i$ is the $i^{th}$ element of $\tilde{\bg}$. For each $i\in \mathcal{G}_0$, define $\ueta_i=(\eta_{i1},\ldots,\eta_{ip})$ by replacing the $i^{th}$ element of $\tilde{\bg}$ with $1$, that is, $\eta_{ij}=1$ if $j=i$ and $\eta_{ij}=\tilde{\gamma}_j$ if $j\neq i$. For every $i\in \mathcal{G}_0$, using \eqref{eq:2}, it can be shown that
\begin{eqnarray}\label{eq:app:1}
 m(\uy|\ueta_i) \propto \left[\uy^{\T}\uH_{\tilde{\bg}}\uy-\frac{(
 	\ux_i^{\T}\uH_{\tilde{\bg}}\uy)^2}{\tau^{-1}+\ux_i^{\T}\uH_{\tilde{\bg}} \ux_i }+b_{\sigma}\right]^
 {-\frac{a_{\sigma}+n}{2}}(\tau^{-1}+\ux_i^{\T}\uH_{\tilde{\bg}} \ux_i)^{-1/2},
\end{eqnarray}
where $\ux_i$ is the $i^{th}$ column of $\uX$. The details of our calculation in \eqref{eq:app:1} are shown by Appendix \ref{app:1}. It is important to note that $\ux_i^{\T}\uH_{\tilde{\bg}}\ux_i$ is the $i^{th}$ diagonal element of $\uX^{\T}\uH_{\tilde{\bg}}\uX$ and that $\ux_i^{\T}\uH_{\tilde{\bg}}\uy$ is the $i^{th}$ element of $\uX^{\T}\uH_{\tilde{\bg}}\uy$. Let $s_{\tilde{\bg}}=\uy^{\T}\uH_{\tilde{\bg}}\uy$, $\ud_{\tilde{\bg}}=\diag(\uX^{\T}\uH_{\tilde{\bg}}\uX)$, and $\uv_{\tilde{\bg}}=\uX^{\T}\uH_{\tilde{\bg}}\uy$. Define
$$\um^+_{\tilde{\bg}}= \left[(s_{\tilde{\bg}}+b_{\sigma}) \1_p-\frac{\uv_{\tilde{\bg}}^2}{\tau^{-1}\1_p+\ud_{\tilde{\bg}} } \right]^
 {-\frac{a_{\sigma}+n}{2}}(\tau^{-1} \1_p  +\ud_{\tilde{\bg}} )^{-1/2},$$
 where $\ua^x=(a_1^x,\ldots, a_p^x)$ and $\ua/\ub=(a_1/b_1,\ldots,a_p/b_p)$ for generic vectors $\ua$ and $\ub$. Note that $\mathcal{N}_+(\tilde{\bg})=\{\ueta_i:i\in \mathcal{G}_0\}$. Hence, in the addition-step, evaluating all the models in $\mathcal{N}_+(\tilde{\bg})$ (i.e.,  calculating all the marginal likelihoods) can be done at once by extracting the sub-vector corresponding to $\mathcal{G}_0$ from $\um^+_{\tilde{\bg}}$. Similarly, let $\mathcal{E}_1=\{\ell:\tilde{\eta}_\ell=1\}$ be an index set of active predictors associated with $\tilde{\ueta}$, where $\tilde{\eta}_\ell$ denotes the $\ell^{th}$ element of $\tilde{\ueta}$. For each $\ell \in\mathcal{E}_1$, we define $\bg_\ell$ by replacing the $\ell^{th}$ element of $\tilde{\ueta}$ with $0$. We can show that 
 \begin{eqnarray}\label{eq:app:2}
 m(\uy|\bg_\ell)  \propto \left[\uy^{\T}\uH_{\tilde{\ueta}}\uy+\frac{(
 	\ux_\ell^{\T}\uH_{\tilde{\ueta}}\uy)^2}{\tau^{-1}-\ux_\ell^{\T}\uH_{\tilde{\ueta}} \ux_\ell }+b_{\sigma}\right]^
 {-\frac{a_{\sigma}+n}{2}}(\tau^{-1}-\ux_\ell^{\T}\uH_{\tilde{\ueta}} \ux_\ell)^{-1/2}.
\end{eqnarray} Some details of our calculation for \eqref{eq:app:2} are shown in Appendix \ref{app:2}. Define
$$\um^-_{\tilde{\ueta}}= \left[(s_{\tilde{\ueta}}+b_{\sigma}) \1_p+\frac{\uv_{\tilde{\ueta}}^2}{\tau^{-1}\1_p-\ud_{\tilde{\ueta}} } \right]^
 {-\frac{a_{\sigma}+n}{2}}(\tau^{-1} \1_p  -\ud_{\tilde{\ueta}} )^{-1/2}.$$
Note that $\mathcal{N}_-(\tilde{\ueta})=\{\bg_\ell:\ell\in \mathcal{E}_1\}$. Hence, as in the addition-step,  evaluating all the candidates in the deletion-step can be done at once by extracting the sub-vector corresponding to $\mathcal{E}_1$ from $\um^-_{\tilde{\ueta}}$.

In general, hyperparameter $\tau$ can be chosen to be a large value so that the Gaussian prior for $\ubeta_{\bg}$ becomes approximately non-informative (or flat). However, when predictors are strongly correlated (i.e., when multicollinearity occurs), hyperparameter optimization for $\tau$ plays a crucial role to improve the prediction accuracy \citep{hoerl1970ridge}. Since multicollinearly is common in high-dimensional settings, we propose to estimate the optimal value of $\tau$ using an empirical Bayesian approach. Note that, given $\bg$, the marginal likelihood in \eqref{eq:2} can be considered as a function of $\tau$. Taking the negative logarithm of the right hand side of $\eqref{eq:2}$ and applying Lemma \ref{lem:1} in Appendix \ref{app:3}, we define
\begin{eqnarray}
	\nonumber Q(\tau|\bg) 
	&=&\frac{|\bg|}{2}\log\tau+ \frac{1}{2}\sum_{j=1}^{p}\log  (\lambda_{\bg j} +\tau^{-1})\\
	\label{gtau} && + {\frac{a_{\sigma}+n}{2}}\log\left\{\uy^{\T}\uy 
	-\sum_{j=1}^p \frac{\lambda_{\bg j} (\uu_{\bg j}^\T \uy)^2}{\lambda_{\bg j}+\tau^{-1} }+b_{\sigma} \right\},
\end{eqnarray}
where $\lambda_{\bg j}$ is the $j^{th}$ largest eigenvalue of $\uX_\bg^\T \uX_\bg$ and $\uu_{\bg j}$ is the eigenvector of $\uX_\bg^\T \uX_\bg$ corresponding to $\lambda_{\bg j}$. Then, for given $\tilde{\bg}$, we estimate the optimal value of $\tau$, say $\tilde{\tau}$, by minimizing $Q(\tau|\tilde{\bg})$. Note that $\tilde{\tau}$ can be easily and quickly obtained by using a simple numerical optimization method such as the Newton-Raphson method. We now introduce our Bayesian best subset algorithm as follows:
\begin{algorithm}[ht]
\caption{Deterministic best subset search with a fixed $k$}\label{alg:1}
\begin{itemize}
\item[1.] Initialize $\tilde{\bg}$ and $\tilde{\tau}$.
\item[2.] \textbf{Repeat}
\begin{itemize}
\item[] Update $\tilde{\ueta}\leftarrow \arg\max_{\ueta  \in \mathcal{N}_+(\tilde{\bg} ) } m(\uy|\ueta,\tilde{\tau})$; 
\item[] Update $\tilde{\bg}\leftarrow  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\ueta} ) } m(\uy|\bg,\tilde{\tau})$;
\item[] Update $\tilde{\tau} \leftarrow \arg\min_{\tau \in (0,\infty)}Q(\tau|\tilde{\bg})$;
\end{itemize}
\item[] \textbf{until} convergence.
\item[3.] Return $\hat{\bg}=\tilde{\bg}$.
\end{itemize}
\end{algorithm}

A possible drawback of our deterministic search is that the proposed algorithm can get trapped in a local optimum. To resolve this issue, we propose to add a stochastic global search algorithm to the proposed deterministic local search algorithm. This additional step will be used only to check whether or not the local search algorithm reaches the global optimum. To develop a fast global search algorithm, we employ a notion of the shotgun stochastic search \citep{hans2007shotgun}. However, while the shotgun stochastic search evaluates the candidate models using parallel computing, our simultaneous evaluation is based on analytical calculations. Our stochastic search algorithm can be implemented by generating a Markov chain via the following iterative sampling scheme:
\begin{itemize}
\item[1.] Given $\bg^*$, generate $\ueta^*$ with probability,
$$\pi(\ueta|\uy,\bg^*)=\frac{m(\uy|\ueta)}{\sum_{\ueta \in \mathcal{N}_+(\bg^* )  } m(\uy|\ueta) }\mathbb{I}\{\ueta \in \mathcal{N}_+(\bg^* ) \}.$$
\item[2.] Given $\ueta^*$, generate $\bg^*$ with probability
$$\pi(\bg|\uy,\ueta^*)=\frac{m(\uy|\bg)}{\sum_{\bg \in \mathcal{N}_-({\ueta}^* )  } m(\uy|\bg) }\mathbb{I}\{\bg \in \mathcal{N}_-({\ueta}^* )   \}.$$
\end{itemize}
Recall that  using $\eqref{eq:app:1}$ and  $\eqref{eq:app:2}$, calculating $\pi(\ueta|\uy,\bg^*)$ for all $\ueta \in \mathcal{N}_+(\bg^* )$ can be done simultaneously. Similarly, we can calculate $\pi(\bg|\uy,\ueta^*)$ for all $\bg \in \mathcal{N}_-({\ueta}^* ) $ at once.   
Using the notion of the Metropolis-Hasting algorithm, it is easy to check that the states of generated Markov chain by our sampling method is equivalent to the support of $\pi(\bg|\uy)$\textcolor{red}{(Revise it later)}. Let $\bg^{(t)}$ be the sample generated at iteration $t$. If the outcome from Algorithm \ref{alg:1}, $\hat{\bg}$, is not the global maximum, then we must observe at least one case that $\pi(\hat{\bg}|\uy)< \pi(\bg^{(t)}|\uy)$ (or equivalently $m(\uy|\hat{\bg})<m(\uy|\bg^{(t)})$) with probability one as $t\to \infty$. Therefore, if this case does not occur for sufficiently large $t$, we can treat $\hat{\bg}$ as the global maximum.

\begin{algorithm}[ht]
\caption{Hybrid best subset search with a fixed $k$}\label{alg:2}
\begin{itemize}
\item[1.] Initialize $\tilde{\bg}$ and $\tilde{\tau}$.
\item[2.] \textbf{Repeat}
\begin{itemize}
\item[] Update $\tilde{\ueta}\leftarrow \arg\max_{\ueta  \in \mathcal{N}_+(\tilde{\bg} ) } m(\uy|\ueta,\tilde{\tau});$ 
\item[] Update $\tilde{\bg}\leftarrow  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\ueta} ) } m(\uy|\bg,\tilde{\tau});$
\item[] Update $\tilde{\tau} \leftarrow \arg\min_{\tau \in (0,\infty)}Q(\tau|\tilde{\bg})$;
\end{itemize}
\item[] \textbf{until} convergence.
\item[3.] Set $\bg^{(0)}=\tilde{\bg}$.
\item[4.] \textbf{Repeat} for $t=1,\ldots,T$:
\begin{itemize}
\item[] Generate $\ueta^{(t)}\sim \pi(\ueta|\uy,\bg^{(t-1)})$;
\item[] Generate $\bg^{(t)}\sim \pi(\bg|\uy,\ueta^{(t)})$;
\item[] \textbf{If} $m(\uy|\tilde{\bg})<m(\uy|\bg^{(t)})$, \textbf{then} set $\tilde{\bg}=\bg^{(t)}$, break the loop, and go to 2.
\end{itemize}
\item[5.] Return $\hat{\bg}=\tilde{\bg}$.
\end{itemize}
\end{algorithm}

\section{Best subset selection with bounded size}\label{sec:3}
In this section, we extend the proposed method to best subset selection with varying $k (\leq K)$ for a prespecified upper bound $K$, which is a common setting for high-dimensional best subset selection (e.g., \citealt{bertsimas2016best, liang2013bayesian}). In our Bayesian framework, this extension can be easily done by assigning an appropriate prior for unknown $k$. As a non-informative prior, one may consider a discrete uniform prior for $k$, that is, $k \sim \text{Uniform}\{1,\ldots,K\}$. However, the uniform prior tends to assign larger probability to a larger subset due to the fact that the total number of subsets is $\binom{p}{k}$ for $k$. To remove this issue, using  a similar idea of \citet{chen2008extended}, we define 
$$\pi(k)\propto 1/\binom{p}{k} \mathbb{I}(k\leq K).$$
Let $\bg_{k}=(\gamma_{k1},\ldots,\gamma_{kp})$ indicate a subset of size $k$. Then, our best subset selection can be performed by maximizing  
\begin{eqnarray*}
\pi(\bg_k|\uy)\propto  m(\uy|\bg_k)/\binom{p}{k},
\end{eqnarray*}
subject to $k\leq K$. Hence, our best subset search algorithms with varying $k$ can be summarized as follows:
\begin{algorithm}[ht]
\caption{Best subset search with varying $k$}\label{alg:3}
\begin{itemize}
\item[1.] \textbf{Repeat} for $k=1,\ldots,K$:
\begin{itemize}
\item[a.] Initialize $\tilde{\bg}$ and $\tilde{\tau}$.
\item[b.] Implement step 2 of Algorithm \ref{alg:1} for deterministic search.
\item[] (or Implement steps 2 -- 4 of Algorithm \ref{alg:2} for hybrid search.)
\item[c.] Set $\hat{\bg}_k=\tilde{\bg}$.
\end{itemize}
\item[2.] Return $\hat{\bg}=\hat{\bg}_{\hat{k}}$, where \begin{eqnarray}\label{eq:post}  \hat{k}=\arg\max_{1\leq k\leq K} \left\{\log m(\uy|\hat{\bg}_k)-\log \binom{p}{k}\right\}.
\end{eqnarray}
\end{itemize}
\end{algorithm}

From \citet{kass1995}, for sufficiently large $n$, we have 
$$  \log m(\uy|\bg_{k_1}) -\log m(\uy|\bg_{k_2})  \approx \hat{l}(\uy|\bg_{k_1})-\hat{l}(\uy|\bg_{k_2})- \frac{1}{2}(k_1-k_2) \log(n),$$
where $\hat{l}(\uy|\bg)$ denotes the log-likelihood evaluated at the maximum likelihood estimates given $\bg$. This implies that our posterior criterion in \eqref{eq:post} is asymptotically equivalent to the following extended BIC,
\begin{eqnarray}\label{ebic}
\text{EBIC}(\bg_{k})=-2 \hat{l}(\uy|\bg_{k})+k\log(n)+2\log \binom{p}{k}.
\end{eqnarray}
Consequently, by Theorem 1 of \citet{chen2008extended}, our method possesses the model selection consistency in the high-dimensional setting with $p=O(n^\xi)$ for $\xi\geq 1$. 
\section{Simulation study}
In this section, we investigate the variable selection performance of our best subset selection algorithm on simulated high-dimensional data. For given $n=100$, we generate the data $\{(y_i,x_{i1},\ldots,x_{ip}):i=1,\ldots,n\}$ from the following linear regression model:
$$y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},1\right),$$
where $(x_{i1},\ldots,x_{ip})^\T \overset{iid}{\sim}\text{Normal}(\0_p,\uSigma)$ with $\uSigma=(\Sigma_{ij})_{p\times p}$ and $\Sigma_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining coefficients are set equal to $0$.

We consider four different scenarios: (i) $p=200$, $\rho=0.1$, (ii) $p=200$, $\rho=0.9$, (iii) $p=1000$, $\rho=0.1$, and (iv) $p=1000$, $\rho=0.9$. We assume that there is no prior information. Hence, to make our prior distribution non-informative, we define the hyperparameters of inverse gamma prior as $a_\sigma=b_\sigma=1$. Recall that we have proposed four algorithms: 1) deterministic search with fixed subset size, called DS$_k$, 2) deterministic search with bounded subset size, called DS$_{\leq K}$, 3) hybrid search with fixed subset size, called HS$_{k}$, 4) hybrid search with bounded subset size, called HS$_{\leq K}$. In DS$_{\leq K}$ and HS$_{\leq K}$, we define the upper bound of subset size by $K=\lceil n^{2/3} \rceil =22$. In DS$_k$ and HS$_k$, we define $k=4$, which is the true number of active predictors in the data generating model. For the hybrid search algorithms (HS$_{k}$ and HS$_{\leq K}$), the stochastic search iteration size, $T$, is set to $T=100$. \textcolor{red}{We use the marginal correlation between the response and each predictor to define the initial values.} All simulation
studies are implemented in the R statistical software with computer( Intel Core i7-7700, 32GB, Window 10 Enterprise)

For comparison purposes, we also apply the most popular penalized likelihood methods, LASSO \citep{tibshirani1996regression}, the elastic net \citep{zou2005regularization}, SCAD \citep{fan2001variable}, and MCP \citep{zhang2010nearly}, to the simulated data, where the regularization parameters (i.e., tuning parameters) are determined by the extended BIC in \eqref{ebic}. To evaluate the variable selection performance, we calculate false discovery rate (FDR), percentage of selecting the exact true model (TRUE\%), size of the selected model (SIZE), and Hamming distance (HAM) based on $2,000$ replications.

\begin{table}[H]
  \centering
  \caption{Simulation study results based on $2,000$ replications; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance), and s.e. (standard error).}\label{T:sim1}
  \begin{tabular}{cc|c|c|c|c}
    \hline
    Scenario&Method&FDR  (s.e.) & TRUE\% (s.e.) & SIZE (s.e.) & HAM (s.e.)  \\
    \hline
i&Proposed & 0.016 (0.001) & 92.600 (0.585)& 4.087 (0.007) & 0.087 (0.007) \\ 
    &SCAD & 0.034 (0.002) &  85.200 (0.794) & 4.188 (0.011) & 0.188 (0.011)\\ 
   &MCP & 0.035 (0.002) & 84.750 (0.804) & 4.191 (0.011) & 0.191 (0.011)\\ 
  &ENET & 0.016 (0.001) & 92.700 (0.582) & 4.087 (0.007) & 0.087 (0.007)\\ 
  &LASSO & 0.020 (0.002) & 91.350 (0.629) & 4.109 (0.009) & 0.109 (0.009)\\
    \hline
    ii&Proposed & 0.030 (0.002) & 86.250 (0.770) & 4.034 (0.007) & 0.236 (0.014)   \\
&SCAD & 0.059 (0.003) & 74.150 (0.979) & 4.107 (0.015) & 0.480 (0.022) \\ 
  &MCP & 0.137 (0.004) & 55.400 (1.112) & 4.264 (0.020) & 1.098 (0.034) \\ 
  &ENET & 0.501 (0.004) & 0.300 (0.122) & 7.716 (0.072) & 5.018 (0.052) \\ 
  &LASSO & 0.276 (0.004) & 15.550 (0.811) & 5.308 (0.033) & 2.038 (0.034) \\ 
    \hline
    iii&Proposed&0.014 (0.001) & 93.450 (0.553) & 4.073 (0.007) & 0.073 (0.007)\\
&SCAD & 0.027 (0.002) & 87.900 (0.729) & 4.145 (0.010) & 0.145 (0.010) \\ 
  &MCP & 0.031 (0.002) & 86.550 (0.763) & 4.172 (0.013) & 0.172 (0.013) \\ 
  &ENET & 0.035 (0.002) & 84.850 (0.802) & 4.181 (0.013) & 0.206 (0.012) \\ 
  &LASSO & 0.014 (0.001) & 93.850 (0.537) & 4.073 (0.007) & 0.073 (0.007) \\ 
    \hline
    iv&Proposed&0.032 (0.002) & 86.700 (0.759) & 4.051 (0.007) & 0.236 (0.015) \\
&SCAD & 0.068 (0.003) & 74.250 (0.978) & 4.196 (0.014) & 0.493 (0.023) \\ 
  &MCP & 0.152 (0.004) & 53.750 (1.115) & 4.226 (0.017) & 1.202 (0.035) \\ 
  &ENET & 0.417 (0.005) & 0.150 (0.087) & 6.228 (0.068) & 4.089 (0.043) \\ 
  &LASSO & 0.265 (0.004) & 19.500 (0.886) & 5.139 (0.029) & 1.909 (0.035) \\ 
    \hline
  \end{tabular}
\end{table}

\section{Real data application}
 In this section, we apply our proposed methods to breast cancer tissue samples from The Cancer Genome Atlas (TCGA) Research Network: \url{http://cancergenome.nih.gov}. The dataset "Breast Invasive Carcinoma" (BRCA) we use in this paper is extracted from the R package "curatedTCGAData" and is publicly available and described at \url{http://bioconductor.org/packages/release/data/experiment/html/curatedTCGAData.html}, where includes many other Bioconductor MultiAssayExperiment class objects. The data set contains $17814$ gene expression measurements originally. After removing missing data, it is left $526$ patients with $17,323$ gene expression measurements (recorded on the log scale).  BRCA1 is a tumor suppressor gene and its mutations predispose women to breast cancer \citep{findlay2018accurate}. Our goal here is to identify the best fitting model for estimating an association between BRCA1 (response variable) and the other genes (independent variables). We standardize all the variables.

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & NSP & MSE\_Pred & MSE\_fit & BIC & EBIC & Detection Rate\\ 
  \hline
  Local & 31.00 & 0.48 & 0.40 & 738.91 & 1048.20 & 2/11\\ 
  Grobal & 50.00 & 0.39 & 0.30 & 548.03 & 1015.81 & 1/11\\ 
  SCAD & 4.00 & 0.69 & 0.67 & 1104.69 & 1154.11 & 1/11\\ 
  MCP & 4.00 & 0.69 & 0.67 & 1104.69 & 1154.11 & 1/11\\ 
  ENET & 5.00 & 0.69 & 0.67 & 1110.65 & 1171.30 & 1/11\\ 
  LASSO & 4.00 & 0.69 & 0.67 & 1104.69 & 1154.11 & 1/11\\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}
  \includegraphics[width=\linewidth]{Heatmap.pdf}
  \caption{Heap map}
  \label{fig:heatmap}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{Log_marginal.pdf}
  \caption{Logmarginal}
  \label{fig:Logmarginal}
\end{figure}

\newpage
\appendix
\section{Proof}\label{app:01}
\begin{proof}[Proof of Theorem \ref{thm:1}] Let $\tilde{\bg}^{(i)}$ be the best subset of size $k$ updated by the $i^{th}$ iteration. Then,
$$\tilde{\ueta}^{(i)}=\arg\max_{\ueta  \in \mathcal{N}_+(\tilde{\bg}^{(i)}  ) } m(\uy|\bg)\quad \text{and}\quad \tilde{\bg}^{(i+1)} = \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\ueta}^{(i)} ) } m(\uy|\bg).$$
Due to the fact that $\tilde{\bg}^{(i)} \in \mathcal{N}_-(\tilde{\ueta}^{(i)} ) $, we have
$$m(\uy|\tilde{\bg}^{(i)} ) \leq m(\uy|\tilde{\bg}^{(i+1)}).$$
From Bayes' theorem, this implies 
$$\pi(\tilde{\bg}^{(i)}|\uy ) \leq \pi(\tilde{\bg}^{(i+1)}|\uy),$$
which proves our first statement.
Since the number of all possible $\bg$ satisfying $|\bg|=k $ is finite, the algorithm terminates in a finite number of iterations and this completes our proof.
\end{proof}
\section{Calculation of \eqref{eq:app:1}}\label{app:1}
\begin{eqnarray}
\pi(\bg^{+i}|\uy,\bg)&\propto& \frac{(\tau^{-1})^{(k+1)/2}}{|\uX_{\bg^{+i}}^{\T}\uX_{\bg^{+i}}+\tau^{-1}I_{k+1} |^{1/2} } \left(\uy^{\T}\uH_{\bg^{+i}}\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2} } \mathbb{I}\left\{|\bg^{+i}|=k+1 \right\}\nonumber\\
&\propto&|\uX_{\bg^{+i}}^{\T}\uX_{\bg^{+i}}+\tau^{-1}I_{k+1} |^{-1/2}\left(\uy^{\T}(\uH_\bg-\frac{\uH_\bg \ux_i \ux_i
  ^{\T}\uH_\bg } {\tau^{-1}+\ux_i^{\T}\uH_\bg \ux_i })\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2}}\nonumber\\
&=&| \uX_\bg^{\T}\uX_\bg+\tau^{-1}\uI_{k}|^{-1/2} \left(\tau^{-1}+\ux_i^{\T}\uH_\bg \ux_i\right)^{-1/2}\left(\uy^{\T}(\uH_\bg-\frac{\uH_\bg \ux_i \ux_i^{\T}\uH_\bg } {\tau^{-1}+\ux_i^{\T}\uH_\bg \ux_i })\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2}}\nonumber\\
&\propto& \left[\uy^{\T}\uH_{\bg}\uy-\frac{(
 	\ux_i^{\T}\uH_{\bg}\uy)^2}{\tau^{-1}+\ux_i^{\T}\uH_{\bg} \ux_i }+b_{\sigma}\right]^
 {-\frac{a_{\sigma}+n}{2}}(\tau^{-1}+\ux_i^{\T}\uH_{\bg} \ux_i)^{-1/2}
\end{eqnarray}
The second proportion holds by Lemma 1 in \ref{lm:1} and the equation holds by Lemma 4.1 in \ref{lm:4.1}
\section{Calculation of \eqref{eq:app:2}}\label{app:2}

The details are shown in Appendix \ref{app:2}.
\begin{eqnarray}
&&\pi(\bg^{*-\ell}|\uy,\bg^*) \nonumber \\
&\propto&\frac{(\tau^{-1})^{k/2}}{|\uX_{\bg^{*-\ell}}^{\T}\uX_{\bg^{*-\ell}}+\tau^{-1}I_{k} |^{1/2} } \left(\uy^{\T}\uH_{\bg^{*-\ell}}\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2} } \mathbb{I}\left\{|\bg^{*-\ell}|=k \right\}\nonumber\\
&\propto& |\uX_{\bg^{*-\ell}}^{\T}\uX_{\bg^{*-\ell}}+\tau^{-1}I_{k}|^{-1/2}\left(\uy^{\T}(\uH_{\bg^*}+\frac{\uH_{\bg^*} \ux_{\ell} \ux_{\ell}^{\T}\uH_{\bg^*} } {\tau^{-1}-\ux_{\ell}^{\T}\uH_{\bg^*} \ux_{\ell} })\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2}} \nonumber \\
&=& |\uX_{\bg^*}^{\T}\uX_{\bg^*}+\tau^{-1}\uI_{k+1}|^{-1/2} (\tau^{-1}-\ux_\ell^{\T}\uH_{\bg^*} \ux_\ell)^{-1/2}\left[\uy^{\T}\uH_{\bg^*}\uy+\frac{(\ux_\ell^{\T}\uH_{\bg^*}\uy)^2}{\tau^{-1}-\ux_\ell^{\T}\uH_{\bg^*} \ux_\ell }+b_{\sigma}\right]^{-\frac{a_{\sigma}+n}{2}} \nonumber \\
&\propto& \left[\uy^{\T}\uH_{\bg^*}\uy+\frac{(\ux_\ell^{\T}\uH_{\bg^*}\uy)^2}{\tau^{-1}-\ux_\ell^{\T}\uH_{\bg^*} \ux_\ell }+b_{\sigma}\right]^
  {-\frac{a_{\sigma}+n}{2}}(\tau^{-1}-\ux_\ell^{\T}\uH_{\bg^*} \ux_\ell)^{-1/2},
\end{eqnarray}
\section{Lemmas}\label{app:3}
\begin{lemma}\label{lem:1}
Let $\uX=UDV^{\T}$. We have
\begin{eqnarray}\label{lm:5.1}
	|\uX^{\T}\uX+\tau^{-1}\uI_p|
	&=&|VD^{\T}U^{\T}UDV^{\T}+\tau^{-1}VV^{\T}|\nonumber\\
	&=&|VD^{\T}DV^{\T}+V\tau^{-1}\uI_pV^{\T}|\nonumber\\
	&=&|V(D^{\T}D+\tau^{-1}\uI_p)V^{\T}|\nonumber\\
	&=&|V||D^{\T}D+\tau^{-1}\uI_p||V^{\T}|\nonumber\\
	&=&|VV^{\T}||D^{\T}D+\tau^{-1}\uI_p|\nonumber\\
	&=&|D^{\T}D+\tau^{-1}\uI_p|\nonumber\\
	&=&\prod_{j=1}^{p}(d_j^2+\tau^{-1})
\end{eqnarray}
where $d_j$ is $j^{th}$ diagonal element of $D$. Also, we have
\begin{eqnarray}\label{lm:5.2}
	&&\uy^{\T}\uX(\uX^{\T}\uX+\tau^{-1}\uI_p)^{-1}\uX^{\T}\uy\nonumber\\
	&=& \uy^{\T}UDV^{\T}(VD^{\T}U^{\T}UDV^{\T}+V\tau^{-1}\uI_pV^{\T})^{-1}
	VD^{\T}U^{\T}\uy \nonumber\\
	&=& \uy^{\T}UDV^{\T}(V(D^{\T}D+\tau^{-1}\uI_p)V^{\T})^{-1}
	VD^{\T}U^{\T}\uy \nonumber\\
	&=& \uy^{\T}UD(D^{\T}D+\tau^{-1}\uI_p)^{-1}D^{\T}U^{\T}\uy \nonumber\\
	&=& \uy^{\T}UD(\diag(d_j^2+\tau^{-1}))^{-1}D^{\T}U^{\T}\uy \nonumber\\
	&=& \uy^{\T}U\diag\left(\frac{d_j^2}{d_j^2+\tau^{-1}}\right)U^{\T}\uy \nonumber\\
	&=& \sum_{j}\frac{d_j^2z_j^2}{d_j^2+\tau^{-1} }
	\end{eqnarray}
where $z_j$ is the $j^{th}$ component of $U^{\T}\uy$.
\end{lemma}

\bibliographystyle{chicago}
\bibliography{ref}
\end{document}

### 2019-04-05 Rcode/BRCA_analysis.R

@@ -1,0 +1,572 @@
+library(MASS)
+library(invgamma)
+library(mvtnorm)
+library(xtable)
+library(ggplot2)
+library(reshape2)
+library(glmnet)
+library(ncvreg)
+rm(list=ls())
+###################
+# Data processing #
+###################
+load('~/Dropbox/Goh/BRCA.RData')
+#load('~/BRCA.RData')
+## data processing
+BRCA.stu <- scale(BRCA,center = TRUE, scale = TRUE)
+name.genes <- colnames(BRCA)
+ham.genes <- c('BRCA2','NBR1','NBR2','XRCC2',
+               'ATM','CHEK2','BRIP1','PALB2','RAD51C',
+               'CDH1','TP53')
+BRCA1 <- which(name.genes=='BRCA1')
+y1 <- BRCA.stu[,BRCA1]
+X1 <- BRCA.stu[,-BRCA1]
+name.genes <- name.genes[-BRCA1] # update symbols of genes. 
+ham.vars <- name.genes%in%ham.genes
+lm.ham.gene <- lm(y1~X1[,ham.vars]-1)
+p = dim(X1)[2]
+n = length(y1)
+rep0 <- rep(0,p)
+ksi <- 1.01-0.5*log(n)/log(p)
+set.seed(1314)
+g.tau <- function(tau0) {
+  SVD <- svd(X.r.star)
+  d.j <- as.vector(SVD$d)
+  z.j <- as.vector(t(SVD$u)%*%y1)
+  log.g.tau <- dim(X.r.star)[2]/2*log(tau0) + 0.5*sum(log(1/tau0+d.j^2)) + 
+    0.5*(a.sigma+n)*log(sum(y1^2)- sum((d.j*z.j)^2/(d.j^2+1/tau0))+b.sigma)
+  return(log.g.tau)
+}
+G1.BRO <- list()
+G1.hy <- list()
+k0 <- ceiling(n^(2/3))
+a.sigma = b.sigma = 1
+var.name <- colnames(X1)
+I_n=diag(1,n)
+marginal <- rep(NA,k0)
+G1 <- list()
+##################
+#1. Hybrid #####
+##################
+#Step 1: Set initial values
+beta.ini <- cor(X1,y1)
+marginal.BRO <- rep(NA,k0)
+marginal.hy <- rep(NA,k0)
+G1.hy <- list()
[…]

### 2019-04-05 Rcode/Goh/Bayesian methods_sim1.R

@@ -1,0 +1,84 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+#install.packages("mvtnorm")
+#install.packages("xtable")
+#install.packages("invgamma")
+#install.packages("BayesVarSel")
+library(BayesVarSel)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-200
+rho0 <- 0.1
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+
+Sim.data<-data.frame(y=y1,X=X1)
+Sim.data[1:2,]
+t1 = Sys.time()
+SSVS.sim<-GibbsBvs(formula= y ~ ., data=Sim.data, n.iter=1000, init.model=rep(0,p), n.burnin=100,
+time.test = FALSE)
+t2[i] <- round(difftime(Sys.time(),t1,units = 'secs'), 3)
+result.SSVS<-as.numeric((summary(SSVS.sim)$summary[[3]])=="*")
+  G.1.hy <-which(result.SSVS==1)
[…]

### 2019-04-05 Rcode/Goh/Bayesian methods_sim2.R

@@ -1,0 +1,84 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+#install.packages("mvtnorm")
+#install.packages("xtable")
+#install.packages("invgamma")
+#install.packages("BayesVarSel")
+library(BayesVarSel)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-200
+rho0 <- 0.9
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+
+Sim.data<-data.frame(y=y1,X=X1)
+Sim.data[1:2,]
+t1 = Sys.time()
+SSVS.sim<-GibbsBvs(formula= y ~ ., data=Sim.data, n.iter=1000, init.model=rep(0,p), n.burnin=100,
+time.test = FALSE)
+t2[i] <- round(difftime(Sys.time(),t1,units = 'secs'), 3)
+result.SSVS<-as.numeric((summary(SSVS.sim)$summary[[3]])=="*")
+  G.1.hy <-which(result.SSVS==1)
[…]

### 2019-04-05 Rcode/Goh/Bayesian methods_sim3.R

@@ -1,0 +1,84 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+#install.packages("mvtnorm")
+#install.packages("xtable")
+#install.packages("invgamma")
+#install.packages("BayesVarSel")
+library(BayesVarSel)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-1000
+rho0 <- 0.1
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+
+Sim.data<-data.frame(y=y1,X=X1)
+Sim.data[1:2,]
+t1 = Sys.time()
+SSVS.sim<-GibbsBvs(formula= y ~ ., data=Sim.data, n.iter=1000, init.model=rep(0,p), n.burnin=100,
+time.test = FALSE)
+t2[i] <- round(difftime(Sys.time(),t1,units = 'secs'), 3)
+result.SSVS<-as.numeric((summary(SSVS.sim)$summary[[3]])=="*")
+  G.1.hy <-which(result.SSVS==1)
[…]

### 2019-04-05 Rcode/Goh/Bayesian methods_sim4.R

@@ -1,0 +1,84 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+#install.packages("mvtnorm")
+#install.packages("xtable")
+#install.packages("invgamma")
+#install.packages("BayesVarSel")
+library(BayesVarSel)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-1000
+rho0 <- 0.9
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+
+Sim.data<-data.frame(y=y1,X=X1)
+Sim.data[1:2,]
+t1 = Sys.time()
+SSVS.sim<-GibbsBvs(formula= y ~ ., data=Sim.data, n.iter=1000, init.model=rep(0,p), n.burnin=100,
+time.test = FALSE)
+t2[i] <- round(difftime(Sys.time(),t1,units = 'secs'), 3)
+result.SSVS<-as.numeric((summary(SSVS.sim)$summary[[3]])=="*")
+  G.1.hy <-which(result.SSVS==1)
[…]

### 2019-04-05 Rcode/Goh/Penalized methods.R

@@ -1,0 +1,184 @@
+library(mvtnorm)
+library(MASS)
+library(glmnet)
+library(ncvreg)
+library(ggplot2)
+library(latex2exp)
+library(xtable)
+if (!require(matrixStats)) install.packages('matrixStats')
+library(matrixStats)
+rm(list=ls())
+REP <- 2000
+p<-200
+n<-100
+K.upper<-ceiling(n^(2/3))
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+gamma.true <- rep0
+Sig2<-1
+RHO <- c(0.1)
+hat.gamma.SCAD <- matrix(0,p,REP)
+hat.gamma.MCP <- matrix(0,p,REP)
+hat.gamma.ENET <- matrix(0,p,REP)
+hat.gamma.LASSO <- matrix(0,p,REP)
+for (rho0 in RHO) {
+  FDR.LASSO <- rep(NA,REP)
+  FOR.LASSO <- rep(NA,REP)
+  t2.LASSO  <- rep(NA,REP)
+  n.var.LASSO  <- rep(0,REP)
+  n.true.LASSO  <- rep(0,REP)
+  ham.LASSO  <- rep(0,REP)
+  
+  FDR.SCAD <- rep(NA,REP)
+  FOR.SCAD <- rep(NA,REP)
+  t2.SCAD  <- rep(NA,REP)
+  n.var.SCAD  <- rep(0,REP)
+  n.true.SCAD  <- rep(0,REP)
+  ham.SCAD  <- rep(0,REP)
+  
+  FDR.MCP <- rep(NA,REP)
+  FOR.MCP <- rep(NA,REP)
+  t2.MCP  <- rep(NA,REP)
+  n.var.MCP  <- rep(0,REP)
+  n.true.MCP  <- rep(0,REP)
+  ham.MCP  <- rep(0,REP)
+  
+  FDR.ENET <- rep(NA,REP)
+  FOR.ENET <- rep(NA,REP)
+  t2.ENET  <- rep(NA,REP)
+  n.var.ENET  <- rep(0,REP)
+  n.true.ENET  <- rep(0,REP)
+  ham.ENET  <- rep(0,REP)
+  Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p)))) # AR
+  for (k in 1:REP) {
+    set.seed(1314+k)
+    beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
[…]

### 2019-04-05 Rcode/Goh/Penalized methods_revised_v1.R

@@ -1,0 +1,197 @@
+library(mvtnorm)
+library(MASS)
+library(glmnet)
+library(ncvreg)
+library(ggplot2)
+library(latex2exp)
+library(xtable)
+
+if (!require(matrixStats)) install.packages('matrixStats')
+library(matrixStats)
+rm(list=ls())
+p<-1000
+RHO <- c(0.9)
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+Sig2<-1
+K.upper<-ceiling(n^(2/3))
+
+hat.gamma.SCAD <- matrix(0,p,REP)
+hat.gamma.MCP <- matrix(0,p,REP)
+hat.gamma.ENET <- matrix(0,p,REP)
+hat.gamma.LASSO <- matrix(0,p,REP)
+for (rho0 in RHO) {
+  FDR.LASSO <- rep(NA,REP)
+  FOR.LASSO <- rep(NA,REP)
+  t2.LASSO  <- rep(NA,REP)
+  n.var.LASSO  <- rep(NA,REP)
+  n.true.LASSO  <- rep(NA,REP)
+  ham.LASSO  <- rep(NA,REP)
+  
+  FDR.SCAD <- rep(NA,REP)
+  FOR.SCAD <- rep(NA,REP)
+  t2.SCAD  <- rep(NA,REP)
+  n.var.SCAD  <- rep(NA,REP)
+  n.true.SCAD  <- rep(NA,REP)
+  ham.SCAD  <- rep(NA,REP)
+  
+  FDR.MCP <- rep(NA,REP)
+  FOR.MCP <- rep(NA,REP)
+  t2.MCP  <- rep(NA,REP)
+  n.var.MCP  <- rep(NA,REP)
+  n.true.MCP  <- rep(NA,REP)
+  ham.MCP  <- rep(NA,REP)
+  
+  FDR.ENET <- rep(NA,REP)
+  FOR.ENET <- rep(NA,REP)
+  t2.ENET  <- rep(NA,REP)
+  n.var.ENET  <- rep(NA,REP)
+  n.true.ENET  <- rep(NA,REP)
+  ham.ENET  <- rep(NA,REP)
+  Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p)))) # AR
+  for (k in 1:REP) {
+    set.seed(1314+k)
+    beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
[…]

### 2019-04-05 Rcode/Goh/Penalized methods_sim1.R

@@ -1,0 +1,191 @@
+library(mvtnorm)
+library(MASS)
+library(glmnet)
+library(ncvreg)
+#library(ggplot2)
+#library(latex2exp)
+library(xtable)
+if (!require(matrixStats)) install.packages('matrixStats')
+library(matrixStats)
+rm(list=ls())
+REP <- 2000
+p<-200
+n<-100
+K.upper<-ceiling(n^(2/3))
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+gamma.true <- rep0
+Sig2<-1
+RHO <- c(0.1)
+rho0<-RHO
+hat.gamma.SCAD <- matrix(0,p,REP)
+hat.gamma.MCP <- matrix(0,p,REP)
+hat.gamma.ENET <- matrix(0,p,REP)
+hat.gamma.LASSO <- matrix(0,p,REP)
+
+  FDR.LASSO <- rep(NA,REP)
+  FOR.LASSO <- rep(NA,REP)
+  t2.LASSO  <- rep(NA,REP)
+  n.var.LASSO  <- rep(0,REP)
+  n.true.LASSO  <- rep(0,REP)
+  ham.LASSO  <- rep(0,REP)
+  
+  FDR.SCAD <- rep(NA,REP)
+  FOR.SCAD <- rep(NA,REP)
+  t2.SCAD  <- rep(NA,REP)
+  n.var.SCAD  <- rep(0,REP)
+  n.true.SCAD  <- rep(0,REP)
+  ham.SCAD  <- rep(0,REP)
+  
+  FDR.MCP <- rep(NA,REP)
+  FOR.MCP <- rep(NA,REP)
+  t2.MCP  <- rep(NA,REP)
+  n.var.MCP  <- rep(0,REP)
+  n.true.MCP  <- rep(0,REP)
+  ham.MCP  <- rep(0,REP)
+  
+  FDR.ENET <- rep(NA,REP)
+  FOR.ENET <- rep(NA,REP)
+  t2.ENET  <- rep(NA,REP)
+  n.var.ENET  <- rep(0,REP)
+  n.true.ENET  <- rep(0,REP)
+  ham.ENET  <- rep(0,REP)
+  Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p)))) # AR
+  for (k in 1:REP) {
+    set.seed(1314+k)
+    beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
[…]

### 2019-04-05 Rcode/Goh/Penalized methods_sim2.R

@@ -1,0 +1,191 @@
+library(mvtnorm)
+library(MASS)
+library(glmnet)
+library(ncvreg)
+#library(ggplot2)
+#library(latex2exp)
+library(xtable)
+if (!require(matrixStats)) install.packages('matrixStats')
+library(matrixStats)
+rm(list=ls())
+REP <- 2000
+p<-200
+n<-100
+K.upper<-ceiling(n^(2/3))
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+gamma.true <- rep0
+Sig2<-1
+RHO <- c(0.9)
+rho0<-RHO
+hat.gamma.SCAD <- matrix(0,p,REP)
+hat.gamma.MCP <- matrix(0,p,REP)
+hat.gamma.ENET <- matrix(0,p,REP)
+hat.gamma.LASSO <- matrix(0,p,REP)
+
+  FDR.LASSO <- rep(NA,REP)
+  FOR.LASSO <- rep(NA,REP)
+  t2.LASSO  <- rep(NA,REP)
+  n.var.LASSO  <- rep(0,REP)
+  n.true.LASSO  <- rep(0,REP)
+  ham.LASSO  <- rep(0,REP)
+  
+  FDR.SCAD <- rep(NA,REP)
+  FOR.SCAD <- rep(NA,REP)
+  t2.SCAD  <- rep(NA,REP)
+  n.var.SCAD  <- rep(0,REP)
+  n.true.SCAD  <- rep(0,REP)
+  ham.SCAD  <- rep(0,REP)
+  
+  FDR.MCP <- rep(NA,REP)
+  FOR.MCP <- rep(NA,REP)
+  t2.MCP  <- rep(NA,REP)
+  n.var.MCP  <- rep(0,REP)
+  n.true.MCP  <- rep(0,REP)
+  ham.MCP  <- rep(0,REP)
+  
+  FDR.ENET <- rep(NA,REP)
+  FOR.ENET <- rep(NA,REP)
+  t2.ENET  <- rep(NA,REP)
+  n.var.ENET  <- rep(0,REP)
+  n.true.ENET  <- rep(0,REP)
+  ham.ENET  <- rep(0,REP)
+  Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p)))) # AR
+  for (k in 1:REP) {
+    set.seed(1314+k)
+    beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
[…]

### 2019-04-05 Rcode/Goh/Penalized methods_sim3.R

@@ -1,0 +1,191 @@
+library(mvtnorm)
+library(MASS)
+library(glmnet)
+library(ncvreg)
+#library(ggplot2)
+#library(latex2exp)
+library(xtable)
+if (!require(matrixStats)) install.packages('matrixStats')
+library(matrixStats)
+rm(list=ls())
+REP <- 2000
+p<-1000
+n<-100
+K.upper<-ceiling(n^(2/3))
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+gamma.true <- rep0
+Sig2<-1
+RHO <- c(0.1)
+rho0<-RHO
+hat.gamma.SCAD <- matrix(0,p,REP)
+hat.gamma.MCP <- matrix(0,p,REP)
+hat.gamma.ENET <- matrix(0,p,REP)
+hat.gamma.LASSO <- matrix(0,p,REP)
+
+  FDR.LASSO <- rep(NA,REP)
+  FOR.LASSO <- rep(NA,REP)
+  t2.LASSO  <- rep(NA,REP)
+  n.var.LASSO  <- rep(0,REP)
+  n.true.LASSO  <- rep(0,REP)
+  ham.LASSO  <- rep(0,REP)
+  
+  FDR.SCAD <- rep(NA,REP)
+  FOR.SCAD <- rep(NA,REP)
+  t2.SCAD  <- rep(NA,REP)
+  n.var.SCAD  <- rep(0,REP)
+  n.true.SCAD  <- rep(0,REP)
+  ham.SCAD  <- rep(0,REP)
+  
+  FDR.MCP <- rep(NA,REP)
+  FOR.MCP <- rep(NA,REP)
+  t2.MCP  <- rep(NA,REP)
+  n.var.MCP  <- rep(0,REP)
+  n.true.MCP  <- rep(0,REP)
+  ham.MCP  <- rep(0,REP)
+  
+  FDR.ENET <- rep(NA,REP)
+  FOR.ENET <- rep(NA,REP)
+  t2.ENET  <- rep(NA,REP)
+  n.var.ENET  <- rep(0,REP)
+  n.true.ENET  <- rep(0,REP)
+  ham.ENET  <- rep(0,REP)
+  Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p)))) # AR
+  for (k in 1:REP) {
+    set.seed(1314+k)
+    beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
[…]

### 2019-04-05 Rcode/Goh/Penalized methods_sim4.R

@@ -1,0 +1,191 @@
+library(mvtnorm)
+library(MASS)
+library(glmnet)
+library(ncvreg)
+#library(ggplot2)
+#library(latex2exp)
+library(xtable)
+if (!require(matrixStats)) install.packages('matrixStats')
+library(matrixStats)
+rm(list=ls())
+REP <- 2000
+p<-1000
+n<-100
+K.upper<-ceiling(n^(2/3))
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+gamma.true <- rep0
+Sig2<-1
+RHO <- c(0.9)
+rho0<-RHO
+hat.gamma.SCAD <- matrix(0,p,REP)
+hat.gamma.MCP <- matrix(0,p,REP)
+hat.gamma.ENET <- matrix(0,p,REP)
+hat.gamma.LASSO <- matrix(0,p,REP)
+
+  FDR.LASSO <- rep(NA,REP)
+  FOR.LASSO <- rep(NA,REP)
+  t2.LASSO  <- rep(NA,REP)
+  n.var.LASSO  <- rep(0,REP)
+  n.true.LASSO  <- rep(0,REP)
+  ham.LASSO  <- rep(0,REP)
+  
+  FDR.SCAD <- rep(NA,REP)
+  FOR.SCAD <- rep(NA,REP)
+  t2.SCAD  <- rep(NA,REP)
+  n.var.SCAD  <- rep(0,REP)
+  n.true.SCAD  <- rep(0,REP)
+  ham.SCAD  <- rep(0,REP)
+  
+  FDR.MCP <- rep(NA,REP)
+  FOR.MCP <- rep(NA,REP)
+  t2.MCP  <- rep(NA,REP)
+  n.var.MCP  <- rep(0,REP)
+  n.true.MCP  <- rep(0,REP)
+  ham.MCP  <- rep(0,REP)
+  
+  FDR.ENET <- rep(NA,REP)
+  FOR.ENET <- rep(NA,REP)
+  t2.ENET  <- rep(NA,REP)
+  n.var.ENET  <- rep(0,REP)
+  n.true.ENET  <- rep(0,REP)
+  ham.ENET  <- rep(0,REP)
+  Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p)))) # AR
+  for (k in 1:REP) {
+    set.seed(1314+k)
+    beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
[…]

### 2019-04-05 Rcode/Goh/Proposed methods_sim1.R

@@ -1,0 +1,281 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-200
+rho0 <- 0.1
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+g.tau <- function(tau0) {
+  SVD <- svd(X.r.star)
+  d.j <- as.vector(SVD$d)
+  z.j <- as.vector(t(SVD$u)%*%y1)
+  log.g.tau <- dim(X.r.star)[2]/2*log(tau0) + 0.5*sum(log(1/tau0+d.j^2)) + 
+    0.5*(a.sigma+n)*log(sum(y1^2)- sum((d.j*z.j)^2/(d.j^2+1/tau0))+b.sigma)
+  return(log.g.tau)
+}
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+  ###############################
+  #Step 1: Set initial values
+  ###############################
+  beta.ini= as.numeric(cor(y1,X1))/diag(var(X1))
[…]

### 2019-04-05 Rcode/Goh/Proposed methods_sim2.R

@@ -1,0 +1,281 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-200
+rho0 <- 0.9
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+g.tau <- function(tau0) {
+  SVD <- svd(X.r.star)
+  d.j <- as.vector(SVD$d)
+  z.j <- as.vector(t(SVD$u)%*%y1)
+  log.g.tau <- dim(X.r.star)[2]/2*log(tau0) + 0.5*sum(log(1/tau0+d.j^2)) + 
+    0.5*(a.sigma+n)*log(sum(y1^2)- sum((d.j*z.j)^2/(d.j^2+1/tau0))+b.sigma)
+  return(log.g.tau)
+}
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+  ###############################
+  #Step 1: Set initial values
+  ###############################
+  beta.ini= as.numeric(cor(y1,X1))/diag(var(X1))
[…]

### 2019-04-05 Rcode/Goh/Proposed methods_sim3.R

@@ -1,0 +1,281 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-1000
+rho0 <- 0.1
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+g.tau <- function(tau0) {
+  SVD <- svd(X.r.star)
+  d.j <- as.vector(SVD$d)
+  z.j <- as.vector(t(SVD$u)%*%y1)
+  log.g.tau <- dim(X.r.star)[2]/2*log(tau0) + 0.5*sum(log(1/tau0+d.j^2)) + 
+    0.5*(a.sigma+n)*log(sum(y1^2)- sum((d.j*z.j)^2/(d.j^2+1/tau0))+b.sigma)
+  return(log.g.tau)
+}
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+  ###############################
+  #Step 1: Set initial values
+  ###############################
[…]

### 2019-04-05 Rcode/Goh/Proposed methods_sim4.R

@@ -1,0 +1,281 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-1000
+rho0 <- 0.9
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+g.tau <- function(tau0) {
+  SVD <- svd(X.r.star)
+  d.j <- as.vector(SVD$d)
+  z.j <- as.vector(t(SVD$u)%*%y1)
+  log.g.tau <- dim(X.r.star)[2]/2*log(tau0) + 0.5*sum(log(1/tau0+d.j^2)) + 
+    0.5*(a.sigma+n)*log(sum(y1^2)- sum((d.j*z.j)^2/(d.j^2+1/tau0))+b.sigma)
+  return(log.g.tau)
+}
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+  ###############################
+  #Step 1: Set initial values
+  ###############################
[…]

### 2019-04-05 Rcode/Goh/Proposed_HS_K.R

@@ -1,0 +1,282 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-1000
+rho0 <- 0.9
+mcsize = 100
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+g.tau <- function(tau0) {
+  SVD <- svd(X.r.star)
+  d.j <- as.vector(SVD$d)
+  z.j <- as.vector(t(SVD$u)%*%y1)
+  log.g.tau <- dim(X.r.star)[2]/2*log(tau0) + 0.5*sum(log(1/tau0+d.j^2)) + 
+    0.5*(a.sigma+n)*log(sum(y1^2)- sum((d.j*z.j)^2/(d.j^2+1/tau0))+b.sigma)
+  return(log.g.tau)
+}
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+  ###############################
+  #Step 1: Set initial values
+  ###############################
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/00_config(1).js

@@ -1,0 +1,17 @@
+window._colwizStylesPath_={"webpdf/button-chrome.css":"webpdf/button-chrome.4e4b96f2f70b3c71591b0d6782b89af5.css","webpdf/button-web.css":"webpdf/button-web.4e4b96f2f70b3c71591b0d6782b89af5.css","webpdf/csl.css":"webpdf/csl.e5c8e7a9ed200f27898a0737f94f74f3.css","webpdf/popup-chrome.css":"webpdf/popup-chrome.c6b1f466455516ec57830d9b5bb84165.css","webpdf/reader-chrome.css":"webpdf/reader-chrome.9e40f03a691803828c465bbb4d873b20.css","webpdf/reader-desktop.css":"webpdf/reader-desktop.9e40f03a691803828c465bbb4d873b20.css",
+"webpdf/reader-web.css":"webpdf/reader-web.9e40f03a691803828c465bbb4d873b20.css"};var CWPDFReaderMode;(function(a){a[a.Chrome=0]="Chrome";a[a.Library=1]="Library";a[a.Publisher=2]="Publisher";a[a.Webimporter=3]="Webimporter";a[a.Drive=4]="Drive";a[a.Firefox=5]="Firefox";a[a.LibraryDesktop=6]="LibraryDesktop";a[a.OpenDrive=7]="OpenDrive"})(CWPDFReaderMode||(CWPDFReaderMode={}));
+var CWPDFReaderConfig,CWApiHandler,publisher=window.publisher,publishersList={colwiz:{name:"colwiz",appIds:{stage:null,production:null},logoClass:"cw-logo",pubModeBtnsTxt:{view:"View & annotate PDF",add:"Add to wizdom.ai Library",viewHover:"Read, annotate and save this article using the wizdom.ai Interactive PDF Reader",addHover:"Save this article to your wizdom.ai library to read and reference anywhere"},readerOptions:{sideBarVisible:!1,tools:{dragPage:!0,textSelection:!0,drawHighlight:!0,eraser:!0,
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/00_config.js

@@ -1,0 +1,18 @@
+var CWPDFReaderMode,CWPDFReaderConfig,CWApiHandler;
+window._colwizStylesPath_={"webpdf/button-chrome.css":"webpdf/button-chrome.4e4b96f2f70b3c71591b0d6782b89af5.css","webpdf/button-web.css":"webpdf/button-web.4e4b96f2f70b3c71591b0d6782b89af5.css","webpdf/csl.css":"webpdf/csl.e5c8e7a9ed200f27898a0737f94f74f3.css","webpdf/popup-chrome.css":"webpdf/popup-chrome.c6b1f466455516ec57830d9b5bb84165.css","webpdf/reader-chrome.css":"webpdf/reader-chrome.9e40f03a691803828c465bbb4d873b20.css","webpdf/reader-desktop.css":"webpdf/reader-desktop.9e40f03a691803828c465bbb4d873b20.css","webpdf/reader-web.css":"webpdf/reader-web.9e40f03a691803828c465bbb4d873b20.css"};
+(function(a){a[a.Chrome=0]="Chrome";a[a.Library=1]="Library";a[a.Publisher=2]="Publisher";a[a.Webimporter=3]="Webimporter";a[a.Drive=4]="Drive";a[a.Firefox=5]="Firefox";a[a.LibraryDesktop=6]="LibraryDesktop";a[a.OpenDrive=7]="OpenDrive"})(CWPDFReaderMode||(CWPDFReaderMode={}));
+var publisher=window.publisher,publishersList={colwiz:{name:"colwiz",appIds:{stage:null,production:null},logoClass:"cw-logo",pubModeBtnsTxt:{view:"View & annotate PDF",add:"Add to wizdom.ai Library",viewHover:"Read, annotate and save this article using the wizdom.ai Interactive PDF Reader",addHover:"Save this article to your wizdom.ai library to read and reference anywhere"},readerOptions:{sideBarVisible:!1,tools:{dragPage:!0,textSelection:!0,drawHighlight:!0,eraser:!0,pencil:!0,rectangle:!0,ellipse:!0,
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/00_main.js

@@ -1,0 +1,755 @@
+/**
+ * Created by Zohaib Khan on 12/2/2015.
+ */
+
+var CwZ = window['CwZ'];
+var CWPDFReader = window['CWPDFReader'] || {followAuth: noop};
+var pubdoi;
+var dataStore = {};
+
+var CWAuthorTip = function (doi) {
+    pubdoi = doi;
+    var _authorList = [];
+    var indexedAuthorList = {};
+    var target = undefined;
+    var xhrInstance;
+    var mouseIn = false;
+
+    function _init() {
+        indexedAuthorList = _authorList;
+        // registerEvents();
+        AuthorTipUtils.CWComApi.init();
+    }
+
+    function _setPopupPosition(target, mouseEvent) {
+        var elem = CwZ("#auProfNewUI");
+        CwZ("#auProfNewUI .tab-container a").on("click", function (e) {//toggle tabs
+            CwZ(".tab-container a").removeClass("selected");
+            CwZ(this).addClass("selected");
+            CwZ(".auth-main-container [data-tab]").hide();
+            CwZ(".auth-main-container [data-tab='" + CwZ(this).attr("data-tab") + "']").show();
+        });
+
+        CwZ(".cw-follow").on("click", function (e) {
+            var authId = CwZ(this).attr("data-id");
+            (CWPDFReader.followAuth || function () {
+            })(authId);
+        });
+
+        var pos = _getPopPosCustom(target, mouseEvent);
+        elem.css("top", pos.top + "px");
+        elem.css("left", pos.left + "px");
+        _setPopupTip(pos.tip);
+    }
+
+    function _getPopPosCustom(target, mouseEvent) {
+        var pos = {tip: {}};
+        var frame = CwZ("#auProfNewUI");
+        var verticalThreshold = 5,
+            horizontalThreshold = (CwZ(target).outerWidth() / 2) + (frame.outerWidth() / 2);
+        var newHorizontalThreshold = 5,
+            newVerticalThreshold = 50;
+
+        var targetRight = CwZ(target)[0].getBoundingClientRect().right;
+        var targetLeft = CwZ(target)[0].getBoundingClientRect().left;
+        var targetTop = CwZ(target)[0].getBoundingClientRect().top;
+        var targetBottom = CwZ(target)[0].getBoundingClientRect().bottom;
+        var tipHeight = CwZ("#auProfNewUI .tooltip-pointer").outerHeight();
+
+        if (target.height() > 20) { //case when link split in two lines
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/01_logger.js

@@ -1,0 +1,3 @@
+var CWloggerClass=function(){function a(){this.headingArea=this.textArea=this.innerDiv=this.button=this.outterDiv=null;this.init()}a.prototype.init=function(d){var b=this;if(0<CwZ("#CWDailogOverlay").length)this.outterDiv=CwZ("#CWDailogOverlay"),this.button=this.outterDiv.find("#btnCancel"),this.innerDiv=this.outterDiv.find(".cw-dailog"),this.headingArea=this.outterDiv.find("h1"),this.textArea=this.outterDiv.find("p"),this.button.off("click").on("click",function(){return b.close()}),d&&d();else{var a=
+this;setTimeout(function(){a.init()},3E3)}};a.prototype.logConsole=function(a,b,c){c&&this.dialog(a,b)};a.prototype.dialog=function(a,b){var c=this;if(this.outterDiv&&0<this.outterDiv.length)this.reset(),b&&this.headingArea.text(b),a&&this.textArea.text(a),"Sign up Successful"===b||"Log in Successful"===b?this.innerDiv.removeClass("cw-error").addClass("cw-success"):this.innerDiv.removeClass("cw-success").addClass("cw-error"),CwZ("#CWDailogOverlay").is(":visible")||this.outterDiv.show();else{var e=
+CWHtmlStructure.getSignupDialog();CwZ("body").append(e);this.init(function(){c.reset();c.dialog(a,b)})}};a.prototype.reset=function(){this.headingArea.text("");this.textArea.text("")};a.prototype.close=function(){0<this.outterDiv.length&&(this.outterDiv.hide(),this.reset())};return a}(),CWlogger=new CWloggerClass;

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/02_cw_codec.js

@@ -1,0 +1,11 @@
+var CWCodecClass=function(){function b(){}b.prototype.encode=function(b,f){var c=new CWShapeParser;return'{"List":{"MemberData":[{"data":{'+c.getCommentsString(b)+","+c.getGraphicsString(b)+","+c.getDeletedString(f)+"}}]}}"};b.prototype.decode=function(b){var f=[],c=[],a=new CWShapeParser,l;try{l=CwZ.parseJSON(b)}catch(e){b=CWUtils.decompress(b),l=CwZ.parseJSON(b)}l=l.List.MemberData[0].data;var d=l.Comments;for(b=0;b<d.length;b++)f.push(a.parseComment(d[b]));d=l.Graphics;for(b=0;b<d.length;b++){var g=
+d[b];g.Cmt=g.Cmt.split("!^!").join("\n");var k=null;g.R?k=a.parseRectangle(g):g.E?k=a.parseEllipse(g):g.A?k=a.parseArrow(g):g.S?k=a.parseLine(g):g.H?k=a.parseHighlight(g):g.F?k=a.parseFreehand(g):g.SHL&&(k=a.parseSelectionHL(g));f.push(k)}a=l.Deleted;for(b=0;b<a.length;b++)c.push(a[b]);return{comments:f,deleted:c}};return b}(),CWCodec=new CWCodecClass;
+function CWShapeParser(){var b=function(c,a){a&&(c.ID=a.uId,c.color=translateCoordinate.convertColorSVG(a.Color),c.lineWidth=parseInt(a.LineWidth,10),c.page=parseInt(a.Page,10),c.ts=parseInt(a.TS,10),c.cmt=a.Cmt)},h=function(c,a){for(var b=c.split(","),e=[],d=0;d<b.length;d+=2)e.push(new CWPoint(b[d],b[d+1]));a&&(e=translateCoordinate.getSVGPoints(e));return e},f=function(c,a){var b="";a&&(c=translateCoordinate.getJSONPoints(c));for(var b=b+(c[0].x.toString()+","+c[0].y.toString()),e=1;e<c.length;e++)b+=
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/03_utilities.js

@@ -1,0 +1,23 @@
+var CWUtilsClass=function(){function e(){this.isIframe=window!==window.parent;this.bParserTest=!1;this.browser={adobeAir:!1,ie:!1,ie9:!1,ie8:!1,ie7:!1,ie6:!1,chrome:!1,firefox:!1,opera:!1,safari:!1};this.sentry={};this.ajax={post:function(a,b,c,d){void 0===c&&(c=function(){});void 0===d&&(d=function(){});void 0===b&&(b={});CwZ.ajax({url:a,type:"POST",dataType:"text",data:b,success:c,error:d})},get:function(a,b,c,d){void 0===c&&(c=function(){});void 0===d&&(d=function(){});void 0===b&&(b={});CwZ.ajax({url:a,
+type:"GET",dataType:"text",data:b,success:c,error:d})}}}e.prototype.removeTags=function(a){return a.replace(RegExp("(\\[(CSA|CrossRef|PubMed|Web of Science \u00ae|Taylor & Francis Online|Google Scholar)\\],?)","g"),"")};e.prototype.matchDoi=function(a){return a?(a=a.match(/\b(10[.][0-9]{4,}(?:[.][0-9]+)*\/(?:\S)+)/g))?a[0]:null:null};e.prototype.findDoi=function(a,b,c){a=CwZ(a).find("."+b).text();!a&&c&&(a=c);return CWUtils.matchDoi(a)};e.prototype.isValidURL=function(a){return/(ftp|http|https):\/\/(\w+:{0,1}\w*@)?(\S+)(:[0-9]+)?(\/|\/([\w#!:.?+=&%@!\-\/]))?/.test(a)?
+!0:!1};e.prototype.getPageUrl=function(){return window.parent.location.href};e.prototype.getPageDomain=function(){var a=window.parent.location;return a.protocol+"//"+a.host};e.prototype.getDomainFromURL=function(a){a=a.replace(/^(.*\/\/)(.*?)(\/.*)$/,"$2");var b=/(.*?)(\w+)(\.[a-z]{2,3})(\.[a-z]{2})?$/;a.replace(b,"$1").replace(/\./g,"");return a=a.replace(b,"$2")};e.prototype.getQueryParam=function(a,b){void 0===b&&(b=location.search);a=a.replace(/[\[]/,"\\[").replace(/[\]]/,"\\]");var c=(new RegExp("[\\?&]"+
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/03b_pdfreader.js

@@ -1,0 +1,147 @@
+var CwZ,referenceCollector=function(){var c={};return{addReferences:function(a){a&&a.forEach(function(a){if(a.year){var d="",k=[];c.hasOwnProperty(a.year)||(c[a.year]={});for(var e=a.author.split(/ and |,|\s/),f=0;f<e.length;f++)0===f%2&&e[f].trim()&&k.push(e[f].trim().replace(/\[|\]/g,"")),e[f].charAt(0)===e[f].charAt(0).toUpperCase()&&(d+=e[f].charAt(0));k.push(d);c[a.year][a.id]=k}})},getReference:function(a,b){var d=a,k=-1;if(c.hasOwnProperty(b))if(1<Object.keys(c[b]).length){var k={},d=d.replace(" et al.",
+"").replace(/[&|;|(|)|,|"]/g,""),d=d.replace(" and "," ").replace("  "," "),d=d.replace(/([a-z])([A-Z])/g,"$1 $2"),d=d.split(" "),e;for(e in c[b]){var f;f=c[b][e];var l=0,g=d.length;if(0<g){for(var h=0;h<f.length;h++)for(var m=0;m<g;m++)d[m]===f[h]&&l++;f=Math.floor(l/g*100)}else f=0;k[f]=e}k=k[Object.keys(k)[Object.keys(k).length-1]]}else k=parseInt(Object.keys(c[b])[0],10);return k},getTestReference:function(){return c}}}(),CWPDFReaderDialogClass=function(){function c(){this.msgBox=this.dialog=
+null;this.dontHide=!1;this.params=""}c.prototype.init=function(){var a=this;this.dialog=CwZ("#cw-dialogBox");this.msgBox=CwZ("#cw-dialogBox span");CwZ("#firstButton").on("click",function(){a.onOkFunc();a.dontHide||a.hide()});CwZ("#secondButton").on("click",function(){a.onCancelFunc();a.hide()})};c.prototype.onOkFunc=function(){};c.prototype.onCancelFunc=function(){};c.prototype.show=function(a){this.dialog||this.init();this.reset();this.params=a;var b={ok:a.okBtnTxt,cancel:a.cnclBtnTxt};this.setMessage(a);
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/04a_pdfreader_publisher.js

@@ -1,0 +1,14 @@
+var __extends=this&&this.__extends||function(){var e=function(c,a){e=Object.setPrototypeOf||{__proto__:[]}instanceof Array&&function(a,g){a.__proto__=g}||function(a,g){for(var c in g)g.hasOwnProperty(c)&&(a[c]=g[c])};return e(c,a)};return function(c,a){function b(){this.constructor=c}e(c,a);c.prototype=null===a?Object.create(a):(b.prototype=a.prototype,new b)}}(),CWPDFReaderPublisher=function(e){function c(){var a=e.call(this)||this;a.recordsOnPage=[];a.extractReferences=!0;return a}__extends(c,e);
+c.prototype.init=function(){var a=this;if(CWUtils.isIframe)try{PDFJS=window["pdfjs-dist/build/pdf"];PDFJS.GlobalWorkerOptions.workerSrc=CWPDFReaderConfig.staticDomainURL+"/js/webpdf/lib/pdf.worker.js?v="+(CWPDFReaderConfig.version||1);-1<navigator.userAgent.toLowerCase().indexOf("firefox")&&PDFJS&&(PDFJS.disableWorker=!0);var b=CwZ("#cw-pdfReaderConfig").html();void 0!==b&&""!==CwZ.trim(b)&&(CWPDFReaderConfig=b=JSON.parse(b));CWUtils.log("LOADING FRAME...:"+CWPDFReaderConfig.cwURL);this.CWIFrameManager=
+new IframeManager;this.CWIFrameManager.setListener(function(b){return a.onMessage(b)});this.CWIFrameManager.tell("iframe-loaded",{view:"mainExt",source:"pdfFrame"});this.initFileLoad(window.parent.CWPDFReader_Publisher.getInstance().urlToOpen)}catch(c){CWUtils.log(c)}};c.prototype.appendDivToHTML=function(a,b,c){CwZ(".referenceHTMLTopDiv").remove();var e=b;b-=155;c+=25;var f=a.title,d=48-f.length;0<d&&(b+=2*d);var d=a.doi,h,k;d?h="http://dx.doi.org/"+CwZ.trim(d):k=f?"https://scholar.google.com.pk/scholar?hl=en&q="+
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/05_annotations.js

@@ -1,0 +1,65 @@
+var CWDrawMode;(function(c){c[c.Drag=0]="Drag";c[c.Freehand=1]="Freehand";c[c.Line=2]="Line";c[c.Rectangle=3]="Rectangle";c[c.Highlight=4]="Highlight";c[c.Ellipse=5]="Ellipse";c[c.Arrow=6]="Arrow";c[c.Eraser=7]="Eraser";c[c.Comment=8]="Comment";c[c.TextSelection=9]="TextSelection"})(CWDrawMode||(CWDrawMode={}));var CWDrawEvent;(function(c){c[c.Click=0]="Click";c[c.TouchStart=1]="TouchStart";c[c.TouchEnd=2]="TouchEnd";c[c.TouchMove=3]="TouchMove"})(CWDrawEvent||(CWDrawEvent={}));
+var CWPoint=function(){return function(c,a){"undefined"===typeof c&&(c=null);"undefined"===typeof a&&(a=null);this.x=parseInt(c,10);this.y=parseInt(a,10)}}(),CWAnnotateClass=function(){function c(){this.oldMousePos=[null,null];this.newIds=(new Date).getTime();this.pagesSVG=[];this.hashSVG={};this.hashComment={};this.mouseDn=0;this.mouseMovePage=this.mouseDownPage=this.mousemovestartY=this.mousemovestartX=this.newMousePosY=this.newMousePosX=this.oldMousePosY=this.oldMousePosX=-1;this.clipboardText=
+""}c.prototype.init=function(a){a=a?a.jqElement:CwZ(document);a.find(".cw-textLayer").off("click mousemove mousedown mouseup");a.find(".cw-textLayer").on("click mousemove mousedown mouseup",function(a){a.stopImmediatePropagation();CWDataHolder.lastActivity.click=(new Date).getTime();if(CWDraw.drawMode===CWDrawMode.TextSelection){CwZ(".cw-body").removeClass("no-select");var b=CwZ(".cw-text-tip"),e=0,d=0;CWPageManager.scrollPosition&&(e=CWPageManager.scrollPosition.y,d=CWPageManager.scrollPosition.x);
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/06_page.js

@@ -1,0 +1,61 @@
+var SCROLLBAR_PADDING,parseQueryString,CSS_UNITS=96/72,CWPDFManagerClass=function(){function f(){this.loading=!1;this.destinationsPromise=this.pdf=null;this.pagesRefMap={};this.tsLoadingStart=0;this.viewMode="";this.documentInfo=this.metadata=null;this.viewModes={height:1,width:2,other:3}}f.prototype.openFile=function(a,b){CWPDFReader.initialize();CWUtils.log("in openFIle");CWUtils.log("openFileURL: "+a);this.loading=!0;this.tsLoadingStart=(new Date).getTime();var c=this,d=function(a){c.progress(a.loaded/
+a.total)},e={url:a};try{PDFJS.openExternalLinksInNewWindow=!0,PDFJS.getDocument(e,null,null,d).then(function(a){CWPDFManager.pdf=a;c.loadPDF(a);c.loading=!1},function(b,d){var e="An error occurred while loading the PDF.";if(b&&(e="There was an error opening this document. Invalid or corrupted PDF file.",CWPDFReaderConfig.isDesktopMode())){var g={};g.msg=e;g.onOk=function(){window.parent.postMessage({message:"closepdf",data:CWPDFReader.commentsSyncPending,frameId:window.frameElement.id},"*")};CWPDFReaderDialog.show(g)}d&&
+"MissingPDFException"===d.name&&(e="Missing PDF file.");CWPDFReaderConfig.isDesktopMode()||void 0!==CWPDFReader.errorLoadingFile&&CWPDFReader.errorLoadingFile(a);CWUtils.log(e);c.loading=!1})}catch(g){CWPDFReaderConfig.checkReaderMode("library")?PDFRaven.captureException(g.stack):CwZ(document).trigger("cwExcToSentry",g)}};f.prototype.loadPDF=function(a){var b=this;try{CWPDFReader.onRenderComplete(),CWPDFReaderConfig.isCoreMode()||CWPDFReaderConfig.isDesktopMode()||(CWEventTracker.pushEvent("viewpdf"),
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/07_datacenter.js

@@ -1,0 +1,93 @@
+var _paq=_paq||[],CWApiHandler=CWApiHandler?CWApiHandler:{loadConfig:function(c){CWApiHandler.get(c)},loadComments:function(c){CWApiHandler.get(c)},get:function(c){CWUtils.ajax.get(c.url,c.data,function(a){c.success(a)},function(){c.error()})},post:function(c){CWUtils.ajax.post(c.url,c.data,function(a){c.success(a)},function(a){c.error(a)})},checkLogin:function(c){CWUtils.log(c);CwZ.ajax({type:"GET",url:c.url,success:function(a,e,b){c.success(a,e,b)},error:function(a){c.error(a)}})},loadContacts:function(c){CwZ.ajax({type:"GET",
+url:c.url,success:function(a,e,b){c.success(a,e,b)},error:function(a){c.error(a)}})},loadGroups:function(c){CwZ.ajax({type:"GET",url:c.url,success:function(a,e,b){c.success(a,e,b)},error:function(a){c.error(a)}})},saveComments:function(c){CWApiHandler.post(c)},findPublication:function(c){CWApiHandler.post(c)},createPublication:function(c){CWApiHandler.post(c)},findFile:function(c){CWApiHandler.post(c)},getUploadParams:function(c){CwZ.ajax({url:c.url,data:c.data,type:"POST",success:function(a){c.success(a)},
+error:function(){c.error()}})},findPubs:function(c){CWUtils.ajax.post(c.url,c.data,function(a,e,b){c.success(a,e,b)})},findPubsDOI:function(c){CWApiHandler.get(c)},getFileURL:function(c){CWUtils.ajax.get(c.url,c.data,c.success,c.error)},uploadFile:function(c){try{CWPDFReader.uploadFile(void 0!==c.data.blobLink?c.data.blobLink:c.data.pdfLink,c.data.index,{euId:c.data.euId,fileId:c.data.fileId})}catch(a){CWDataCenter.exceptionHandler(a)}},postToTracker:function(c){},injectPiwik:function(c){},trackPiwik:function(c){},
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/08_textlayer.js

@@ -1,0 +1,13 @@
+var CustomStyle=function(){function g(){}var q=["ms","Moz","Webkit","O"],e={};g.getProp=function(a,d){if(1===arguments.length&&"string"===typeof e[a])return e[a];d=d||document.documentElement;var c=d.style,b,f;if("string"===typeof c[a])return e[a]=a;f=a.charAt(0).toUpperCase()+a.slice(1);for(var m=0,h=q.length;m<h;m++)if(b=q[m]+f,"string"===typeof c[b])return e[a]=b;return e[a]="undefined"};g.setProp=function(a,d,c){a=this.getProp(a);"undefined"!==a&&(d.style[a]=c)};return g}(),TextLayerBuilder=function(g){var q=
+document.createDocumentFragment();this.textLayerDiv=g.textLayerDiv;this.divContentDone=this.layoutDone=!1;this.pageIdx=g.pageIndex;this.matches=[];this.lastScrollSource=g.lastScrollSource;this.viewport=g.viewport;this.isViewerInPresentationMode=g.isViewerInPresentationMode;this.textDivs=[];"undefined"===typeof PDFFindController&&(window.PDFFindController=null);"undefined"===typeof this.lastScrollSource&&(this.lastScrollSource=null);this.renderLayer=function(){var e=this.textDivs,a=document.createElement("canvas").getContext("2d");
+if(!(1E5<e.length)){for(var d=0,c=e.length;d<c;d++){var b=e[d];if(!("isWhitespace"in b.dataset)){a.font=b.style.fontSize+" "+b.style.fontFamily;var f=void 0,f="true"===b.dataset.edited?a.measureText(b.textContent.substring(0,b.textContent.length-1)).width:a.measureText(b.textContent).width;0<f&&(q.appendChild(b),f="scale("+parseFloat((b.dataset.canvasWidth/f).toFixed(3))/2+", 1)",f="rotate("+b.dataset.angle+"deg) "+f,CustomStyle.setProp("transform",b,f),CustomStyle.setProp("transformOrigin",b,"0% 0%"))}}this.textLayerDiv.appendChild(q);
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/09_comments.js

@@ -1,0 +1,36 @@
+var CWCommentManagerClass=function(){function e(){this.annotationArr=[];this.deletedArr=[];this.commentSideBar=new CWSideBar;this.bCommentLoaded=!1;this.oldComments=this.selectedComments=null;this.annotationsOwner="";this.sidebarHtml={};this.commentsList={}}e.prototype.bUpdateCmt=function(b,d){if(parseInt(b.ts,10)>parseInt(d.ts,10)){if(b.Pos!==d.Pos){d.Pos=b.Pos;var a=d.Pos.split(","),c="";CwZ("#"+CWAnnotate.hashComment[d.uId]).attr("d");c+="m"+a[0]+","+a[1];c+="l0,-6l-3,0c-1.5,0 -3,-1.5 -3,-3l0,-5c0,-1.5 1.5,-3 3,-3l14,0c1.5,0 3,1.5 3,3l0,5c0,1.5 -1.5,3 -3,3l-7,0l-4,6z";
+CwZ("#"+CWAnnotate.hashComment[d.uId]).attr("d",c)}return!0}return!1};e.prototype.bUpdateShp=function(b,d,a){var c="",m;for(m in b)if(1===m.length&&-1!=="ERHASF".indexOf(m)){c=m;break}var e="";for(m in d)if(1===m.length&&-1!=="ERHASF".indexOf(m)){e=m;break}if(parseInt(b.TS,10)>parseInt(d.TS,10)){if(b[c]&&d[e]&&b[c]!==d[e])for(d[e]=b[c],c=void 0,b=0;b<a.length;b++)if(a[b].ID===d.uId)if(d.R)c=d.R.split(","),a[b].points[1].x=c[0],a[b].points[1].y=c[1],CwZ("#"+CWAnnotate.hashComment[d.uId]).attr("x",
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/10_shape.js

@@ -1,0 +1,3 @@
+function CWShape(){this.ID="";this.color="0x000000";this.lineWidth=1;this.ts=this.page=0;this.cmt="";this.points=[]}CWShape.prototype.toString=function(){};CWShape.prototype.addPoint=function(a){0===this.points.length?this.points.push(a):this.points[0]=a};CWShape.prototype.updatePoint=function(a){1===this.points.length?this.points.push(a):this.points[1]=a};function CWRectangle(){this.constructor()}CWRectangle.prototype=new CWShape;function CWEllipse(){this.constructor()}CWEllipse.prototype=new CWShape;
+function CWArrow(){this.constructor()}CWArrow.prototype=new CWShape;function CWLine(){this.constructor()}CWLine.prototype=new CWShape;function CWHighlight(){this.constructor()}CWHighlight.prototype=new CWShape;function CWSelectionHL(){this.constructor();this.rects=[];this.points=[]}CWSelectionHL.prototype=new CWShape;function CWFreehand(){this.points=[];this.constructor()}CWFreehand.prototype=new CWShape;
+CWFreehand.prototype.updatePoint=function(a){var b=this.points[this.points.length-1],d=a.x,c=a.y,c=b.y>=c?b.y-c:c-b.y;(3<=(b.x>=d?b.x-d:d-b.x)||3<=c)&&this.points.push(a)};function CWComment(){this.ID="";this.ts=this.page=0;this.cmt="";this.point=null;this.color="#be964b"}CWComment.prototype.addPoint=function(a){this.point=a};

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/Blob.js

@@ -1,0 +1,1 @@
+!function(t,e){"object"==typeof exports&&"string"!=typeof exports.nodeName?module.exports=t.document?e(t,!0):function(t){if(!t.document)throw new Error("blobjs requires a window with a document");return e(t)}:e(t)}(window||this,function(t,e){"use strict";var n=/^((?!chrome|android).)*safari/i.test(navigator.userAgent);if(t.URL=t.URL||t.webkitURL,t.Blob&&t.URL&&!n)try{return new t.Blob,"function"==typeof define&&define.amd&&define("blobjs",[],function(){return t.Blob}),t.Blob}catch(t){}var c=t.BlobBuilder||t.WebKitBlobBuilder||t.MozBlobBuilder||function(t){var c=function(t){return Object.prototype.toString.call(t).match(/^\[object\s(.*)\]$/)[1]},e=function(){this.data=[]},u=function(t,e,n){this.data=t,this.size=t.length,this.type=e,this.encoding=n},n=e.prototype,o=u.prototype,d=t.FileReaderSync,s=function(t){this.code=this[this.name=t]},i="NOT_FOUND_ERR SECURITY_ERR ABORT_ERR NOT_READABLE_ERR ENCODING_ERR NO_MODIFICATION_ALLOWED_ERR INVALID_STATE_ERR SYNTAX_ERR".split(" "),r=i.length,a=t.URL||t.webkitURL||t,l=a.createObjectURL,f=a.revokeObjectURL,p=a,b=t.btoa,R=t.atob,h=t.ArrayBuffer,g=t.Uint8Array,w=/^[\w-]+:\/*\[?[\w\.:-]+\]?(?::[0-9]+)?/;for(u.fake=o.fake=!0;r--;)s.prototype[i[r]]=r+1;return a.createObjectURL||(p=t.URL=function(t){var e,n=document.createElementNS("http://www.w3.org/1999/xhtml","a");return n.href=t,"origin"in n||("data:"===n.protocol.toLowerCase()?n.origin=null:(e=t.match(w),n.origin=e&&e[1])),n}),p.createObjectURL=function(t){var e,n=t.type;return null===n&&(n="application/octet-stream"),t instanceof u?(e="data:"+n,"base64"===t.encoding?e+";base64,"+t.data:"URI"===t.encoding?e+","+decodeURIComponent(t.data):b?e+";base64,"+b(t.data):e+","+encodeURIComponent(t.data)):l?l.call(a,t):void 0},p.revokeObjectURL=function(t){"data:
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/auth.js

@@ -1,0 +1,2 @@
+"use strict";function _slicedToArray(e,t){return _arrayWithHoles(e)||_iterableToArrayLimit(e,t)||_nonIterableRest()}function _nonIterableRest(){throw new TypeError("Invalid attempt to destructure non-iterable instance")}function _iterableToArrayLimit(e,t){var i=[],s=!0,o=!1,n=void 0;try{for(var a,r=e[Symbol.iterator]();!(s=(a=r.next()).done)&&(i.push(a.value),!t||i.length!==t);s=!0);}catch(e){o=!0,n=e}finally{try{s||null==r.return||r.return()}finally{if(o)throw n}}return i}function _arrayWithHoles(e){if(Array.isArray(e))return e}function _extends(){return(_extends=Object.assign||function(e){for(var t=1;t<arguments.length;t++){var i=arguments[t];for(var s in i)Object.prototype.hasOwnProperty.call(i,s)&&(e[s]=i[s])}return e}).apply(this,arguments)}function _classCallCheck(e,t){if(!(e instanceof t))throw new TypeError("Cannot call a class as a function")}function _defineProperties(e,t){for(var i=0;i<t.length;i++){var s=t[i];s.enumerable=s.enumerable||!1,s.configurable=!0,"value"in s&&(s.writable=!0),Object.defineProperty(e,s.key,s)}}function _createClass(e,t,i){return t&&_defineProperties(e.prototype,t),i&&_defineProperties(e,i),e}function _defineProperty(e,t,i){return t in e?Object.defineProperty(e,t,{value:i,enumerable:!0,configurable:!0,writable:!0}):e[t]=i,e}var _wdom=wdom,onReady=_wdom.onReady,el=_wdom.el,parents=_wdom.parents,isMobile=_wdom.isMobile,val=_wdom.val,html=_wdom.html,text=_wdom.text,hide=_wdom.hide,show=_wdom.show,removeAttribute=_wdom.removeAttribute,hasClass=_wdom.hasClass,addClass=_wdom.addClass,removeClass=_wdom.removeClass,setAttribute=_wdom.setAttribute,getAttribute=_wdom.getAttribute,fadeIn=_wdom.fadeIn,trim=_wdom.trim,fadeOut=_wdom.fadeOut,triggerEvent=_wdom.triggerEvent,closest=_wdom.closest,getString=_wdom.getString,hasMaxLength=_wdom.hasMa
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/autosize.js

@@ -1,0 +1,1 @@
+!function(e,t){if("function"==typeof define&&define.amd)define(["module","exports"],t);else if("undefined"!=typeof exports)t(module,exports);else{var n={exports:{}};t(n,n.exports),e.autosize=n.exports}}(this,function(e,t){"use strict";var n,o,p="function"==typeof Map?new Map:(n=[],o=[],{has:function(e){return-1<n.indexOf(e)},get:function(e){return o[n.indexOf(e)]},set:function(e,t){-1===n.indexOf(e)&&(n.push(e),o.push(t))},delete:function(e){var t=n.indexOf(e);-1<t&&(n.splice(t,1),o.splice(t,1))}}),c=function(e){return new Event(e,{bubbles:!0})};try{new Event("test")}catch(e){c=function(e){var t=document.createEvent("Event");return t.initEvent(e,!0,!1),t}}function r(r){if(r&&r.nodeName&&"TEXTAREA"===r.nodeName&&!p.has(r)){var e,n=null,o=null,i=null,d=function(){r.clientWidth!==o&&a()},l=function(t){window.removeEventListener("resize",d,!1),r.removeEventListener("input",a,!1),r.removeEventListener("keyup",a,!1),r.removeEventListener("autosize:destroy",l,!1),r.removeEventListener("autosize:update",a,!1),Object.keys(t).forEach(function(e){r.style[e]=t[e]}),p.delete(r)}.bind(r,{height:r.style.height,resize:r.style.resize,overflowY:r.style.overflowY,overflowX:r.style.overflowX,wordWrap:r.style.wordWrap});r.addEventListener("autosize:destroy",l,!1),"onpropertychange"in r&&"oninput"in r&&r.addEventListener("keyup",a,!1),window.addEventListener("resize",d,!1),r.addEventListener("input",a,!1),r.addEventListener("autosize:update",a,!1),r.style.overflowX="hidden",r.style.wordWrap="break-word",p.set(r,{destroy:l,update:a}),e=window.getComputedStyle(r,null),"vertical"===e.resize?r.style.resize="none":"both"===e.resize&&(r.style.resize="horizontal"),n="content-box"===e.boxSizing?-(parseFloat(e.paddingTop)+parseFloat(e.paddingBottom)):parseFloat(e.borderTopWidth)+parseFloat(e.borderBottomWidth),isNaN(n)&&(n=0),a()}function s(e){var t=r.style.width;r.style.width="0px",r.offsetWidth,r.style.width=t
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/colwiz_frame.js

@@ -1,0 +1,3 @@
+var cPDF_CWFrame=function(){function b(){this.initErrors=[];this.domain=CWPDFReaderConfig.cwURL;this.version="19.03.21-4630-732";this.js="js/webpdf/lib/jquery.js js/webpdf/lib/raven.js js/webpdf/lib/zlib_and_gzip.min.js js/webpdf/lib/jquery.cookie.js js/webpdf/main/03_utilities.js js/webpdf/main/07_datacenter.js js/webpdf/publisher/iframe_pub.js js/webpdf/publisher/com_manager.js js/webpdf/lib/mods_parser.js".split(" ");this.init()}return b.prototype.init=function(){try{var a=window.location.href;this.version=
+a.substring(a.indexOf("?v=")+3,a.length);this.loadJs(0)}catch(d){this.initErrors.push(d)}},b.prototype.loadJs=function(a){try{if(a<this.js.length){var d=this;this.addScript(this.js[a]+"?v="+this.version,function(){d.loadJs(a+1)})}}catch(b){this.initErrors.push(b)}},b.prototype.addScript=function(a,b){var f=this,c=document.createElement("script"),g=document.getElementsByTagName("script")[0];b&&(c.onload=b);c.type="text/javascript";var e=CWPDFReaderConfig.staticDomainURL;0<=e.indexOf("http")?c.src=
+e+"/"+a:c.src=("https:"===document.location.protocol?"https://":"http://")+e+"/"+a;g.parentNode.appendChild(c);-1!==a.indexOf("raven")&&setTimeout(function(){setTimeout(function(){for(var a=0;a<f.initErrors.length;a++)-1!==CWPDFReaderConfig.cwURL.indexOf(colwizOptions.cwURL)&&Raven.captureException(f.initErrors[a]);!0},2E3)},2E3)},b}(),cPDF_CW=new cPDF_CWFrame;

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/com_manager.js

@@ -1,0 +1,18 @@
+var CWComManagerClass=function(){function b(){this.CWIFrameManager=null}b.prototype.init=function(){var a=this;this.CWIFrameManager=new IframeManager;this.CWIFrameManager.setListener(function(b){return a.onMessage(b)});this.CWIFrameManager.tell("iframe-loaded",{view:"mainExt",source:"cwFrame"});CWUtils.log("loaded cwz frame")};b.prototype.onMessage=function(a){var b=this;CWUtils.log("com_manager.js CWComManager.onMessage:"+a.message);switch(a.message){case "sendException":CWDataCenter.postMsgToSentry(a.data.error);
+break;case "postToTracker":CWDataCenter.postToTracker(a.data.action,a.data.metaData);break;case "signoutCallToColwiz":CWDataCenter.signoutCallToColwiz();break;case "redirectToMyProfile":CWDataCenter.redirectToMyProfile();break;case "polling":CWDataCenter.polling();break;case "loadConfig":CWDataCenter.checkLogin(CWDataCenter.loadConfig);break;case "checkLogin":CWDataCenter.checkLogin(function(){b.CWIFrameManager.tell("defferredAction",{loggedIn:!0,view:"mainExt",source:"cwFrame"})},function(){b.CWIFrameManager.tell("defferredAction",
+{showSignIn:a.data.showSignIn,loggedIn:!1,view:"mainExt",source:"cwFrame"})});break;case "updateUserDOM":CWDataCenter.updateUserDOM();break;case "findPubsCall":CWDataCenter.findPubs();break;case "getFileId":CWDataCenter.getFileId(!0);break;case "syncData":CWDataCenter.syncData();break;case "saveComments":CWDataCenter.saveComments(a.data.cmtString);break;case "pubSelected":CWDataCenter.pubSelected=a.data.metaData;break;case "createPublication":CWDataCenter.createPublication(a.data.obj);break;case "addToLibrary":CWDataCenter.addToLibrary(a.data.index);
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/gtm.js

@@ -1,0 +1,607 @@
+
+// Copyright 2012 Google Inc. All rights reserved.
+(function(w,g){w[g]=w[g]||{};w[g].e=function(s){return eval(s);};})(window,'google_tag_manager');(function(){
+
+var data = {
+"resource": {
+  "version":"29",
+  "macros":[{
+      "function":"__k",
+      "vtp_decodeCookie":false,
+      "vtp_name":"_ga"
+    },{
+      "function":"__jsm",
+      "vtp_javascript":["template","(function(){try{var a=",["escape",["macro",0],8,16],".split(\".\");return a[2]+\".\"+a[3]}catch(b){return console.log(\"No Universal Analytics cookie found\"),\"n\/a\"}})();"]
+    },{
+      "function":"__jsm",
+      "vtp_javascript":["template","(function(){var a=document.getElementsByTagName(\"meta\");for(i=0;i\u003Ca.length;i++)if(\"pbContext\"==a[i].getAttribute(\"name\")){a=a[i].getAttribute(\"content\");var b=a.indexOf(\"journal:journal:\");return-1==b?\"n\/a\":a[b+16]+a[b+17]+a[b+18]+a[b+19]+a[b+20]+a[b+21]}})();"]
+    },{
+      "function":"__e"
+    },{
+      "function":"__gas",
+      "vtp_cookieDomain":"auto",
+      "vtp_doubleClick":false,
+      "vtp_setTrackerName":false,
+      "vtp_useDebugVersion":false,
+      "vtp_useHashAutoLink":false,
+      "vtp_decorateFormsAutoLink":false,
+      "vtp_enableLinkId":false,
+      "vtp_enableEcommerce":false,
+      "vtp_trackingId":"UA-3062505-5",
+      "vtp_enableRecaptchaOption":false,
+      "vtp_enableUaRlsa":false,
+      "vtp_enableUseInternalVersion":false
+    },{
+      "function":"__aev",
+      "vtp_varType":"TEXT"
+    },{
+      "function":"__v",
+      "vtp_name":"gtm.elementClasses",
+      "vtp_dataLayerVersion":1
+    },{
+      "function":"__v",
+      "vtp_name":"gtm.element",
+      "vtp_dataLayerVersion":1
+    },{
+      "function":"__u",
+      "vtp_enableMultiQueryKeys":false
+    },{
+      "function":"__u",
+      "vtp_component":"HOST",
+      "vtp_enableMultiQueryKeys":false
+    },{
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/hotjar-864760.js

@@ -1,0 +1,13 @@
+window.hjSiteSettings = window.hjSiteSettings || {"features":[],"site_id":864760,"integrations":{"optimizely":{"tag_recordings":false}},"privacy_policy_url":null,"deferred_page_contents":[],"surveys":[],"feedback_widgets":[],"anonymize_digits":true,"forms":[],"state_change_listen_mode":"automatic","testers_widgets":[],"legal_name":null,"recording_capture_keystrokes":true,"rec_value":1.0,"suppress_text":null,"suppress_location":false,"record_targeting_rules":[],"heatmaps":[],"polls":[],"record":false,"r":0.0290013674,"suppress_all":false,"anonymize_emails":true};
+
+!function(t){function e(e){for(var n,r,i=e[0],a=e[1],c=0,s=[];c<i.length;c++)r=i[c],o[r]&&s.push(o[r][0]),o[r]=0;for(n in a)Object.prototype.hasOwnProperty.call(a,n)&&(t[n]=a[n]);for(u&&u(e);s.length;)s.shift()()}var n={},o={0:0};function r(e){if(n[e])return n[e].exports;var o=n[e]={i:e,l:!1,exports:{}};return t[e].call(o.exports,o,o.exports,r),o.l=!0,o.exports}r.e=function(t){var e=[],n=o[t];if(0!==n)if(n)e.push(n[2]);else{var i=new Promise(function(e,r){n=o[t]=[e,r]});e.push(n[2]=i);var a,c=document.getElementsByTagName("head")[0],u=document.createElement("script");u.charset="utf-8",u.timeout=120,r.nc&&u.setAttribute("nonce",r.nc),u.src=function(t){return r.p+""+({1:"modules"}[t]||t)+"."+{1:"eead9e9a55afdb3247fc"}[t]+".js"}(t),a=function(e){u.onerror=u.onload=null,clearTimeout(s);var n=o[t];if(0!==n){if(n){var r=e&&("load"===e.type?"missing":e.type),i=e&&e.target&&e.target.src,a=new Error("Loading chunk "+t+" failed.\n("+r+": "+i+")");a.type=r,a.request=i,n[1](a)}o[t]=void 0}};var s=setTimeout(function(){a({type:"timeout",target:u})},12e4);u.onerror=u.onload=a,c.appendChild(u)}return Promise.all(e)},r.m=t,r.c=n,r.d=function(t,e,n){r.o(t,e)||Object.defineProperty
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/html_structure.js

@@ -1,0 +1,16 @@
+var CWHtmlStructureClass=function(){function b(){}return b.prototype.getBody=function(a,d){a=encodeURI(a);d=encodeURI(d);var c="cw-logo";CWPDFReaderConfig.readerMode===CWPDFReaderMode.Publisher&&(c="publisher-logo");var e="display:none;",h="";CWPDFReaderConfig.readerMode!==CWPDFReaderMode.Library&&CWPDFReaderConfig.readerMode!==CWPDFReaderMode.Drive&&(e="",h="display:none;");var b=CWPDFReaderConfig.readerMode===CWPDFReaderMode.Drive,g=CWPDFReaderConfig.readerMode!==CWPDFReaderMode.Library&&CWPDFReaderConfig.readerMode!==
+CWPDFReaderMode.Drive;CwH.partials=CwH.templates;var k=CwH.templates.getBody;return k({smallCanvasClass:"",imageUrl:a,logoClass:c,modeDrive:b,modeNotDriveLibrary:g,fullscreenBtnStyle:e,restoreBtnStyle:h,CWPDFReaderConfig:{cwURL:CWPDFReaderConfig.cwURL,idURL:CWPDFReaderConfig.idURL},pdfUrl:d})},b.prototype.getCommentBody=function(a){return(CWPDFReaderConfig.isDesktopMode()||CWPDFReaderConfig.readerMode===CWPDFReaderMode.Chrome?CwH.templates.getCommentBody:window.parent.CwH.templates.getCommentBody)({cmtId:a.cmtId,
+cmtText:a.cmtText,cmtClass:a.cmtClass,timeDiff:a.timeDiff,cmtPage:a.cmtPage,minY:a.minY})},b.prototype.getSplashScreen=function(a){CwH.partials=CwH.templates;var d=CwH.templates.getSplash,c=!CWPDFReaderConfig.isCoreMode();return d({classSpec:a,notCoreMode:c,loaderClass:c?"cw-loader":""})},b.prototype.getPopupBody=function(a,d){var c=CwH.templates.getPopupBody;return c({getRecHtml:a,contextCont:d})},b.prototype.getDownloadPopup=function(a,d){var c=JSON.parse(JSON.stringify(a));/^(?:[A-Za-z0-9+/]{4})*(?:[A-Za-z0-9+/]{2}==|[A-Za-z0-9+/]{3}=|[A-Za-z0-9+/]{4})([=]{1,2})?$/.test(c.title)&&
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/iframe_pub.js

@@ -1,0 +1,2 @@
+var IframeManager=function(){function c(){this._this={};this._listener=null;this.init()}c.prototype.init=function(){var b=this;window.addEventListener("message",function(a){return b.background_onMessage(a)},!1)};c.prototype.background_onMessage=function(b){b=b.data;b.message&&this._listener&&this._listener(b)};c.prototype.setListener=function(b){this._listener=b};c.prototype.tell=function(b,a){a=a||{};a.name&&-1!==a.name.toLowerCase().indexOf("error")&&(a={view:a.view,message:a.message,stack:a.stack});
+window.parent.postMessage({message:b,data:a},"*")};return c}();

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/initials_avatar.js

@@ -1,0 +1,2 @@
+!function(n){function a(t){if(r[t])return r[t].exports;var e=r[t]={exports:{},id:t,loaded:!1};return n[t].call(e.exports,e,e.exports,a),e.loaded=!0,e.exports}var r={};a.m=n,a.c=r,a.p="",a(0)}([function(t,e,n){"use strict";function a(t){var e=["#626be0","#e06277","#b467da","#e09862","#1abc9c","#f44336","#3498db","#673ab7","#34495e","#8bc24a","#27ae60","#2980b9","#8e44ad","#6c3244","#f1c40f","#2266e6","#e74c3c","#50e3c2","#4498ae","#f39c12","#2c5e1c","#ea1e63","#62b6e0","#484d9c"],n=c((t.getAttribute("data-fulltitle")||"").replace(/[`~!@#$%^&*()_|+\-=?;:'",.<>\{\}\[\]\\\/]/gi,""));""==n&&(n=c(t.getAttribute("data-fulltitle")||""));var a="";if(n){var r=n.split(" "),i=r[0][0];if(a=d(i)?i.toUpperCase():i,1<r.length&&r[r.length-1][0]){var o=r[r.length-1][0];a+=d(o)?o.toUpperCase():o}t.setAttribute("data-avatar",a)}else a=t.getAttribute("data-avatar"),t.setAttribute("data-avatar",a||"");if(a=t.getAttribute("data-avatar")){var s=Math.abs(a[0].charCodeAt()-64),l=s*(1<a.length?Math.abs(a[1].charCodeAt()-64):0)+s;t.setAttribute("style","background-color:"+e[l%e.length])}}function c(t){return"string"==typeof t&&t&&t.length?t.replace(/^\s+|\s+$|\s+(?=\s)/g,""):""}n(4);var r=function(t){"nodeInserted"==t.animationName&&a(t.target)},d=function(t){return 1===t.length&&/[a-z]/i.test(t)};window.rerenderAvatar=function(){var t=document.querySelectorAll("[data-avatar]");[].slice.call(t).forEach(function(t){return a(t)})},document.addEventListener("animationstart",r,!1),document.addEventListener("MSAnimationStart",r,!1),document.addEventListener("webkitAnimationStart",r,!1)},function(t,e,n){(t.exports=n(2)()).push([t.id,"@-webkit-keyframes nodeInserted{0%{opacity:.99}to{opacity:1}}@keyframes nodeInserted{0%{opacity:.99}to{opacity:1}}[data-
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/ireader.js

@@ -1,0 +1,1 @@
+var CwZ,CwH,CWParser,CWPDFReaderConfig,Handlebars,define;window._colwizStylesPath_={"webpdf/button-chrome.css":"webpdf/button-chrome.4e4b96f2f70b3c71591b0d6782b89af5.css","webpdf/button-web.css":"webpdf/button-web.4e4b96f2f70b3c71591b0d6782b89af5.css","webpdf/csl.css":"webpdf/csl.e5c8e7a9ed200f27898a0737f94f74f3.css","webpdf/popup-chrome.css":"webpdf/popup-chrome.c6b1f466455516ec57830d9b5bb84165.css","webpdf/reader-chrome.css":"webpdf/reader-chrome.9e40f03a691803828c465bbb4d873b20.css","webpdf/reader-desktop.css":"webpdf/reader-desktop.9e40f03a691803828c465bbb4d873b20.css","webpdf/reader-web.css":"webpdf/reader-web.9e40f03a691803828c465bbb4d873b20.css"};var cPDF_Class=function(){function t(){this.initErrors=[],this.domain="app.wizdom.ai",this.staticDomainURL="cdn.wizdom.ai/static",this.assetsDomainURL="cdn.wizdom.ai/assets",this.version="19.04.03-4671-738",this.initialized=!1,this.js=["js/webpdf/extension/all_pubsol.js","js/webpdf/lib/initials-avatar.js","js/webpdf/lib/FileSaver.js","js/webpdf/lib/citation.converter.js","js/extraction/authortooltip/js/00_main.js","js/webpdf/lib/cwcsl.js","js/webpdf/lib/citeproc.js"],this.init()}return t.prototype.init=function(){try{var t=this.supports_canvas_text(),e=this.check_mobile_browser(),s=this.check_for_ie();if(publisher&&publisher.readerOptions.mobileModeEnable&&(e=!1),t&&!e&&s){colwizOptions.appId;this.loadJs(0),this.addCSS("css/"+window._colwizStylesPath_["webpdf/button-web.css"])}}catch(t){this.initErrors.push(t)}},t.prototype.loadJs=function(t){var e=e||{};try{if(t<this.js.length)
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/jDialog.js

@@ -1,0 +1,1 @@
+var dialogHTML={shareDialog:'<div id="dlgFileShare"><table class="cmsg" cellpadding="0" cellspacing="0"><tr><td style="width:80px;">Share with:</td><td><div id="shareFile"><div class="inputBox"><div class="shareToBox"><input id="shareTo" class="dialogShareRecipient" type="text" value="" style="width: 100%;"/></div></div></div></td></tr><tr><td colspan="2" style="display:none" class="shareToUsers"><ul class="users"><dt class="hidden"><li class="last"><span class="name">&#160;</span><a class="cw-btn removercpt" data-action="close" href="javascript:void(0);" cw-title="Close">x</a></li></dt></ul></td></tr></table></div>'};function jDialog(i,t){this.name=i;var e="",a="",n="OK",o="Cancel",l=[];this.cached=!0,null!=t.cached&&(this.cached=t.cached),this.setNavItems=function(i){null!=i&&(l=i)},this.getNavItems=function(){return l},this.setContentHtml=function(i){null!=i&&(a=i,CwZ("#"+this.name+"_dialog .dialogContent").html(i))},this.getContentHtml=function(){return a},this.setTitle=function(i){null!=i&&(e=i,CwZ("#"+this.name+"_dialog .dialogTitle h2").html(i))},this.getTitle=function(){return e},this.setSubTitle=function(i){null!=i&&(e=i,this.removeSubTitle(),CwZ("#"+this.name+"_dialog .dialogTitle h2").after("<p>"+i+"</p>"))},this.removeSubTitle=function(){CwZ("#"+this.name+"_dialog .dialogTitle h2").next("p").remove()},this.setOkLabel=function(i){null!=i&&(n=i,CwZ("#"+this.name+"_dialog .dialogOk").html(i))},this.getOkLabel=function(){return n},this.setCancelLabel=function(i){null!=i&&(o=i,CwZ("#"+this.name+"_dialog .dialogCancel").html(i))},this.getCancelLabel=function(){return o},this.bindOnOkEvent=function(i){if(null!=i){CwZ("#"+this.name+"_dialog .dialogOk").off("click").on("click",function(){i()})}},this.bindOnCancelEvent=function(i){if(null!=i){var t=this;CwZ("#"+this.name+"_dialog .dialogCancel").off("click").on("click",functi
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/jDialogFunc.js

@@ -1,0 +1,1 @@
+var shareDialog={isInitialized:!1,sendToList:{},selectedPublication:null,pubId:null,cmnts:!1,sharedUsersList:[],emailRegex:/(?:[a-z0-9!#CwZ%&'*+\/=?^_`{|}~-]+(?:\.[a-z0-9!#CwZ%&'*+\/=?^_`{|}~-]+)*|"(?:[\x01-\x08\x0b\x0c\x0e-\x1f\x21\x23-\x5b\x5d-\x7f]|\\[\x01-\x09\x0b\x0c\x0e-\x7f])*")@(?:(?:[a-z0-9](?:[a-z0-9-]*[a-z0-9])?\.)+[a-z0-9](?:[a-z0-9-]*[a-z0-9])?|\[(?:(?:25[0-5]|2[0-4][0-9]|[01]?[0-9][0-9]?)\.){3}(?:25[0-5]|2[0-4][0-9]|[01]?[0-9][0-9]?|[a-z0-9-]*[a-z0-9]:(?:[\x01-\x08\x0b\x0c\x0e-\x1f\x21-\x5a\x53-\x7f]|\\[\x01-\x09\x0b\x0c\x0e-\x7f])+)\])/gi,addItem:function(e,a,t){function i(){$(".dialogShareRecipient").val("").trigger("focus"),shareDialog.hideUsers()}if(void 0===t&&(t=!0),null==e&&(e=""),e=XmL.escapeXml(e),-1==a&&(a=e.toLowerCase()),a==CWDataCenter.userEmail){var s={msg:"Sharing on your own email is not allowed, please enter valid email address.",onOk:function(){i()}};CWPDFReaderDialog.show(s)}else if(void 0===shareDialog.sendToList[a]){var n=CwZ(".shareToUsers dt li").clone(!0).insertBefore("dt.hidden").removeClass("last").find(".name").text(e).attr("data-id",a);t&&n.end().find(".allowed-rights").val(t),CwZ(".shareToUsers").show(),shareDialog.sendToList[a]=e}setTimeout(function(){i()},1)},initDialog:function(){var e=CwZ(".dialogShareRecipient");shareDialog.isInitialized=!0,e.autocomplete({appendTo:"#dialogCurtain",source:function(e,a){var t=e.term.toLocaleLowerCase();UaC.getAutocompleteRecords({query:t,et:["101","161"],onComplete:a,length:5,sender:"shareDialog"})},minLength:1,autoFocus:!0,select:function(e,
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/jquery_ireader.js

@@ -1,0 +1,1 @@
+var oldJQ=null,jQueryInc=!1;"undefined"!=typeof jQuery&&(jQueryInc=!0,oldJQ=jQuery),function(e,t){"use strict";"object"==typeof module&&"object"==typeof module.exports?module.exports=e.document?t(e,!0):function(e){if(!e.document)throw new Error("jQuery requires a window with a document");return t(e)}:t(e)}("undefined"!=typeof window?window:this,function(C,e){"use strict";var t=[],T=C.document,i=Object.getPrototypeOf,a=t.slice,g=t.concat,l=t.push,o=t.indexOf,n={},r=n.toString,m=n.hasOwnProperty,s=m.toString,u=s.call(Object),v={},y=function(e){return"function"==typeof e&&"number"!=typeof e.nodeType},b=function(e){return null!=e&&e===e.window},c={type:!0,src:!0,noModule:!0};function x(e,t,n){t=t||T;var i,o=t.createElement("script");if(o.text=e,n)for(i in c)n[i]&&(o[i]=n[i]);t.head.appendChild(o).parentNode.removeChild(o)}function w(e){return null==e?e+"":"object"==typeof e||"function"==typeof e?n[r.call(e)]||"object":typeof e}var f="3.3.1",E=function(e,t){return new E.fn.init(e,t)},h=/^[\s\uFEFF\xA0]+|[\s\uFEFF\xA0]+$/g;function d(e){var t=!!e&&"length"in e&&e.length,n=w(e);return!y(e)&&!b(e)&&("array"===n||0===t||"number"==typeof t&&0<t&&t-1 in e)}E.fn=E.prototype={jquery:f,constructor:E,length:0,toArray:function(){return a.call(this)},get:function(e){return null==e?a.call(this):e<0?this[e+this.length]:this[e]},pushStack:function(e){var t=E.merge(this.constructor(),e);return t.prevObject=this,t},each:function(e){return E.each(this,e)},map:function(n){return this.pushStack(E.map(this,function(e,t){return n.call(e,t,e)}))},slice:function(){return this.pushStack(a.apply(this,arguments))},first:function(){return this.eq(0)},last:function(){return this.eq(-1)}
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/pdf_find_controller.js

@@ -1,0 +1,1 @@
+"use strict";var PDFFindController={matchCount:0,startedTextExtraction:!1,extractTextPromises:[],pendingFindMatches:{},active:!1,pageContents:[],pageMatches:[],selected:{pageIdx:-1,matchIdx:-1},offset:{pageIdx:null,matchIdx:null},resumePageIdx:null,resumeCallback:null,state:null,dirtyMatch:!1,findTimeout:null,initialize:function(t){var e=["find","findagain","findhighlightallchange","findcasesensitivitychange"];this.firstPagePromise=new Promise(function(t){this.resolveFirstPage=t}.bind(this)),this.handleEvent=this.handleEvent.bind(this);for(var a=0;a<e.length;a++)window.addEventListener(e[a],this.handleEvent)},reset:function(){this.startedTextExtraction=!1,this.extractTextPromises=[],this.active=!1},calcFindMatch:function(t){var e=this.pageContents[t],a=this.state.query,s=this.state.caseSensitive,i=a.length;if(0!==i){s||(e=e.toLowerCase(),a=a.toLowerCase());for(var h=[],n=-i;n=e.indexOf(a,n+i),-1!==n;)h.push(n);this.pageMatches[t]=h,this.updatePage(t),this.resumePageIdx===t&&(this.resumePageIdx=null,this.nextPageMatch()),0<h.length&&(this.matchCount+=h.length,CWUtils.log("Match found: "+this.matchCount))}},extractText:function(){if(!this.startedTextExtraction){this.startedTextExtraction=!0,this.pageContents=[];for(var n=[],t=0,e=CWPDFManager.pdf.numPages;t<e;t++)this.extractTextPromises.push(new Promise(function(t){n.push(t)}));var r=this;!function i(h){CWPageManager.pages[h].getTextContent().then(function(t){for(var e=t.items,a="",s=0;s<e.length;s++)" "!=e[s].str[e[s].str.length-1]&&s<e.length-1&&e[s].transform[5]!=e[s+1].transform[5]?a+=e[s].str+" ":a+=e[s].str;r.pageContents.push(a),n[h](h),h+1<CWPageManager.pages.length&&i(h+1)})}(0)}},handleEvent:function(t){null!==this.state&&"findagain"===t.type||(this.dirtyMatch=!0),0<CwZ("#cw-searchTab").length&&0<CwZ("#cw-sear
[…]

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/svgicon.e8fcd135a74ca5b73898.js

@@ -1,0 +1,2 @@
+!function(e){function n(t){if(o[t])return o[t].exports;var r=o[t]={i:t,l:!1,exports:{}};return e[t].call(r.exports,r,r.exports,n),r.l=!0,r.exports}var o={};n.m=e,n.c=o,n.d=function(e,o,t){n.o(e,o)||Object.defineProperty(e,o,{configurable:!1,enumerable:!0,get:t})},n.n=function(e){var o=e&&e.__esModule?function(){return e.default}:function(){return e};return n.d(o,"a",o),o},n.o=function(e,n){return Object.prototype.hasOwnProperty.call(e,n)},n.p="https://cdn.wizdom.ai/assets/",n(n.s=5)}({0:function(e,n){var o=function(e){var n=!1,o=void 0;if(e&&e.filename&&(n=e.filename),!n)return!1;var t,r=new XMLHttpRequest;"undefined"!=typeof XDomainRequest&&(r=new XDomainRequest),void 0===o&&(o=void 0!==window.baseUrl?window.baseUrl:window.location.protocol+"//"+window.location.hostname+(window.location.port?":"+window.location.port:"")),t=/^https?:\/\//g.test(n)?n:(o+"/"+n).replace(/([^:]\/)\/+/g,"$1"),r.open("GET",t,!0),r.onprogress=function(){},r.onload=function(){if(!r.responseText||"<svg"!==r.responseText.substr(0,4))throw Error("Invalid SVG Response");if(!(r.status<200||r.status>=300)){var e=document.createElement("div");e.className="visuallyhidden",e.innerHTML=r.responseText,document.body.insertBefore(e,document.body.childNodes[0])}},r.send()};e.exports=o},5:function(e,n,o){var t={filename:o.p+"images/web/home/svgicons.1554292332908.svg"};o(0)(t)}});
+//# sourceMappingURL=../../../../sourcemaps/js/web/home/svgicon.e8fcd135a74ca5b73898.js.map

### 2019-04-05 papers/Mixtures of g Priors for Bayesian Variable Selection_ Journal of the American Statistical Association_ Vol 103, No 481_files/wdom.js

@@ -1,0 +1,1304 @@
+"use strict";
+
+var _this = void 0;
+
+function _objectSpread(target) { for (var i = 1; i < arguments.length; i++) { var source = arguments[i] != null ? arguments[i] : {}; var ownKeys = Object.keys(source); if (typeof Object.getOwnPropertySymbols === 'function') { ownKeys = ownKeys.concat(Object.getOwnPropertySymbols(source).filter(function (sym) { return Object.getOwnPropertyDescriptor(source, sym).enumerable; })); } ownKeys.forEach(function (key) { _defineProperty(target, key, source[key]); }); } return target; }
+
+function _defineProperty(obj, key, value) { if (key in obj) { Object.defineProperty(obj, key, { value: value, enumerable: true, configurable: true, writable: true }); } else { obj[key] = value; } return obj; }
+
+function _typeof(obj) { if (typeof Symbol === "function" && typeof Symbol.iterator === "symbol") { _typeof = function _typeof(obj) { return typeof obj; }; } else { _typeof = function _typeof(obj) { return obj && typeof Symbol === "function" && obj.constructor === Symbol && obj !== Symbol.prototype ? "symbol" : typeof obj; }; } return _typeof(obj); }
+
+var wdom = {
+  loadScript: function loadScript(src) {
+    var ver = arguments.length > 1 && arguments[1] !== undefined ? arguments[1] : Date.now();
+    var onload = arguments.length > 2 && arguments[2] !== undefined ? arguments[2] : wdom.noop;
+    return document.head.appendChild(wdom.createScript(src, ver, onload));
+  },
+  createScript: function createScript(src) {
+    var ver = arguments.length > 1 && arguments[1] !== undefined ? arguments[1] : Date.now();
+    var onload = arguments.length > 2 && arguments[2] !== undefined ? arguments[2] : wdom.noop;
+    var async = arguments.length > 3 ? arguments[3] : undefined;
+    var defer = arguments.length > 4 ? arguments[4] : undefined;
+    var id = arguments.length > 5 && arguments[5] !== undefined ? arguments[5] : '';
+    if (id && document.getElementById(id) != null) return;
+    var script = document.createElement('script');
+    script.type = "text/javascript";
+    script.innerHTML = '';
+    script.src = src + (ver != null ? '?v=' + ver : '');
+    script.onload = onload;
+    script.async = async;
+    script.defer = defer;
+    if (id) script.id = id;
+    return script;
[…]

### 2019-04-05 papers/Spike & Slab paper/Supplementary of The Spike -and-Slab LASSO/SSL.R

@@ -1,0 +1,105 @@
+SSL <- function(X, y, penalty=c("separable","adaptive"),
+                   lambda1, theta=0.5, lambda0, a=1, b=p, eps=.001, max.iter=500, counter=10, approximate=FALSE,
+                   warn=FALSE) {
+  # Coersion
+  penalty <- match.arg(penalty)
+  if (approximate){approximate=1}else{approximate=0}
+  if (missing(approximate)){approximate=0}
+  
+  nlambda <- length(lambda0)
+  if (class(X) != "matrix") {
+    tmp <- try(X <- model.matrix(~0+., data=X), silent=TRUE)
+    if (class(tmp)[1] == "try-error") stop("X must be a matrix or able to be coerced to a matrix")
+  }
+  if (storage.mode(X)=="integer") storage.mode(X) <- "double"
+  if (class(y) != "numeric") {
+    tmp <- try(y <- as.numeric(y), silent=TRUE)
+    if (class(tmp)[1] == "try-error") stop("y must numeric or able to be coerced to numeric")
+  }
+
+ 
+  # Lambda0 should be an increasing sequence
+
+  monotone<-sum((lambda0[-1]-lambda0[-nlambda])>0)
+  if (monotone!=nlambda-1){stop("lambda0 must be a monotone increasing sequence")}
+
+
+
+  # Error checking
+  standardize <- TRUE
+
+  if (lambda1 > min(lambda0) ) stop("lambda1 must be smaller than lambda0")
+  if (any(is.na(y)) | any(is.na(X))) stop("Missing data (NA's) detected.  Take actions (e.g., removing cases, removing features, imputation) to eliminate missing data before passing X and y to ncvreg")
+
+ 
+  ## Set up XX, yy, lambda
+  if (standardize) {
+    std <- .Call("standardize", X)
+    XX <- std[[1]]
+    center <- std[[2]]
+    scale <- std[[3]]
+    nz <- which(scale > 1e-6)
+    if (length(nz) != ncol(XX)) XX <- XX[ ,nz, drop=FALSE]    
+  } else {
+    XX <- X
+  }
+  p <- ncol(XX)
+
+  yy <- y - mean(y)
+
+  n <- length(yy)
+ 
+
+  ## Fit
+  if (standardize==TRUE) {
+    res <- .Call("SSL_gaussian", XX, yy, penalty, lambda0, eps, as.integer(max.iter), as.double(lambda1), as.double(theta), as.integer(counter),
+                 as.integer(approximate), as.double(a), as.double(b))
[…]

### 2019-04-05 papers/Spike & Slab paper/Supplementary of The Spike -and-Slab LASSO/SSL.c

@@ -1,0 +1,227 @@
+#include <math.h>
+#include <string.h>
+#include "Rinternals.h"
+#include "R_ext/Rdynload.h"
+#include <R.h>
+#include <R_ext/Applic.h>
+
+
+#include <stdio.h>
+
+
+
+SEXP SSL_gaussian(SEXP X_, SEXP y_, SEXP penalty_, SEXP lambda0s_, SEXP eps_, SEXP max_iter_, SEXP lambda1_, SEXP theta_);
+
+SEXP standardize(SEXP X_);
+
+
+// Cross product of y with jth column of X
+double crossprod(double *X, double *y, int n, int j) {
+
+  int nn = n*j;
+
+  double val=0;
+
+  for (int i=0;i<n;i++) val += X[nn+i]*y[i];
+
+  return(val);
+}
+
+
+
+// Sum of squares of jth column of X
+double sqsum(double *X, int n, int j) {
+
+  int nn = n*j;
+
+  double val=0;
+
+  for (int i=0;i<n;i++) val += pow(X[nn+i], 2);
+
+  return(val);
+
+}
+
+double sum(double *x, int n) {
+
+  double val=0;
+
+  for (int i=0;i<n;i++) val += x[i];
+
+  return(val);
+}
+
+int checkConvergence(double *beta, double *beta_old, double eps, int l, int J) {
+
+  int converged = 1;
+
+  for (int j=0; j<J; j++) {
+
+    if (fabs((beta[l*J+j]-beta_old[j])/beta_old[j]) > eps) {
+
+      converged = 0;
+
+      break;
+
+    }
+
+  }
+
+  return(converged);
+}
+
+
+double pstar(double x, double theta, double lambda1, double lambda0){
+
+  double value;
+
+  if (lambda1==lambda0){return 1;} else{
+
+  value=(1-theta)/theta*lambda0/lambda1*exp(-fabs(x)*(lambda0-lambda1));
+
+  value+=1;
+
+  value=1/value;
+
+  return value;}
+
+
+}
+
+
+
+
+double expectation_approx(double *beta, double a, double b, int p, int l){
+
+  int sum=0;
+
+  int i;
+  
+  for (i=0;i<p;i++){
+    
+    if(beta[l*p+i]!=0){sum++;}
+  
+  } 
+
+  return (sum+a)/(a+b+p);
+
+}
+
+
+
+
+double lambdastar(double x, double theta, double lambda1, double lambda0){
+
[…]

### 2019-04-05 papers/Spike & Slab paper/Supplementary of The Spike -and-Slab LASSO/SSL_gaussian.c

@@ -1,0 +1,378 @@
+/* 
+
+Compilation:
+
+sudo rm -r SSL2
+
+cp -r /Users/rockova/Desktop/SSL2  /Library/Frameworks/R.framework/Versions/3.1/Resources/library/SSL2
+
+R CMD build /Library/Frameworks/R.framework/Versions/3.1/Resources/library/SSL2
+
+sudo  R CMD install /Library/Frameworks/R.framework/Versions/3.1/Resources/library/SSL_0.0-1.tar.gz
+
+*/
+
+
+
+
+#include <math.h>
+#include <string.h>
+#include "Rinternals.h"
+#include "R_ext/Rdynload.h"
+#include <R.h>
+#include <R_ext/Applic.h>
+
+double crossprod(double *X, double *y, int n, int j);
+
+double sum(double *x, int n);
+
+int checkConvergence(double *beta, double *beta_old, double eps, int l, int J);
+
+double SSL(double z, double beta, double lambda0, double lambda1, double theta, double v, int n, double delta);
+
+double pstar(double x, double theta, double lambda1, double lambda0);
+
+double lambdastar(double x, double theta, double lambda1, double lambda0);
+
+double expectation_approx(double *beta, double a, double b, int p, int l);
+
+double threshold(double theta, double lambda1, double lambda0, int n, int approximate);
+
+// Memory handling, output formatting (Gaussian)
+
+SEXP cleanupG(double *a, double *r, int *e1, int *e2, double *z, double *thetas, SEXP beta, SEXP loss, SEXP iter, SEXP thetas_export) {
+
+  Free(a);
+
+  Free(r);
+
+  Free(e1);
+
+  Free(e2);
+
+  Free(z);
+
+  SEXP res;
+
+  PROTECT(res = allocVector(VECSXP, 4));
+
+  SET_VECTOR_ELT(res, 0, beta);
+
+  SET_VECTOR_ELT(res, 1, loss);
+
+  SET_VECTOR_ELT(res, 2, iter);
+
+  SET_VECTOR_ELT(res, 3, thetas_export);
+
+  UNPROTECT(5);
+
+  return(res);
+}
+
+// Gaussian loss
+double gLoss(double *r, int n) {
+ 
+  double l = 0;
+ 
+  for (int i=0;i<n;i++) l = l + pow(r[i],2);
+ 
[…]

### 2019-04-05 papers/Spike & Slab paper/Supplementary of The Spike -and-Slab LASSO/Simulation_Study.R

@@ -1,0 +1,551 @@
+# SIMULATION STUDY
+
+library(mvtnorm)
+library(SSL)
+library(ncvreg)
+library(monomvn)
+library(EMVS)
+library(sparsenet)
+library(parcor)
+
+
+
+
+
+# ********* Keep track of the following quantities ******** #
+# MSE.... mean squared error
+# FN .... false negatives
+# FP .... false positives
+# TP .... true positives
+# DIM.... dimensionality
+# TRUE... found the true model
+# TIME... execution time
+# HAM ... Hamming distance
+
+
+# ******** Methods compared ******************************* #
+
+# SSL oracle
+# SSL adaptive
+# MCP
+# SCAD
+# LASSO
+# Horseshoe
+# EMVS
+# MCP sparsenet (two-dimensional cross-validation)
+
+# ******** Hyperparameters ******************************* #
+
+p<-1000
+
+n<-100
+
+Sigma<-matrix(0.6,p,p)
+    
+diag(Sigma)<-1
+
+lambda1<-1      # slab penalty for Spike-and-Slab LASSO
+
+lambda0<-seq(lambda1,n,length=100) # slab penalties for Spike-and-Slab LASSO
+
+L<-length(lambda0)
+
+v0<-seq(0.1,5,by=0.1) # spike variance for EMVS
+
+v1<-100          # slab variance for EMVS
+
+burnin<-200 # burnin for the horseshoe
+
+T<-1000     # length of the MCMC chain for the horseshoe
+
+nrep<-100
+
+q<-6
+
+result<-matrix(0,15,8)
+
+for (i in (1:nrep)){
+
+    # Generate data
+
+        X<-(rmvnorm(n,numeric(p),Sigma))
+        
+        index<-c(1,51,101,151,201,251)  # choose location of nonzero entries
+
+        beta<-numeric(p)
+
+        beta[index]<-1/sqrt(3)*c(-2.5,-2,-1.5,1.5,2,2.5) # assign nonzero entries
+
+        model.true<-numeric(p)
+
+        model.true[index]<-1
+
+        Y<-X%*%beta+rnorm(n)
+
+
+        # Oracle Spike-and-Slab LASSO
+
+        time<-system.time(result1<-SSL(X, Y,penalty="separable",lambda=lambda0,lambda1=lambda1,theta=q/p,warn=FALSE))
+
+        model<-result1$model
+
+        beta.est<-result1$beta[,L]
+
+        model.est<-numeric(p)
+
+        model.est[model]<-1
+
+     
[…]

### 2019-04-05 papers/Spike & Slab paper/Supplementary of The Spike -and-Slab LASSO/Simulation_Study2.R

@@ -1,0 +1,556 @@
+# SIMULATION STUDY
+
+library(mvtnorm)
+library(SSL)
+library(ncvreg)
+library(monomvn)
+library(EMVS)
+library(sparsenet)
+library(parcor)
+
+
+
+
+
+# ********* Keep track of the following quantities ******** #
+# MSE.... mean squared error
+# FN .... false negatives
+# FP .... false positives
+# TP .... true positives
+# DIM.... dimensionality
+# TRUE... found the true model
+# TIME... execution time
+# HAM ... Hamming distance
+
+
+# ******** Methods compared ******************************* #
+
+# SSL oracle
+# SSL adaptive
+# MCP
+# SCAD
+# LASSO
+# Horseshoe
+# EMVS
+# MCP sparsenet (two-dimensional cross-validation)
+
+# ******** Hyperparameters ******************************* #
+
+p<-1000
+
+n<-100
+
+block<-matrix(0.9,50,50)
+
+
+Sigma<-diag(20)%x%block
+
+diag(Sigma)<-1
+
+lambda1<-1      # slab penalty for Spike-and-Slab LASSO
+
+lambda0<-seq(lambda1,n,length=100) # slab penalties for Spike-and-Slab LASSO
+
+L<-length(lambda0)
+
+v0<-seq(0.1,5,by=0.1) # spike variance for EMVS
+
+v1<-100          # slab variance for EMVS
+
+burnin<-200 # burnin for the horseshoe
+
+T<-1000     # length of the MCMC chain for the horseshoe
+
+nrep<-100
+
+q<-6
+
+result<-matrix(0,15,8)
+
+for (i in (1:nrep)){
+
+    # Generate data
+
+        X<-(rmvnorm(n,numeric(p),Sigma))
+        
+        index<-c(1,51,101,151,201,251)  # choose  location of nonzero entries
+
+        beta<-numeric(p)
+
+        beta[index]<-1/sqrt(3)*c(-2.5,-2,-1.5,1.5,2,2.5) # assign nonzero entries
+
+        model.true<-numeric(p)
+
+        model.true[index]<-1
+
+        Y<-X%*%beta+rnorm(n)
+
+
+        # Oracle Spike-and-Slab LASSO
+
+        time<-system.time(result1<-SSL(X, Y,penalty="separable",lambda=lambda0,lambda1=lambda1,theta=q/p,warn=FALSE))
+
+        model<-result1$model
+
[…]

### 2019-04-05 papers/Spike & Slab paper/Supplementary of The Spike -and-Slab LASSO/plot.SSL.R

@@ -1,0 +1,32 @@
+
+plot.SSL<-function(result){
+
+	betas <-t(result$beta)
+        
+     	v0s <-result$lambda0
+
+        select <-apply(betas,2,function(x){as.numeric(x!=0)})
+
+        matplot(v0s,betas,xlab=expression(lambda[0]),ylab=expression(hat(beta)),lwd=1,col="grey",lty=2,type="l")
+
+        betas[select==F]=NA
+
+        matpoints(v0s,betas*select,xlab=expression(lambda[0]),ylab=expression(hat(beta)),lwd=1,col=4,lty=2,pch=19)
+
+        matpoints(v0s,betas*(1-select),xlab=expression(lambda[0]),ylab=expression(hat(beta)),lwd=1,col=2,lty=2,pch=19)
+
+        title("Spike-and-Slab LASSO")
+
+        par(xpd=T)
+
+        labels=paste("X",1:ncol(betas),sep="")
+
+        labels[select[length(v0s),]==0]<-""
+
+        text(max(v0s)*(1.1),betas[length(v0s),],labels=labels,col=4)
+    	
+
+
+}
+
+

### 2019-04-10 Manuscript/Jin/Project2.tex
[1]. we change the tau into (log(p))^2 for the simulation study. [2]. I insert into hybrid part the temperature idea borrowed from simulated annealing alrogithm [3]. For the real data analysis, we consistently use that tau and temperature idea, and sceen out 500 genes, with mcsize 5000 to select genes related BRCA1.

@@
 i&Proposed & 0.016 (0.001) & 92.600 (0.585)& 4.087 (0.007) & 0.087 (0.007) \\ 
+&\textcolor{red}{local(new)}& 0.01(0.001) & 96.90 (0.388) & 4.03  (0.004) & 0.03 (0.004) \\
+&\textcolor{red}{Proposed(new)} & 0.006 (0.001)& 96.900 (0.388) & 4.032(0.004) & 0.032 (0.004) \\
     &SCAD & 0.034 (0.002) &  85.200 (0.794) & 4.188 (0.011) & 0.188 (0.011)\\ 
@@
     ii&Proposed & 0.030 (0.002) & 86.250 (0.770) & 4.034 (0.007) & 0.236 (0.014)   \\
+    &\textcolor{red}{local(new)}& 0.03  (0.002) &  86.15  (0.773) & 3.99 (0.007) & 0.25  (0.015)\\
+    &\textcolor{red}{Proposed(new)}& 0.023  (0.002) & 88.750  (0.707) & 3.985  (0.006) & 0.203 (0.014) \\
 &SCAD & 0.059 (0.003) & 74.150 (0.979) & 4.107 (0.015) & 0.480 (0.022) \\ 
@@
     iii&Proposed&0.014 (0.001) & 93.450 (0.553) & 4.073 (0.007) & 0.073 (0.007)\\
+    &\textcolor{red}{local(new)}& 0.00  (0.001)  & 98.10  (0.305) & 4.02  (0.003)& 0.02(0.003)\\
+    &\textcolor{red}{Proposed(new)} & 0.004(0.001)& 98.100 (0.305) & 4.020(0.003) & 0.020 (0.003) \\ 
 &SCAD & 0.027 (0.002) & 87.900 (0.729) & 4.145 (0.010) & 0.145 (0.010) \\ 
@@
     iv&Proposed&0.032 (0.002) & 86.700 (0.759) & 4.051 (0.007) & 0.236 (0.015) \\
+    &\textcolor{red}{local(new)}& 0.04  (0.002)  & 85.30  (0.792) & 4.02  (0.006) & 0.28  (0.016) \\ 
+     &\textcolor{red}{Proposed(new)}& 0.023(0.002)& 89.850 (0.675) & 4.005  (0.005 )& 0.190 (0.013) \\ 
 &SCAD & 0.068 (0.003) & 74.250 (0.978) & 4.196 (0.014) & 0.493 (0.023) \\ 

### 2019-04-10 Rcode/BRCA_analysis.R

@@ -10,222 +10,114 @@ rm(list=ls())
 ###################
 # Data processing #
 ###################
-load('~/Dropbox/Goh/BRCA.RData')
-#load('~/BRCA.RData')
+# load('~/Dropbox/Goh/BRCA.RData')
+load('~/BRCA.RData')
 ## data processing
 BRCA.stu <- scale(BRCA,center = TRUE, scale = TRUE)
 name.genes <- colnames(BRCA)
 ham.genes <- c('BRCA2','NBR1','NBR2','XRCC2',
                'ATM','CHEK2','BRIP1','PALB2','RAD51C',
-               'CDH1','TP53')
+               'CDH1','TP53','LDLRAD1', 'SLC19A1', 
+               'FGFBP3', 'CASP5', 'MMAB', 'SLC16A6',
+               'NBS1','RAD50','RAD51D','BARD1',
+               'CASP8', 'CTLA4', 'CYP19A1', 'FGFR2',
+               'H19', 'LSP1', 'MAP3K1', 'MRE11A',
+               'NBN', 'RAD51','TERT','MSH6','PMS2',
+               'SEC23B','NF1')
 BRCA1 <- which(name.genes=='BRCA1')
 y1 <- BRCA.stu[,BRCA1]
-X1 <- BRCA.stu[,-BRCA1]
+X0 <- BRCA.stu[,-BRCA1]
 name.genes <- name.genes[-BRCA1] # update symbols of genes. 
-ham.vars <- name.genes%in%ham.genes
-lm.ham.gene <- lm(y1~X1[,ham.vars]-1)
-p = dim(X1)[2]
+mcsize = 1000
+p=5000
+abs.cor <- abs(cor(y1,X0))
+g=sort(abs.cor,decreasing = TRUE)[p]
+X1 <- X0[,which(abs.cor>=g)]
+name.genes.X1 <- colnames(X1)
+sum(ham.genes%in%name.genes.X1)
 n = length(y1)
-rep0 <- rep(0,p)
-ksi <- 1.01-0.5*log(n)/log(p)
-set.seed(1314)
-g.tau <- function(tau0) {
-  SVD <- svd(X.r.star)
-  d.j <- as.vector(SVD$d)
-  z.j <- as.vector(t(SVD$u)%*%y1)
[…]

### 2019-04-10 Rcode/Proposed.R

@@ -1,0 +1,310 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-200
+rho0 <- 0.9
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+localvshy <- rep(0,REP)
+tau = (log(p))^2
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+  ###############################
+  #Step 1: Set initial values
+  ###############################
+  beta.ini= as.numeric(cor(y1,X1))/diag(var(X1))
+  marginal.FNVS <- rep(NA,k0)
+  marginal.hy <- rep(NA,k0)
+  G1.hy <- list()
+  tXX <-  crossprod(X1)
+  d.tXX<-diag(tXX)
+  sum.y2<-sum(y1^2)
+  tXy<-t(X1)%*%y1
+  t1 = Sys.time()
+  #################################
+  ##BEGIN: Bounded subset size
+  #################################
+  for (k in 1:k0) { #For loop for k<=k0
+    #k<-1
+    # tau=choose(p,k)^(2/k)
[…]

### 2019-04-10 Rcode/local.R

@@ -1,0 +1,188 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-1000
+rho0 <- 0.1
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Sig<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+Sig2<-1 # variance for y1
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+tau = (log(p))^2
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2))
+  ###############################
+  #Step 1: Set initial values
+  ###############################
+  beta.ini= as.numeric(cor(y1,X1))/diag(var(X1))
+  marginal.FNVS <- rep(NA,k0)
+  marginal.hy <- rep(NA,k0)
+  G1.hy <- list()
+  tXX <-  crossprod(X1)
+  d.tXX<-diag(tXX)
+  sum.y2<-sum(y1^2)
+  tXy<-t(X1)%*%y1
+  t1 = Sys.time()
+  #################################
+  ##BEGIN: Bounded subset size
+  #################################
+  for (k in 1:k0) { #For loop for k<=k0
+    #k<-1
+    I_k <- diag(1,k)
+    I_k1 <- diag(1,k+1)
[…]

### 2019-04-22 Manuscript/Jin/Project2.tex
set tau = log(p)^2

--- 2019-04-05 Manuscript/Jin/Project2.tex
@@
 Therefore, if this case does not occur for sufficiently large $t$, we can treat $\hat{\bg}$ as the global maximum.
-
+\textcolor{blue}{However, this global maximum is unefficient because it require large enough $t$.
+To improve the efficiency of global search, We applied the idea from Simulated Annealing to Algorithm \ref{alg:2}:
+\begin{itemize}
+ \item[1.] Given $\bg^*$, generate $\ueta^*$ with probability,
+       $$\pi(\ueta|\uy,\bg^*)=\frac{\tilde{m}(\uy|\ueta)}{\sum_{\ueta \in \mathcal{N}_+(\bg^* )  } \tilde{m}(\uy|\ueta) }\mathbb{I}\{\ueta \in \mathcal{N}_+(\bg^* ) \},$$ where $\tilde{m}(\uy|\ueta)=\exp\{\frac{1}{\alpha}\log(m(\uy|\ueta)))\}.$ \\
+ \item[2.] Given $\ueta^*$, generate $\bg^*$ with probability
+       $$\pi(\bg|\uy,\ueta^*)=\frac{\tilde{m}(\uy|\bg)}{\sum_{\bg \in \mathcal{N}_-({\ueta}^* )  } \tilde{m}(\uy|\bg) }\mathbb{I}\{\bg \in \mathcal{N}_-({\ueta}^* )  \},$$ where $\tilde{m}(\uy|\bg)=\exp\{\frac{1}{\alpha}\log(m(\uy|\bg))\}.$
+\end{itemize}
+}
 \begin{algorithm}[ht]
@@
          \item[] Update $\tilde{\bg}\leftarrow  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\ueta} ) } m(\uy|\bg,\tilde{\tau});$
-\item[] Update $\tilde{\tau} \leftarrow \arg\min_{\tau \in (0,\infty)}Q(\tau|\tilde{\bg})$;
         \end{itemize}
@@
   \hline
-    Scenario&Method&FDR  (s.e.) & TRUE\% (s.e.) & SIZE (s.e.) & HAM (s.e.)  \\
+  Scenario & Method                         & FDR  (s.e.)    & TRUE\% (s.e.)   & SIZE (s.e.)     & HAM (s.e.)    \\
   \hline
-i&Proposed & 0.016 (0.001) & 92.600 (0.585)& 4.087 (0.007) & 0.087 (0.007) \\ 
-    &SCAD & 0.034 (0.002) &  85.200 (0.794) & 4.188 (0.011) & 0.188 (0.011)\\ 
-   &MCP & 0.035 (0.002) & 84.750 (0.804) & 4.191 (0.011) & 0.191 (0.011)\\ 
-  &ENET & 0.016 (0.001) & 92.700 (0.582) & 4.087 (0.007) & 0.087 (0.007)\\ 
-  &LASSO & 0.020 (0.002) & 91.350 (0.629) & 4.109 (0.009) & 0.109 (0.009)\\
+  i        & Proposed                       & 0.016 (0.001)  & 92.600 (0.585)  & 4.087 (0.007)   & 0.087 (0.007) \\
+           & \textcolor{red}{local(new)}    & 0.01(0.001)    & 96.90 (0.388)   & 4.03  (0.004)   & 0.03 (0.004)  \\
+           & \textcolor{red}{Proposed(new)} & 0.006 (0.001)  & 96.900 (0.388)  & 4.032(0.004)    & 0.032 (0.004) \\
+           & SCAD                           & 0.034 (0.002)  & 85.200 (0.794)  & 4.188 (0.011)   & 0.188 (0.011) \\
+           & MCP                            & 0.035 (0.002)  & 84.750 (0.804)  & 4.191 (0.011)   & 0.191 (0.011) \\
+           & ENET                           & 0.016 (0.001)  & 92.700 (0.582)  & 4.087 (0.007)   & 0.087 (0.007) \\
+           & LASSO                          & 0.020 (0.002)  & 91.350 (0.629)  & 4.109 (0.009)   & 0.109 (0.009) \\
   \hline
-    ii&Proposed & 0.030 (0.002) & 86.250 (0.770) & 4.034 (0.007) & 0.236 (0.014)   \\
-&SCAD & 0.059 (0.003) & 74.150 (0.979) & 4.107 (0.015) & 0.480 (0.022) \\ 
-  &MCP & 0.137 (0.004) & 55.400 (1.112) & 4.264 (0.020) & 1.098 (0.034) \\ 
-  &ENET & 0.501 (0.004) & 0.300 (0.122) & 7.716 (0.072) & 5.018 (0.052) \\ 
-  &LASSO & 0.276 (0.004) & 15.550 (0.811) & 5.308 (0.033) & 2.038 (0.034) \\ 
+  ii       & Proposed                       & 0.030 (0.002)  & 86.250 (0.770)  & 4.034 (0.007)   & 0.236 (0.014) \\
+           & \textcolor{red}{local(new)}    & 0.03  (0.002)  & 86.15  (0.773)  & 3.99 (0.007)    & 0.25  (0.015) \\
+           & \textcolor{red}{Proposed(new)} & 0.023  (0.002) & 88.750  (0.707) & 3.985  (0.006)  & 0.203 (0.014) \\
+           & SCAD                           & 0.059 (0.003)  & 74.150 (0.979)  & 4.107 (0.015)   & 0.480 (0.022) \\
+           & MCP                            & 0.137 (0.004)  & 55.400 (1.112)  & 4.264 (0.020)   & 1.098 (0.034) \\
+           & ENET                           & 0.501 (0.004)  & 0.300 (0.122)   & 7.716 (0.072)   & 5.018 (0.052) \\
+           & LASSO                          & 0.276 (0.004)  & 15.550 (0.811)  & 5.308 (0.033)   & 2.038 (0.034) \\
   \hline
-    iii&Proposed&0.014 (0.001) & 93.450 (0.553) & 4.073 (0.007) & 0.073 (0.007)\\
-&SCAD & 0.027 (0.002) & 87.900 (0.729) & 4.145 (0.010) & 0.145 (0.010) \\ 
-  &MCP & 0.031 (0.002) & 86.550 (0.763) & 4.172 (0.013) & 0.172 (0.013) \\ 
-  &ENET & 0.035 (0.002) & 84.850 (0.802) & 4.181 (0.013) & 0.206 (0.012) \\ 
-  &LASSO & 0.014 (0.001) & 93.850 (0.537) & 4.073 (0.007) & 0.073 (0.007) \\ 
+  iii      & Proposed                       & 0.014 (0.001)  & 93.450 (0.553)  & 4.073 (0.007)   & 0.073 (0.007) \\
+           & \textcolor{red}{local(new)}    & 0.00  (0.001)  & 98.10  (0.305)  & 4.02  (0.003)   & 0.02(0.003)   \\
+           & \textcolor{red}{Proposed(new)} & 0.004(0.001)   & 98.100 (0.305)  & 4.020(0.003)    & 0.020 (0.003) \\
+           & SCAD                           & 0.027 (0.002)  & 87.900 (0.729)  & 4.145 (0.010)   & 0.145 (0.010) \\
+           & MCP                            & 0.031 (0.002)  & 86.550 (0.763)  & 4.172 (0.013)   & 0.172 (0.013) \\
+           & ENET                           & 0.035 (0.002)  & 84.850 (0.802)  & 4.181 (0.013)   & 0.206 (0.012) \\
+           & LASSO                          & 0.014 (0.001)  & 93.850 (0.537)  & 4.073 (0.007)   & 0.073 (0.007) \\
   \hline
-    iv&Proposed&0.032 (0.002) & 86.700 (0.759) & 4.051 (0.007) & 0.236 (0.015) \\
-&SCAD & 0.068 (0.003) & 74.250 (0.978) & 4.196 (0.014) & 0.493 (0.023) \\ 
-  &MCP & 0.152 (0.004) & 53.750 (1.115) & 4.226 (0.017) & 1.202 (0.035) \\ 
-  &ENET & 0.417 (0.005) & 0.150 (0.087) & 6.228 (0.068) & 4.089 (0.043) \\ 
-  &LASSO & 0.265 (0.004) & 19.500 (0.886) & 5.139 (0.029) & 1.909 (0.035) \\ 
+  iv       & Proposed                       & 0.032 (0.002)  & 86.700 (0.759)  & 4.051 (0.007)   & 0.236 (0.015) \\
+           & \textcolor{red}{local(new)}    & 0.04  (0.002)  & 85.30  (0.792)  & 4.02  (0.006)   & 0.28  (0.016) \\
+           & \textcolor{red}{Proposed(new)} & 0.023(0.002)   & 89.850 (0.675)  & 4.005  (0.005 ) & 0.190 (0.013) \\
+           & SCAD                           & 0.068 (0.003)  & 74.250 (0.978)  & 4.196 (0.014)   & 0.493 (0.023) \\
+           & MCP                            & 0.152 (0.004)  & 53.750 (1.115)  & 4.226 (0.017)   & 1.202 (0.035) \\
+           & ENET                           & 0.417 (0.005)  & 0.150 (0.087)   & 6.228 (0.068)   & 4.089 (0.043) \\
+           & LASSO                          & 0.265 (0.004)  & 19.500 (0.886)  & 5.139 (0.029)   & 1.909 (0.035) \\
   \hline
@@
 
-\section{Real data application}
- In this section, we apply our proposed methods to breast cancer tissue samples from The Cancer Genome Atlas (TCGA) Research Network: \url{http://cancergenome.nih.gov}.
-The dataset "Breast Invasive Carcinoma" (BRCA) we use in this paper is extracted from the R package "curatedTCGAData" and is publicly available and described at \url{http://bioconductor.org/packages/release/data/experiment/html/curatedTCGAData.html}, where includes many other Bioconductor MultiAssayExperiment class objects.
-The data set contains $17814$ gene expression measurements originally.
-After removing missing data, it is left $526$ patients with $17,323$ gene expression measurements (recorded on the log scale).
-BRCA1 is a tumor suppressor gene and its mutations predispose women to breast cancer \citep{findlay2018accurate}.
+\section{Real data example using mRNA gene expression data}
+\subsection{Data and data precessing}
+"Breast Invasive Carcinoma" (BRCA) is mRNA gene expression dataset from the R package "curatedTCGAData" in \citet{Ramos2019}.
+This package provides us with publicly available data from The Cancer Genome Atlas (TCGA) Bioconductor MultiAssayExperiment class objects.
+BRCA dataset comprises $526$ patients with primary solid tumor and $17814$ gene expression measurements, including a gene called BRCA1.
+BRCA1 is a well-known tumor suppressor gene and its mutations predispose women to breast cancer \citep{findlay2018accurate}.
 Our goal here is to identify the best fitting model for estimating an association between BRCA1 (response variable) and the other genes (independent variables).
-We standardize all the variables.
 
+After removing some missing data, we have $n=526$ samples with $17,323$ genes.
+Then it is further screened and normalized and we selected $p=5000$ genes that are most marginally correlated with the response BRCA1 gene expression measurement.
+\subsection{Results}
+In our proposed method, the upper bound of subset size $K=\lceil n^{2/3} \rceil =66$, $\tau=(\log p)^2=72.54$.
+To evaluate the fit of model, we computed the average of prediction MSE, BIC and EBIC under the our proposed method compared with SCAD, MCP, elastic net and LASSO.
+We used cross validation method to randomly split data into $70\%$ training set and remaining part as testing set.
+For selected genes by each method, we fitted the linear model and compute the MSE, BIC and EBIC.
+Repeated this procedure $500$ times and compute the average.
+
+Table \ref{T:realdata} shows our proposed method selects $8$ genes (NSP: number of selected predictors) while others $4$ or $5$.
+In addition, it indicates that our proposed method outperforms other models since it has smallest values of prediction MSE, BIC and EBIC.
+Fig \ref{Fig:heatmap} gives us a heat map of the specific gene's names selected and the magnitude of coefficients estimated by each methods under the linear regression model with the whole data.
+"X" represents non-significance of coefficient.
+
+Fig \ref{Fig:logmarginal} is $\log m(\bg|\uy)$ with $k$ predictors selected by proposed method. It increases to be maximized at when $k=8$ and then decreases all the way down.
 \begin{table}[ht]
  \centering
-\begin{tabular}{rrrrrrr}
+ \caption{Predicion MSE, BIC and EBIC of Proposed method and other methods}\label{T:realdata}
+ \begin{tabular}{rrrrr}
   \hline
- & NSP & MSE\_Pred & MSE\_fit & BIC & EBIC & Detection Rate\\ 
+           & NSP  & MSE\_Pred & BIC     & EBIC    \\
   \hline
-  Local & 31.00 & 0.48 & 0.40 & 738.91 & 1048.20 & 2/11\\ 
-  Grobal & 50.00 & 0.39 & 0.30 & 548.03 & 1015.81 & 1/11\\ 
-  SCAD & 4.00 & 0.69 & 0.67 & 1104.69 & 1154.11 & 1/11\\ 
-  MCP & 4.00 & 0.69 & 0.67 & 1104.69 & 1154.11 & 1/11\\ 
-  ENET & 5.00 & 0.69 & 0.67 & 1110.65 & 1171.30 & 1/11\\ 
-  LASSO & 4.00 & 0.69 & 0.67 & 1104.69 & 1154.11 & 1/11\\ 
+  Proposed & 8.00 & 0.60      & 984.45  & 1099.50 \\
+  SCAD     & 4.00 & 0.68      & 1104.69 & 1166.47 \\
+  MCP      & 4.00 & 0.68      & 1104.69 & 1166.47 \\
+  ENET     & 5.00 & 0.68      & 1110.65 & 1186.25 \\
+  LASSO    & 4.00 & 0.68      & 1104.69 & 1166.47 \\
   \hline
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{Heatmap.pdf}
-  \caption{Heap map}
+ \centering
+ \includegraphics{Heatmap.pdf}
+ \caption{Heap map}\label{Fig:heatmap}
  \label{fig:heatmap}
@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{Log_marginal.pdf}
-  \caption{Logmarginal}
-  \label{fig:Logmarginal}
-\end{figure}
+\section{Comments}
+We have presented a novel approach for best subsets selection, a hybrid algorithm for exploring model spaces via local search and stochastic global search to consider and evaluate thousands of possible predictors simultaneously.
+The ability of identification of model spaces rapidly and accurately will be more practical than some traditional methods, such as MCMC stochastic search, which are inefficient due to high dimensions and high noise data.
+Furthermore, this approach can be applied into multivariate response regression model and binary regression model with logit link and probit link since marginal likelihood of them can be assessed or approximated quickly.
+
+In future, we plan to introduce distributed computing (or parallel computing) to further improve the speed, e.g.
+evaluating best subset for each $k$ by parallel computing.
+Besides, we plan to apply this algorithm into multivariate linear regression model, probit model and then multivariate mixed response regression model so that this model can be used in clinical data with both continuous and binary responses data.
 

### 2019-04-22 Rcode/BRCA_analysis.R

@@ -253,15 +253,14 @@ for (k in 1:k0) { #For loop for k<=k0
   print(sum(name.genes.X1[G1.hy[[k]]]%in%ham.genes))
 } # for (k in 1:k0) ends here
 choice.hy <- G1.hy[[which.max(marginal.hy)]]
-choice.hy.name <- name.genes.X1[choice.hy]
+gene.hy <- name.genes.X1[choice.hy]
 lm.hy <- lm(y1~X1[,choice.hy]-1)
 hat.beta.hy <- rep(0,p)
 hat.beta.hy[choice.hy] <- coef(lm.hy)
 BIC.hy <- BIC(lm.hy) 
 EBIC.hy <- BIC.hy + 2*lchoose(p,length(choice.hy))
-print(choice.hy.name)
-choice.hy.name%in%ham.genes
-
+print(gene.hy)
+gene.hy%in%ham.genes
 
 
 #########################
@@ -290,7 +289,7 @@ hat.beta.LASSO <- rep0
 hat.beta.LASSO[choice.LASSO] <- coef(lm.LASSO)
 BIC.LASSO <- BIC(lm.LASSO)
 EBIC.LASSO <- BIC.LASSO + 2*lchoose(p,length(choice.LASSO))
-name.genes.X1[choice.LASSO]
+gene.LASSO <- name.genes.X1[choice.LASSO]
 ###################################
 #2. SCAD ##########################
 ###################################
@@ -313,7 +312,8 @@ hat.beta.SCAD<- rep0
 hat.beta.SCAD[choice.SCAD] <- coef(lm.SCAD)
 BIC.SCAD <- BIC(lm(y1~X1[,choice.SCAD]-1))
 EBIC.SCAD <- BIC.SCAD + 2*lchoose(p,length(choice.SCAD)) 
-name.genes.X1[choice.SCAD]
+gene.SCAD <- name.genes.X1[choice.SCAD]
+
 ####################################
 #3. MCP ############################
 ####################################
@@ -335,7 +335,7 @@ hat.beta.MCP <- rep0
 hat.beta.MCP[choice.MCP] <- coef(lm.MCP)
 BIC.MCP <- BIC(lm(y1~X1[,choice.MCP]-1))
 EBIC.MCP <- BIC.MCP + 2*lchoose(p,length(choice.MCP)) 
-name.genes.X1[choice.MCP]
+gene.MCP <- name.genes.X1[choice.MCP]
 ###################################
 #4. ENET #########################
[…]

### 2020-02-07 Manuscript/computational statistics/Major_revision_Questions/response_major_revision.Rmd
major revision 1

---
title: "response_major_revision.Rmd"
author: "Shiqiang Jin"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
## First author comment

- 1) In Algorithm 3, the step 5 should be explained more clearly. Here, I am not sure if:
     - 1.1 we draw a single additional element from $N_+$ with some probability P and do not draw any additional element with probability 1-P or
     - 1.2 we draw a single additional parameter from $N_+$ and the probability of selecting a specific element depends on the marginal likelihoods of models with additional elements and alpha.

Probably, the latter case is true (because the former case does not make too much sense) but the authors should explain it more clearly in the paper.

Answer:

- 2) The authors argue that they "establish model selection consistency for the proposed method in the high dimensional setting". However, there is no proof that Algorithm 3 selects the best subset of predictors as $T\rightarrow \infty$.
Contrary, I can think of the situation where the search procedure does not have a chance to select the best subset of predictors. Imagine that we have 6 potential predictors $x_1, x_2, x_3, x_4, x_5, x_6$ where $x_1, x_2, x_3$ are all strongly correlated with the dependent variable y and each predictor in  $\{x_4, x_5, x_6\}$ is only weakly correlated with y, but $x_4+ x_5+ x_6=y$ .  We want to select the best 3 predictors and we start the search algorithm by selecting $x_1, x_2$, and $x_3$ in the first step. Under certain circumstances, the procedure will never have a chance to compute the marginal likelihood of the model containing $x_4, x_5, x_6$ as predictors. If the new algorithm allowed for selecting the subset of "worse" predictors at the end of its stochastic part the problem would disappear.
The inability to select the specific predictors may be a huge problem when a large number of predictors is considered and we want to identify the most significant predictors, as shown in the real data application.  The standard stochastic search algorithms, including the MC3 algorithm, always find the best subset as $T\rightarrow \infty$.

Answer: The stochastic step is a MCMC process, obtaining the limiting distribution as $T\rightarrow \infty$. Then the mode of it is the best subset.
For the second question, we need to run a simulation with this setting to see what's gonna happen. On the other hand, in the real data scenario, this situation is rare and does not possibly happen.

- 3) The idea of a combined deterministic and stochastic procedure can probably be extended to frequentist model selection approaches. In the frequentist model selection algorithms, the Akaike, Schwarz, Mallows, or cross-validation criteria are computed and they all use similar formulas to $m_+$ and $m_-$. The authors could discuss extension of their algorithm to frequentist model selection.

Answer: Yes, the hybrid search of the proposed method can be easily extended to the frequentist method. The modification is replacement of model selection criterion. But the algorithm that makes use of the Sherman-Morrison formula to reduce the computational burden cannot be extended to frequentist methods.

- 4) Some statisticians argue that mechanical model selection techniques have their disadvantages and the appropriate misspecification tests should be applied to select the best predictors in the model (e.g., Spanos, 2010).  I would like to see how the misspecification testing can be incorporated in the model selection algorithm.

Answer: Adding this technique may imporve the algorithm, but it also may lose our focus of the proposed method -- hybrid search and the use of the Sherman-Morrison formula.

- 5) The main advantage of the new algorithm is the reduction of the computational burden associated with searching for the best subset of predictors. The authors should provide some statistics presenting the improvement in the number of steps and/or the time required to find the optimal subset in comparison to other methods.

Answer: yes, maybe we need to run the simulation again and record the time it cost.

- 6) Some editorial comments: the expressions  "MCP", "LASSO", and "SCAD" should be explained, the expression "setting that p>n" should be "setting where $p>n$" (page 4).
Answer: yes, change it to setting where $p>n$.

## Reviewer #2:

I have two general comments on this very interesting contribution and suggest to resubmit the paper containing some extended analysis of proposed algorithm.

- 1) Extension of the simulation study:
  - why y has unit variance? How interpret prior parameters a_sigma and b_sigma in this case? How results change in the case of estimation for multivariate gaussian Data Generating Process with different relation of the variance of the error term and the variances of the processes generating regressors?

Answer:

i) y can be other variance values. We think if we conduct a fair comparion with other methods (MCP, lasso), the value of variance of y is not important. Besides, when we do the real data analysis, usually we studentize the data first. This make y becomes unit variance.

ii) the hyperparameters a_sigma and b_sigma are set to make the distribution of $\sigma^2$ become flat. $a_\sigma = b_\sigma = 1$

iii) I don't completely understand the question. Is it a hetergeneous variance?

  - How algorithm works in heteroscedastic or generalized regression environment. I would encourage Authors to conduct more extended simulation study focused not only on the simple linear regression, but on some generalized cases with heteroscedasticity or correlation in the vector of error terms.

The hybrid method can be extended to the GLM but not the Sherman-Morrison formula. Since two auther comment about this part, should we extend our hybrid idea to the GLM cases? Or we can comment that our 2nd and 3rd projects are targeting these issues.

  - Some details concerning posterior analysis about inference on variance of the error term should be presented and discussed. Perhaps there is a linkage between ranks of analysed algorithms and inference about parameter of the stochastic structure.

- 2) Extension of the empirical study:
Why empirical part is not conducted for the whole dataset? The progress in search methods developed for model selection (or model averaging) should avoid the step that Authors call the pre-screening procedure. What is the purpose of selecting much smaller set of regressors, that are marginally correlated with endogenous variable. Does final results are invariant with respect to this step?

Answer: I remember at first we try to use the whole dataset, but my computer's memory (8 GB) is too small to store the huge matrix. Maybe we can use beocat to run the whole dataset and compare it with result with pre-screening procedure.

### 2020-02-07 Manuscript/Jin/Project2.tex
major revision 1

@@
 \def\diag{{\rm diag}}
-
-\def\T{{ \mathrm{\scriptscriptstyle T} }}
 
@@
 Therefore, if this case does not occur for sufficiently large $t$, we can treat $\hat{\bg}$ as the global maximum.
-\textcolor{blue}{However, this global maximum is unefficient because it require large enough $t$.
-To improve the efficiency of global search, We applied the idea from Simulated Annealing to Algorithm \ref{alg:2}:
+\textcolor{blue}{However, this global maximum is possibly unefficient because it may require large enough $t$ to make $m(\uy|\hat{\bg})<m(\uy|\bg^{(t)})$ happen.
+To improve the efficiency of global search, We applied the idea from Simulated Annealing to Algorithm \ref{alg:2}, so the step 4 in Algorithm \ref{alg:2} is as follows:
 \begin{itemize}
  \item[1.] Given $\bg^*$, generate $\ueta^*$ with probability,
-       $$\pi(\ueta|\uy,\bg^*)=\frac{\tilde{m}(\uy|\ueta)}{\sum_{\ueta \in \mathcal{N}_+(\bg^* )  } \tilde{m}(\uy|\ueta) }\mathbb{I}\{\ueta \in \mathcal{N}_+(\bg^* ) \},$$ where $\tilde{m}(\uy|\ueta)=\exp\{\frac{1}{\alpha}\log(m(\uy|\ueta)))\}.$ \\
+       $$\tilde{\pi}(\ueta|\uy,\bg^*)=\frac{\tilde{m}(\uy|\ueta)}{\sum_{\ueta \in \mathcal{N}_+(\bg^* )  } \tilde{m}(\uy|\ueta) }\mathbb{I}\{\ueta \in \mathcal{N}_+(\bg^* ) \},$$ where $\tilde{m}(\uy|\ueta)=\exp\{\frac{1}{\alpha}\log(m(\uy|\ueta)))\}.$ \\
  \item[2.] Given $\ueta^*$, generate $\bg^*$ with probability
-       $$\pi(\bg|\uy,\ueta^*)=\frac{\tilde{m}(\uy|\bg)}{\sum_{\bg \in \mathcal{N}_-({\ueta}^* )  } \tilde{m}(\uy|\bg) }\mathbb{I}\{\bg \in \mathcal{N}_-({\ueta}^* )  \},$$ where $\tilde{m}(\uy|\bg)=\exp\{\frac{1}{\alpha}\log(m(\uy|\bg))\}.$
+       $$\tilde{\pi}(\bg|\uy,\ueta^*)=\frac{\tilde{m}(\uy|\bg)}{\sum_{\bg \in \mathcal{N}_-({\ueta}^* )  } \tilde{m}(\uy|\bg) }\mathbb{I}\{\bg \in \mathcal{N}_-({\ueta}^* )  \},$$ where $\tilde{m}(\uy|\bg)=\exp\{\frac{1}{\alpha}\log(m(\uy|\bg))\}.$
 \end{itemize}
 }
+
 \begin{algorithm}[ht]

### 2020-02-07 Manuscript/computational statistics/major_revision_1/BayesSubset_SC.tex
major revision 1

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{Heatmap.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn,natbib]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{url}
%\usepackage[linkcolor=blue,citecolor=blue]{hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
\newcommand{\T}{{ \top}} %
\newcommand{\ua}{{\bf a}} %
\newcommand{\ub}{{\bf b}} %
\newcommand{\uI}{{\bf I}} %
\newcommand{\uH}{{\bf H}} %
\newcommand{\uX}{{\bf X}} %
\newcommand{\ux}{{\bf x}} %
\newcommand{\uy}{{\bf y}} %
\newcommand{\ud}{{\bf d}} %
\newcommand{\uv}{{\bf v}} %
\newcommand{\uV}{{\bf V}} %
\newcommand{\uu}{{\bf u}} %
\newcommand{\um}{{\bf m}} %
\newcommand{\0}{{\boldsymbol 0}} %
\newcommand{\1}{{\boldsymbol 1}} %
\newcommand{\ubeta}{{\boldsymbol \beta}} %
\newcommand{\ueta}{{\boldsymbol \eta}} %
\newcommand{\umu}{{\boldsymbol \mu}} %
\newcommand{\bg}{{\boldsymbol \gamma}} %
\newcommand{\uepsilon}{{\boldsymbol \epsilon}} %
\newcommand{\uSigma}{{\boldsymbol \Sigma}} %
\newcommand{\diag}{{\rm diag}} %
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Computational Statistics}
%
\begin{document}

\title{Bayesian selection of best subsets via hybrid search%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Shiqiang Jin         \and
        Gyuhyeong Goh %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Shiqiang Jin \at Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.\\
\email{jinsq@ksu.edu}           %  \\
\and
Gyuhyeong Goh \at Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.\\
\email{ggoh@ksu.edu} 
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Over the past decades, variable selection for high-dimensional data has drawn increasing attention. With a large number of predictors, there rises a big challenge for model fitting and prediction. In this paper, we develop a new Bayesian method of best subset selection using a hybrid search algorithm that combines a deterministic local search and a stochastic global search. To reduce the computational cost of evaluating multiple candidate subsets for each update, we propose a novel strategy that enables us to calculate exact marginal likelihoods of all neighbor models simultaneously in a single computation. In addition, we establish model selection consistency for the proposed method in the high-dimensional setting in which the number of possible predictors can increase faster than the sample size. Simulation study and real data analysis are conducted to investigate the performance of the proposed method.
\keywords{Bayesian variable selection \and  Best subset selection \and High-dimensional regression analysis \and Hybrid search algorithm}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}\label{sec:1}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%

%% else use the following coding to input the bibitems directly in the
%% TeX file.
Variable selection plays a key role in recent regression analysis. In many statistical applications, especially in genetics studies, researchers often face situations where the number of candidate predictors is extremely large but the sample size is relatively small, often referred to as high-dimensional regression problems. The most pressing challenge in high-dimensional regression is to identify relevant predictor variables from a large pool of candidates. In an attempt to perform high-dimensional variable selection, a lot of effort has been put into the development of penalized likelihood methods (e.g., \citealt{tibshirani1996regression, fan2001variable, zou2005regularization, zhang2010nearly}). By adding a penalty function to the likelihood criterion, the penalized likelihood method produces sparse solutions that automatically eliminate the irrelevant predictors from the regression model using the zero-estimates.

In this paper, we are interested in selecting the $k$ most important predictors out of $p$ candidates, called best subset selection \citep{hocking1967selection}. It is well known that best subset selection involves nonconvex optimization problems that are computationally intractable in high-dimensional settings. Although some penalized likelihood approaches such as Lasso, elastic net, and MCP provide a convex surrogate for nonconvex optimization, their applicability to best subset selection is still limited \citep{bertsimas2016best}. Meanwhile, a Bayesian approach to best subset selection, called Bayesian subset regression (BSR), has been proposed by \citet{liang:2013bayesian}. Using an adaptive Markov chain Monte Carlo (MCMC) algorithm, called the stochastic approximation Monte Carlo \citep{liang2007stochastic}, BSR finds the best subset by performing a stochastic search over the entire model space. However, the stochastic search with a large number of candidate predictors often raises computational challenges including extremely heavy computation and slow convergence. To overcome this limitation, we introduce a hybrid best subset search algorithm that combines a deterministic local search and a stochastic global search in a Bayesian framework. The main attractive feature of our proposed method is that evaluating all possible candidate models for the next update, which is the most expensive part of computation, is simultaneously accomplished in a single computation.
\section{Basic setup}\label{sec:2}
Consider a multiple linear regression model,
\begin{eqnarray}\label{eq:1}
\uy = \uX\ubeta + \uepsilon,
\end{eqnarray}
where $\uy=(y_1,\ldots,y_n)^\T $ is the $n$-dimensional response vector, $\uX = (\ux_1,\ldots,\ux_p)$ is the $n\times p$ design matrix with $\ux_j=(x_{1j},\ldots, x_{nj})^\T$, $\ubeta = (\beta_1,\ldots,\beta_p)^{\T}$ is a $p$-dimensional coefficient vector, and $\uepsilon=(\epsilon_1,\ldots,\epsilon_n)^\T \sim \text{Normal}(\0_n, \sigma^2\uI_n)$. Throughout this paper, we restrict our attention to high-dimensional regression problems and thus it is always assumed that $p>n$ and $\ubeta$ contains many zero elements. We further assume that $\uy$ and columns of $\uX$ are standardized so that the intercept is excluded from our regression analysis. In this paper, our goal is to identify the $k$ most important predictors in \eqref{eq:1}, where the best subset size, $k$, can be considered as being either fixed or varying. To formulate a Bayesian framework for best subset selection, let $\bg=\{j:\beta_j\neq 0\}$ be an index set of the active predictors. Given $\bg$, the full model \eqref{eq:1} reduces  to
\begin{eqnarray*}
\uy = \uX_{\bg} \ubeta_{\bg} + \uepsilon,
\end{eqnarray*}
where $\uX_{\bg}$ and $\ubeta_{\bg}$ are a sub-matrix of $\uX$ and a sub-vector of $\ubeta$ that are determined by $\bg$, respectively. For algebraic and computational convenience, given $\bg$, we consider conjugate priors for $\ubeta_{\bg}$ and $\sigma^2$ as follows:
\begin{eqnarray*}
	\ubeta_{\bg}|\sigma^2,\bg &\sim&\text{Normal}(0,\tau \sigma^2 \uI_{|\bg|} ),\\
	\sigma^2 &\sim& \text{Inverse-Gamma}(a_{\sigma}/2,b_{\sigma}/2),
\end{eqnarray*} 
where $\tau$, $a_{\sigma}$, and $b_{\sigma}$ are hyperparameters and $|\bg|$ denotes the number of elements in the set $\bg$. To impose the constraint $|\bg|=k$, we define the prior distribution of $\bg$ by $\pi(\bg)\propto\mathbb{I}(|\bg|=k )$, where $\mathbb{I}(\cdot)$ is an indicator function. Let $m(\uy|\bg)$ be the marginal likelihood given $\bg$. Using the kernels of normal density and inverse gamma density, the marginal likelihood can be calculated as
\begin{eqnarray}
\label{eq:2} m(\uy|\bg) &=&\int f(\uy|\ubeta_{\bg},\sigma^2)\pi(\ubeta_{\bg}|\sigma^2, \bg) \pi(\sigma^2) d\ubeta_\bg d\sigma^2 \nonumber \\
&\propto& \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
		\uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
	\uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } },
\end{eqnarray}
where $f(\uy|\ubeta_{\bg},\sigma^2)$ denotes the reduced model likelihood function given $\bg$ and $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$.

From Bayes' theorem, the posterior model probability of $\bg$ is proportional to $\pi(\bg|\uy)\propto m(\uy|\bg) \pi(\bg)\propto m(\uy|\bg) \mathbb{I}(|\bg|=k )$. Therefore, Bayesian best subset selection can be performed by maximizing $m(\uy|\bg)$ over $\bg$ subject to the constraint $|\bg|=k$. Keep in mind that high-dimensional and non-convex optimization problems arise in our framework.

\section{Best subset selection with a fixed-size}\label{sec:3}
In this section, we develop a new Bayesian approach to best subset selection with a fixed subset size $k$. Let $\hat{\bg}$ be the current estimate of the best subset of size $k$. Our strategy is to update $\hat{\bg}$ by searching over neighbor models iteratively. To this end, for an index set $\bg$, define $\mathcal{N}_+(\bg)= \{\bg \cup \{i\}:i\notin \bg\},$ which represents the set of larger neighbors of $\bg$ obtained by adding a new index to $\bg$. Similarly, define $\mathcal{N}_-(\bg)= \{\bg \setminus \{j\}:j \in \bg\}$ to be the set of smaller neighbors of $\bg$ obtained by deleting an index from $\bg$.

We introduce a deterministic search algorithm in Algorithm \ref{alg:1} that converges to a local maximum of $m(\uy|\bg)$ subject to $|\bg|=k$.
\begin{algorithm}[H]
\caption{Deterministic best subset search with a fixed $k$}\label{alg:1}
\begin{itemize}\itemsep=0pt
\item[1.] Define $\hat{\bg}$ to be an initial subset of size $k$; and set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[2.] \textbf{Repeat} for $t=1,2,\ldots,$
\begin{itemize}\itemsep=0pt
\item[a)] Compute $\tilde{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)$;\\ \texttt{\# i.e., select the locally best subset of size k+1} 
\item[b)] Compute $\hat{\bg}^{(t)}=  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$;\\ \texttt{\# i.e., select the locally best subset of size k} 
\item[c)] Update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$; 
\end{itemize}
\item[] \textbf{until} $\hat{\bg}^{(t-1)}=\hat{\bg}^{(t)}$. \texttt{\# i.e., terminate immediately if no update is made}
\item[3.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}
The following theorem proves the convergence of the proposed deterministic search algorithm.
\begin{theorem}\label{thm:1} The deterministic search in Algorithm \ref{alg:1} monotonically increases the objective function, $m(\uy|\bg)$, subject to $|\bg|=k$. In addition, the algorithm terminates in a finite number of iterations.
\end{theorem}
\begin{proof}[of Theorem \ref{thm:1}] Let $\hat{\bg}^{(t-1)}$ be the best subset of size $k$ updated by the ${t-1}$-th iteration. Then, $\hat{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$, where $$\tilde{\bg}^{(t)}=\arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)}  ) } m(\uy|\bg).$$ Since $\hat{\bg}^{(t-1)}$ also belongs to $ \mathcal{N}_-(\tilde{\bg}^{(t)} ) $, we thus have $m(\uy|\hat{\bg}^{(t-1)} ) \leq m(\uy|\hat{\bg}^{(t)}),$ which proves our first statement. Since the number of all possible states of $\bg$ satisfying $|\bg|=k$ is finite, the algorithm terminates in a finite number of iterations. This completes our proof.
\end{proof}
Although the deterministic search algorithm converges rapidly, a possible drawback is that the algorithm can get trapped in a local optimum. As an alternative, we introduce a stochastic search algorithm in Algorithm \ref{alg:2} that converges to a global maximum of $m(\uy|\bg)$ with the constraint $|\bg|=k$.
\begin{algorithm}[ht!]
\caption{Stochastic best subset search with a fixed $k$}\label{alg:2}
\begin{itemize}\itemsep=0pt
\item[1.] Define $\hat{\bg}$ to be an initial subset of size $k$; and set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[2.] \textbf{Repeat} for $t=1,\ldots,T$:
\begin{itemize}\itemsep=0pt
\item[a)] Update $\tilde{\bg}^{(t)}$ by selecting one from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probability $$\frac{m(\uy|\bg)}{\sum_{\bg' \in \mathcal{N}_+(\hat{\bg}^{(t-1)})} m(\uy|\bg')},~\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} );$$ 
\item[b)] Update $\hat{\bg}^{(t)}$ by selecting one from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probability $$\frac{m(\uy|\bg)}{\sum_{\bg' \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg')},~\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) ;$$
\item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$.
\end{itemize}
\item[3.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}
Note that the proposed stochastic search algorithm generates a Markov chain, $\{\hat{\bg}^{(t)},t=1,\ldots,T\}$, with the state space $\{\bg:|\bg|=k\}$. Hence, if the current estimate $\hat{\bg}$ is not the global maximum, then we must observe that $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$ with probability one as $T\to \infty$. Therefore, as we iterate the algorithm, $\hat{\bg}$ converges to the global maximum.

Although the stochastic search algorithm eventually reaches the global optimum, it requires the large number of iterations, which is computationally inefficient. To develop a computationally efficient global optimization algorithm, we propose a hybrid best subset selection algorithm that combines the stochastic global search algorithm and the deterministic local search algorithm into one. The proposed hybrid search algorithm is given in Algorithm \ref{alg:3}.
\begin{algorithm}[ht!]
\caption{Hybrid best subset search with a fixed $k$}\label{alg:3}
\begin{itemize}\itemsep=0pt
\item[1.] Define an initial model of size $k$ as $\hat{\bg}$.
\item[2.] Set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[\texttt{\#}] \texttt{deterministic search step}
\item[3.] \textbf{Repeat} for $t=1,2,\ldots:$ 
\begin{itemize}\itemsep=0pt
\item[a)] Compute $\tilde{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)$; 
\item[b)] Compute $\hat{\bg}^{(t)}=  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$;
\item[c)] Update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$;
\end{itemize}
\item[] \textbf{until} $\hat{\bg}^{(t-1)}=\hat{\bg}^{(t)}$.
\item[4.] Set $\hat{\bg}^{(0)}=\hat{\bg}$ and choose a tuning parameter $\alpha \in (0,1]$.
\item[\quad \texttt{\#}] \texttt{stochastic search step}
\item[5.] \textbf{Repeat} for $t=1,\ldots,T$: 
\begin{itemize}
\item[a)] Update $\tilde{\bg}^{(t)}$ by drawing one from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probability $$\frac{m(\uy|\bg)^\alpha}{\sum_{\bg\in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)^\alpha},~\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} );$$
\item[b)] Update $\hat{\bg}^{(t)}$ by drawing one from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probability $$\frac{m(\uy|\bg)^\alpha}{\sum_{\bg' \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg')^\alpha },~\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} );$$
\item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$ and immediately go to Step 2.
\end{itemize}
\item[6.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}
In the proposed hybrid search algorithm, the deterministic search is first used to find a local optimum in an efficient manner. Then, the stochastic search is employed to check whether or not the deterministic search algorithm has reached the global optimum. Note that if the stochastic search finds a better subset $\hat{\bg}^{(t)}$ than the current best subset $\hat{\bg}$ (i.e., when $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$ occurs), then we immediately stop the stochastic search procedure and go back to the deterministic search step with the updated state of $\hat{\bg}$. To improve the performance of stochastic search, we introduce a tuning parameter $\alpha \in (0,1]$ which acts as a precision parameter. As $\alpha\to 0$, the distribution will be more spread out so that the chance of getting stuck in the local maximum will be reduced in the stochastic search step. If we set $\alpha=1$, the stochastic search step is analogous to Algorithm \ref{alg:2}. In our simulation study and real data analysis, we set $\alpha=\min\{1,\log(2)/\log( m_{(1)} /  m_{(2)} )\}$, where $m_{(1)}$ and $m_{(2)}$ are, respectively, the first and second largest values of $\{m(\uy|\bg):\bg  \in \mathcal{N}_+(\hat{\bg})\}$.

In general, calculating marginal likelihoods for many candidate models, which is a necessary step in Bayesian model selection, is computationally expensive, even if an explicit form is available as in \eqref{eq:2}. The great merit of the proposed method is that evaluating the marginal likelihoods of all the candidates for the next update can be done simultaneously \emph{within a single computation}. To this end, let $\hat{\bg}$ be an index set of a model of size $k$ and $\tilde{\bg}$ be an index set of a model of size $k+1$. For any $i\notin \hat{\bg}$, it can be shown that
\begin{eqnarray}
 \nonumber&& m(\uy|\hat{\bg}\cup\{i\}) \\
 \nonumber&&\propto \left\{\uy^{\T}\uH_{\hat{\bg}}\uy-\frac{(
 	\ux_i^{\T}\uH_{\hat{\bg}}\uy)^2}{\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i }+b_{\sigma}\right\}^
 {-\frac{a_{\sigma}+n}{2}} \\
 \label{eq:app:1} & &\quad \times (\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i)^{-1/2},
\end{eqnarray}
where $\ux_i$ is the $i$-th column of $\uX$. The proof of \eqref{eq:app:1} is given in Appendix \ref{app:1}. Note that $\ux_i^{\T}\uH_{\hat{\bg}}\ux_i$ is the $i$-th diagonal element of $\uX^{\T}\uH_{\hat{\bg}}\uX$ and that $\ux_i^{\T}\uH_{\hat{\bg}}\uy$ is the $i$-th element of $\uX^{\T}\uH_{\hat{\bg}}\uy$. This implies that Eq. \eqref{eq:app:1} is the $i$-th element of the following $p$-dimensional vector:
\begin{eqnarray*}
&&\um_+({\hat{\bg}})=\\
&& \left\{(\uy^{\T}\uH_{\hat{\bg}}\uy+b_{\sigma}) \1_p-\frac{(\uX^{\T}\uH_{\hat{\bg}}\uy)^2}{\frac{1}{\tau}\1_p+\diag(\uX^{\T}\uH_{\hat{\bg}}\uX) } \right\}^
 {-\frac{a_{\sigma}+n}{2}}\\
 &&\quad \times\left\{\frac{1}{\tau} \1_p  +\diag(\uX^{\T}\uH_{\hat{\bg}}\uX) \right\}^{-1/2},
 \end{eqnarray*}
 where $\ua^x$ and $\ua/\ub$ indicate entrywise operations for generic vectors $\ua$ and $\ub$, accordingly. For example, $\ua^x=(a_1^x,\ldots, a_p^x)$ and $\ua/\ub=(a_1/b_1,\ldots,a_p/b_p)$. Note that $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{i\}:i\notin \hat{\bg} \}$. Therefore, evaluating $m(\uy|\bg)$ for all $\bg \in \mathcal{N}_+(\hat{\bg} )$ can be done simultaneously in a single computation by obtaining the sub-vector of $\um_+({\hat{\bg}})$ for $\{i:i\notin \hat{\bg} \}$. Similarly, for any $j \in\tilde{\bg}$, we can show that 
 \begin{eqnarray}
 \nonumber&&m(\uy|\tilde{\bg}\setminus \{j\}) \\
 \nonumber &&\propto \left\{\uy^{\T}\uH_{\tilde{\bg}}\uy+\frac{(
 	\ux_j^{\T}\uH_{\tilde{\bg}}\uy)^2}{\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j }+b_{\sigma}\right\}^
 {-\frac{a_{\sigma}+n}{2}}\\
\label{eq:app:2}&&\quad \times (\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j)^{-1/2}.
\end{eqnarray} The proof of \eqref{eq:app:2} is given in \ref{app:2}. Define
\begin{eqnarray*}
&&\um_-({\tilde{\bg}}) =\\
&& \left\{(\uy^{\T}\uH_{\tilde{\bg}}\uy+b_{\sigma}) \1_p+\frac{(\uX^{\T}\uH_{\tilde{\bg}}\uy)^2}{\frac{1}{\tau}\1_p-\diag(\uX^{\T}\uH_{\tilde{\bg}}\uX) } \right\}^
 {-\frac{a_{\sigma}+n}{2}}\\
 &&\quad \times\left\{\frac{1}{\tau} \1_p  -\diag(\uX^{\T}\uH_{\tilde{\bg}}\uX) \right\}^{-1/2}.
 \end{eqnarray*}
It is easy to check that Eq. \eqref{eq:app:2} is the $j$-th element of $\um_-({\tilde{\bg}})$. Since $\mathcal{N}_-(\tilde{\bg})=\{\tilde{\bg} \setminus \{j\}:j\in \tilde{\bg} \}$, evaluating $m(\uy|\bg)$ for all $\bg \in \mathcal{N}_-(\tilde{\bg} )$ can be done simultaneously in a single computation by obtaining the sub-vector of $\um_-({\tilde{\bg}})$ for $\{j :j \in \tilde{\bg} \}$. Using the aforementioned calculation strategy, we can easily and quickly implement steps 3a), 3b), 5a), and 5b) of Algorithm \ref{alg:3}. It is also worth noting that the proposed calculation method enables us to avoid multiple computations of inverse and determinant of matrices in Eq. \eqref{eq:2}.

\section{Best subset selection with varying sizes}\label{sec:4}
In this section, we extend the proposed method to handle the case of varying $k \leq K$, where $K$ is a prespecified upper bound. This is a common setting for high-dimensional best subset selection problems (e.g., \citealt{bertsimas2016best, liang:2013bayesian}). In a Bayesian framework, this extension can be easily done by assigning an appropriate prior for unknown $k$. As a non-informative prior, one may consider a discrete uniform prior for $k$, that is, $k \sim \text{Uniform}\{1,\ldots,K\}$. However, the uniform prior tends to assign larger probability to a larger subset due to the fact that the total number of subsets of size $k$ is $\binom{p}{k}$, which tends to increase exponentially as $k$ increases. To resolve this issue, using a similar idea of \citet{chen2008extended}, we consider
\begin{eqnarray*}
\pi(k)\propto \mathbb{I}(k\leq K) / \binom{p}{k} .
\end{eqnarray*}
From Bayes' theorem, Bayesian best subset selection is then performed by maximizing
\begin{eqnarray}\label{joint:opt}
\pi(\bg|\uy)\propto  m(\uy|\bg)\mathbb{I}(|\bg|\leq K)/\binom{p}{|\bg|} .
\end{eqnarray}
Note that \eqref{joint:opt} is equivalent to the following optimization problem:
\begin{eqnarray*}
 \max_{\bg} \left\{m(\uy|\bg)\mathbb{I}(|\bg|=k) /\binom{p}{k} \right\}  \quad \text{subject to }k\leq K.
 \end{eqnarray*}
Therefore, the optimization problem in Eq. \eqref{joint:opt} can be solved by proceeding the following steps:
\begin{enumerate}
\item For $k=1,\ldots,K$, compute $$\hat{\bg}_k= \arg\max_{\bg:|\bg|=k} m(\uy|\bg)$$ using Algorithm \ref{alg:3}.
\item Compute $$ \hat{k}=\arg\max_{1\leq k \leq K} \left\{\log m(\uy|\hat{\bg}_k)-\log \binom{p}{k} \right\}.$$
\item Return $\hat{\bg}=\hat{\bg}_{\hat{k}}$.
\end{enumerate}
Note that if a parallel or cluster computing environment is available, then it can be applied to the first step of the above procedure to run the for-loop over $k$ in parallel. The following theorem shows that the proposed Bayesian approach achieves the model selection consistency in the high-dimensional setting that $p>n$.

\begin{theorem}\label{thm:2} Define $\Gamma=\{\bg:|\bg|\leq K,\bg\neq \bg_*\}$, where $\bg_*$ is the true model.  Assume that $p=O(n^\xi)$ for $\xi\geq 1$. Under the asymptotic identifiability condition of \citet{chen2008extended}, if $\tau\to \infty$ as $n\to \infty$ but $\tau=o(n)$, then the proposed Bayesian subset selection possesses the Bayesian model selection consistency, that is,
\begin{eqnarray}\label{thm:2:eq}
\pi(\bg_*|\uy) > \max_{ \bg \in \Gamma }\pi(\bg|\uy)
\end{eqnarray}
in probability as $n\to \infty$.
\end{theorem}
\begin{proof}[of Theorem \ref{thm:2}]  From the Laplace approximation of \citet{kass1995}, we have
\begin{eqnarray*}
\log m(\uy|\bg) = \log f(\uy|\hat{\ubeta}_\bg, \hat{\sigma}^2)-\frac{|\bg|}{2}\log n+o_p(\log n ),
\end{eqnarray*}
where  $\hat{\ubeta}_\bg= (\uX_\bg^\T \uX_{\bg})^{-1} \uX_{\bg}^\T \uy$ and $\hat{\sigma}^2=\|\uH_{\bg}\uy\|^2/n$. Ignoring a smaller order term than $\log n$, our posterior criterion \eqref{joint:opt} can be approximated as 
\begin{eqnarray}
\nonumber -2 \log \pi(\bg |\uy) &\approx& -2 \log f(\uy|\hat{\ubeta}_\bg,\hat{\sigma}^2)\\
\label{ebic}&&+{|\bg|}\log n+2\log \binom{p}{k},
\end{eqnarray}
which is equivalent to the extended Bayesian information criterion \citep{chen2008extended}. Therefore, it follows from Theorem 1 of \citet{chen2008extended} that Eq. \eqref{thm:2:eq} holds in probability.
\end{proof}

\section{Simulation study}\label{sec:5}
In this section, we investigate the variable selection performance of our best subset selection algorithm on simulated high-dimensional data. For $n=100$, we generate the data $\{(y_i,x_{i1},\ldots,x_{ip}):i=1,\ldots,n\}$ from the following linear regression model:
\begin{eqnarray*}
y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},\sigma^2_y\right),
\end{eqnarray*}
where $(x_{i1},\ldots,x_{ip})$ follows $\text{Normal}(\0_p,\uV)$ with $\uV=(v_{ij})_{p\times p}$ and $v_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$, and $\sigma^2_y$ is variance of error item.

We consider four different cases: 
\begin{itemize}
	\item [(i)] $p=200$, $\rho=0.1$, $\sigma^2_y = 1$,
	\item [(ii)] $p=200$, $\rho=0.9$, $\sigma^2_y = 1$,
	\item [(iii)] $p=1000$, $\rho=0.1$, $\sigma^2_y = 1$,
	\item [(iv)] $p=1000$, $\rho=0.9$, $\sigma^2_y = 1$,
	\item [(v)] $p=200$, $\rho=0.1$, $\sigma^2_y = 2$,
	\item [(vi)] $p=200$, $\rho=0.9$, $\sigma^2_y = 2$,
	\item [(vii)] $p=1000$, $\rho=0.1$, $\sigma^2_y = 2$,
	\item [(viii)] $p=1000$, $\rho=0.9$, $\sigma^2_y = 2$.
\end{itemize}
We assume that there is no prior information. Hence, to make our prior distributions non-informative, we set $a_\sigma=b_\sigma=1$ and $\tau=(\log p)^2$, which satisfies the sufficient condition for model selection consistency discussed in Theorem \ref{thm:2}. We further assume that the true number of active predictors is unknown. Hence, we employ the proposed method in Section \ref{sec:4} for varying $k$ with $K=\lceil n^{2/3} \rceil =22$. For the hybrid search algorithm given in Algorithm \ref{alg:3}, we set $T=100$, which is a remarkably small number of iterations compared to existing stochastic search algorithms (e.g., \citealt{kirkpatrick1983optimization, george1993variable, hans2007shotgun}), and marginal correlations between the response and each predictor are used to define the initial value of $\hat{\bg}$. For comparison purposes, we also employ four popular penalized likelihood methods: LASSO \citep{tibshirani1996regression}, the elastic net \citep{zou2005regularization}, SCAD \citep{fan2001variable}, and MCP \citep{zhang2010nearly}, where the regularization parameters or tuning parameters are determined by the extended BIC in \eqref{ebic} to achieve a fair comparison with the proposed method. In this simulation study, LASSO and ENET are implemented by R package \texttt{glmnet} and  MCP and SCAD are performed by R package \texttt{ncvreg}. To evaluate the variable selection performance, we calculate false discovery rate, percentage of selecting the exact true model, average size of the selected model, and mean of Hamming distance based on $2,000$ Monte Carlo replications. False discovery rate is defined as $|\hat{\bg}\setminus \bg_*|/|\hat{\bg}|$ and Hamming distance is defined as $|\hat{\bg}\setminus \bg_* |+|\bg_* \setminus  \hat{\bg}|$, where $\bg_*$ denotes the index set of the true model.

\begin{table}[h]
\centering
  \caption{Simulation study results based on $2,000$ Monte Carlo replications for cases i--iv. Notation: FDR---false discovery rate; TRUE---percentage of the true model detected; SIZE---selected model size; HAM---Hamming distance; s.e.--- standard error.}\label{T:sim1}
\begin{tabular}{c|ccccc}
\hline
 & &FDR& TRUE & SIZE & HAM   \\
Case &Method& (s.e.) & (s.e.)   & (s.e.)     & (s.e.)    \\
\hline
    i      & Proposed & 0.006   & 96.900  & 4.032   & 0.032  \\
          & & (0.001)  & (0.388)  & (0.004)    & (0.004) \\
           & SCAD                           & 0.034 & 85.200  & 4.188  & 0.188 \\
           &                         & (0.002)  & (0.794)  &(0.011)   & (0.011) \\
           & MCP                            & 0.035  & 84.750 & 4.191  & 0.191  \\
           &                             &  (0.002)  &  (0.804)  & (0.011)   & (0.011) \\
           & ENET                           & 0.016  & 92.700  & 4.087  & 0.087  \\
           &                            &(0.001)  & (0.582)  &  (0.007)   & (0.007) \\
           & LASSO                          & 0.020  & 91.350  & 4.109   & 0.109\\
           &                          & (0.002)  &  (0.629)  & (0.009)   & (0.009) \\
           \hline
  ii         & Proposed & 0.023 & 88.750& 3.985  & 0.203\\
           &  & (0.002) & (0.707) & (0.006)  & (0.014) \\

           & SCAD                           & 0.059& 74.150  & 4.107   & 0.480  \\
           &                        & (0.003)  & (0.979)  & (0.015)   & (0.022) \\
           & MCP                            & 0.137  & 55.400  & 4.264   & 1.098  \\
           &                        & (0.004)  &  (1.112)  &(0.020)   &  (0.034) \\
           & ENET                           & 0.501   & 0.300   & 7.716  & 5.018  \\
           &                        & (0.004)  &  (0.122)   & (0.072)   &  (0.052) \\
           & LASSO                          & 0.276  & 15.550 & 5.308  & 2.038  \\
           &                          & (0.004)  & (0.811)  & (0.033)   & (0.034) \\
             \hline
  iii         & Proposed & 0.004  & 98.100 & 4.020 & 0.020 \\
          &  &(0.001)   & (0.305)  & (0.003)    & (0.003) \\
           & SCAD                           & 0.027 & 87.900& 4.145   & 0.145\\
           &                           & (0.002)  & (0.729)  &(0.010)   & (0.010) \\
           & MCP                            & 0.031  & 86.550 & 4.172  & 0.172\\
           &                            & (0.002)  & (0.763)  & (0.013)   & (0.013) \\
           & ENET                           & 0.035 & 84.850& 4.181 & 0.206\\
           &                           & (0.002)  & (0.802)  & (0.013)   & (0.012) \\
           & LASSO                          & 0.014 & 93.850 & 4.073 & 0.073\\
           &                          &(0.001)  &(0.537)  &(0.007)   &(0.007) \\
             \hline
   iv      & Proposed & 0.023  & 89.850& 4.005& 0.190 \\
         & & (0.002)   & (0.675)  & (0.005) &(0.013) \\
           & SCAD                           & 0.068 & 74.250& 4.196 & 0.493\\
           &                            & (0.003)  & (0.978)  & (0.014)   & (0.023) \\
           & MCP                            & 0.152 & 53.750 & 4.226 & 1.202 \\
           &                           & (0.004)  & (1.115)  & (0.017)   & (0.035) \\
           & ENET                           & 0.417 & 0.150& 6.228& 4.089 \\
           &                           & (0.005)  & (0.087)   & (0.068)   & (0.043) \\
           & LASSO                          & 0.265& 19.500 & 5.139 & 1.909 \\
           &                          & (0.004)  &(0.886)  &(0.029)   & (0.035) \\
\hline
\end{tabular}
\end{table}

The results are shown in Table \ref{T:sim1}. For every case, the proposed method outperforms all the penalized likelihood methods. The proposed method always achieves the smallest false discovery rate and this implies that the proposed method provides the minimum proportion of incorrectly identifying the true active predictors as inactive. According to the selected model size and the Hamming distance, we argue that the proposed method tends to select the closest model to the true model. In addition, the proposed method selects the exact true model with high probability. Hence, this finite sample performance supports our theoretical result in Theorem \ref{thm:2}.

\section{Real data application}
In this section, we apply the proposed method to Breast invasive carcinoma (BRCA) data, which are generated by The Cancer Genome Atlas (TCGA) Research Network: \url{http://cancergenome.nih.gov}. We download BRCA data using \texttt{R} package \texttt{curatedTCGAData}. The data set contains $17,814$ gene expression measurements (recorded on the log scale) of $526$ patients with primary solid tumor in TCGA project. BRCA1 is a well-known tumor suppressor gene and its mutations predispose women to breast cancer \citep{findlay2018accurate}. Our goal here is to identify the best fitting model for estimating an association between BRCA1 (response variable) and the other genes (independent variables). After removing missing values, the data set reduces to $n=526$ samples with $17,323$ genes.

As a pre-screening procedure, we first select the top $5,000$ genes that are marginally correlated with BRCA1. Then, the proposed method and the penalized likelihood methods as in Section \ref{sec:5} are applied to the reduced data with $n=526$ and $p=5,000$. To assess model fitting, for each method, we compute BIC \citep{schwarz1978}, extended BIC, and mean squared prediction error (MSPE) for the ordinary least squares (OLS) estimate that are obtained by using the selected predictors, where MSPE is estimated by Monte Carlo cross-validation over $500$ replications based on $70\%$ of training set and $30\%$ of testing set.

Table \ref{T:realdata} summarizes model comparison results. As both BIC and extended BIC are minimized at the resulting model from the proposed method, this implies that our Bayesian method is most strongly supported by the data. In addition, the proposed method has the smallest MSPE. Hence, the results demonstrate that the proposed method provides the best fit to the data. 
\begin{table}[t]
\centering
\caption{Model comparison results for BRCA data}\label{T:realdata}
 \begin{tabular}{cccc}
\hline
            & BIC     & extended BIC &  MSPE    \\
\hline
  Proposed       & 984.449  & 1099.504 &  0.599\\
  SCAD           & 1104.693 & 1166.472& 0.681 \\
  MCP           & 1104.693 & 1166.472& 0.681  \\
  ENET           & 1110.653 & 1186.245&  0.683 \\
  LASSO         & 1104.693 & 1166.472  &  0.681\\
\hline
 \end{tabular}
\end{table}
The heatmap in Figure \ref{Fig:heatmap} displays the OLS coefficient estimates and the p-values of the selected predictors for each method. As a result, the proposed method identifies $8$ genes that are statistically related to the human tumor suppressor gene, BRCA1. According to the human gene database, called GeneCards, except for C10orf76, $7$ among the $8$ genes are associated with diseases including Myasthenic Syndrome, Pancreatic Cancer, Kenny-Caffey Syndrome, and Mental Retardation. The GeneCards database is publicly available at \url{https://www.genecards.org}.

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{heatmap.eps}
\caption{A heatmap of OLS coefficient estimates for the selected predictors with p-values.\label{Fig:heatmap}}
\end{figure}

\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrr}
		\hline
		& NSP & MSE\_Pred & BIC & EBIC \\ 
		\hline
		Proposed & 8.00 & 0.60 & 985.93 & 1120.87 \\ 
		SCAD & 4.00 & 0.68 & 1104.69 & 1176.42 \\ 
		MCP & 4.00 & 0.68 & 1104.69 & 1176.42 \\ 
		ENET & 5.00 & 0.68 & 1110.65 & 1198.68 \\ 
		LASSO & 4.00 & 0.68 & 1104.69 & 1176.42 \\ 
		\hline
	\end{tabular}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{heatmap1.pdf}
	\caption{A heatmap of OLS coefficient estimates for the selected predictors with p-values without screening.\label{Fig:heatmap1}}
\end{figure}

\section{Discussion}
The proposed hybrid search approach is computationally beneficial and practically effective compared with traditional stochastic search algorithms that are commonly used in Bayesian variable selection. Although the idea of searching over the neighborhood is somewhat similar to that of the MCMC model composition (MC$^3$) algorithm \citep{madigan1995bayesian} and the shotgun stochastic search (SSS) algorithm \citep{hans2007shotgun}, our search strategy is completely different from the existing methods. While MC$^3$ and SSS perform a stochastic search over the model space of all possible candidates, we implement a hybrid search over the sub-model space of size $k$. In addition, evaluating multiple candidates for the next move can be done simultaneously in a single computation in the proposed method.

In addition, as mentioned in Section \ref{sec:4}, parallel computing, which executes many calculations simultaneously using multiple nodes or multiple processors, can be employed in the proposed framework. Our hybrid search algorithm can be also extended to multivariate regression and binary regression in a Bayesian framework. Such works are in progress by the authors.

\appendix
\section{Calculation of Equation (3)}\label{app:1}
For any $i \notin \hat{\bg}$, from Eq. \eqref{eq:2}, we have
\begin{eqnarray}
\nonumber m(\uy|\hat{\bg}\cup\{i\})&\propto& |\uX_{\hat{\bg}\cup\{i\} }^{\T}\uX_{\hat{\bg}\cup\{i\} }+\tau^{-1}\uI_{k+1} |^{-1/2} \\
 \label{fact:0}&&\times \left(\uy^{\T}\uH_{\hat{\bg}\cup\{i\}}\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2} }.
\end{eqnarray}
It follows from the Sherman-Morrison formula that
\begin{eqnarray}\label{fact:1}
\uH_{\hat{\bg}\cup\{i\} }= \uH_{\hat{\bg}}-\frac{\uH_{\hat{\bg}}\ux_i \ux_i
	^{\T}\uH_{\hat{\bg}} } {\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}}\ux_i}.
\end{eqnarray}
Using the Sylvester's determinant identity and the Sherman-Morrison formula, we obtain 
\begin{eqnarray}
	\nonumber &&|\uX_{\hat{\bg}\cup\{i\} }^{\T}\uX_{\hat{\bg}\cup\{i\} }+\tau^{-1}\uI_{k+1}   | \\
	\nonumber &&= \tau^{-(k+1)}|\tau \uX_{\hat{\bg}\cup\{i\} }\uX_{\hat{\bg}\cup\{i\} }^{\T}+\uI_n |\nonumber\\
	\nonumber &&= \tau^{-(k+1)}|\tau \uX_{\hat{\bg}}\uX_{\hat{\bg}}^{\T}+\uI_n+\tau \ux_i \ux_i^{\T} |\nonumber\\
	\nonumber &&=  \tau^{-(k+1)} |\tau \uX_{\hat{\bg}}\uX_{\hat{\bg}}^{\T}+\uI_n| \{1+ \tau \ux_i^{\T}
	(\tau \uX_{\hat{\bg}}\uX_{\hat{\bg}}^{\T}+\uI_n)^{-1}\ux_i\}\nonumber\\
	\label{fact:2} &&=| \uX_{\hat{\bg}}^{\T}\uX_{\hat{\bg}}+\tau^{-1}\uI_{k}| (\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i).
\end{eqnarray}
Applying \eqref{fact:1} and \eqref{fact:2} to \eqref{fact:0}, we thus have
\begin{eqnarray*}
 m(\uy|\hat{\bg}\cup\{i\}) &\propto& \left\{\uy^{\T}\uH_{\hat{\bg}}\uy-\frac{(
 	\ux_i^{\T}\uH_{\hat{\bg}}\uy)^2}{\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i }+b_{\sigma}\right\}^
 {-\frac{a_{\sigma}+n}{2}}\\
 &&\times (\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i)^{-1/2}
\end{eqnarray*}
for any $i \notin \hat{\bg}$.

\section{Calculation of Equation (4)}\label{app:2}
For any $j \in \tilde{\bg}$, Eq. \eqref{eq:2} leads to
\begin{eqnarray}
\nonumber m(\uy|\tilde{\bg}\setminus\{j\})&\propto& |\uX_{\tilde{\bg}\setminus\{j\} }^{\T}\uX_{\tilde{\bg}\setminus\{j\}}+\tau^{-1}\uI_{k} |^{-1/2} \\
 \label{fact:0-1}&&\times  \left(\uy^{\T}\uH_{\tilde{\bg}\setminus\{j\}}\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2} }.
\end{eqnarray}
From the Sherman-Morrison formula, we have
\begin{eqnarray}\label{fact:1-1}
\uH_{\tilde{\bg}\setminus\{j\} }= \uH_{\tilde{\bg}}+\frac{\uH_{\tilde{\bg}}\ux_j \ux_j
	^{\T}\uH_{\tilde{\bg}} } {\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}}\ux_j}.
\end{eqnarray}
From the Sylvester's determinant identity and the Sherman-Morrison formula, we obtain 
\begin{eqnarray}
	\nonumber &&|\uX_{\tilde{\bg}\setminus\{j\}}^{\T}\uX_{\tilde{\bg}\setminus\{j\} }+\tau^{-1}\uI_{k}   | \\
	&&= \tau^{-k}|\tau \uX_{\tilde{\bg}\setminus\{j\} }\uX_{\tilde{\bg}\setminus\{j\} }^{\T}+\uI_n |\nonumber\\
	&&= \tau^{-k}|\tau \uX_{\tilde{\bg}}\uX_{\tilde{\bg}}^{\T}+\uI_n-\tau \ux_j \ux_j^{\T} |\nonumber\\
	&&=  \tau^{-k} |\tau \uX_{\tilde{\bg}}\uX_{\tilde{\bg}}^{\T}+\uI_n| \{1- \tau \ux_j^{\T}
	(\tau \uX_{\tilde{\bg}}\uX_{\tilde{\bg}}^{\T}+\uI_n)^{-1}\ux_j\}\nonumber\\
	\label{fact:2-1} &&=\tau^2 | \uX_{\tilde{\bg}}^{\T}\uX_{\tilde{\bg}}+\tau^{-1}\uI_{k+1}| (\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j).
\end{eqnarray}
Hence, applying \eqref{fact:1-1} and \eqref{fact:2-1} to \eqref{fact:0-1}, we have
\begin{eqnarray*}
&&m(\uy|\tilde{\bg}\setminus \{j\})  \propto \left\{\uy^{\T}\uH_{\tilde{\bg}}\uy+\frac{(
 	\ux_j^{\T}\uH_{\tilde{\bg}}\uy)^2}{\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j }+b_{\sigma}\right\}^
 {-\frac{a_{\sigma}+n}{2}}\\
 &&\times (\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j)^{-1/2}
\end{eqnarray*}
for any $j \in \tilde{\bg}$.

\bibliographystyle{spbasic} 
\bibliography{Ref_Bayes_Subset}

\end{document}
% end of file template.tex

### 2020-02-07 Manuscript/computational statistics/version_1/Bayes_Subset_Stat_and_computing_Jin_Goh.tex
major revision 1

--- 2020-02-07 Manuscript/computational statistics/major_revision_1/BayesSubset_SC.tex
@@
 % your LaTeX will extract the file if required
-\begin{filecontents*}{Heatmap.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
+
 %
@@
 %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-\documentclass[twocolumn,natbib]{svjour3}          % twocolumn
+\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
 %
@@
 \usepackage{algorithm}
-\usepackage{url}
-%\usepackage[linkcolor=blue,citecolor=blue]{hyperref}
+\usepackage[colorlinks]{hyperref}
+%\usepackage{natbib}
+\newcommand{\T}{\top} %
+\newcommand{\ua}{\bf a} %
+\newcommand{\ub}{\bf b} %
+\newcommand{\uI}{\bf I} %
+\newcommand{\uH}{\bf H} %
+\newcommand{\uX}{\bf X} %
+\newcommand{\ux}{\bf x} %
+\newcommand{\uy}{\bf y} %
+\newcommand{\ud}{\bf d} %
+\newcommand{\uv}{\bf v} %
+\newcommand{\uu}{\bf u} %
+\newcommand{\um}{\bf m} %
+\newcommand{\0}{\boldsymbol 0} %
+\newcommand{\1}{\boldsymbol 1} %
+\newcommand{\ubeta}{\boldsymbol \beta} %
+\newcommand{\ueta}{\boldsymbol \eta} %
+\newcommand{\umu}{\boldsymbol \mu} %
+\newcommand{\bg}{\boldsymbol \gamma} %
+\newcommand{\uepsilon}{\boldsymbol \epsilon} %
+\newcommand{\uSigma}{\boldsymbol \Sigma} %
+\newcommand{\diag}{\rm diag}
 %
@@
 % please place your own definitions here and don't use \def but
-\newcommand{\T}{{ \top}} %
-\newcommand{\ua}{{\bf a}} %
-\newcommand{\ub}{{\bf b}} %
-\newcommand{\uI}{{\bf I}} %
-\newcommand{\uH}{{\bf H}} %
-\newcommand{\uX}{{\bf X}} %
-\newcommand{\ux}{{\bf x}} %
-\newcommand{\uy}{{\bf y}} %
-\newcommand{\ud}{{\bf d}} %
-\newcommand{\uv}{{\bf v}} %
-\newcommand{\uV}{{\bf V}} %
-\newcommand{\uu}{{\bf u}} %
-\newcommand{\um}{{\bf m}} %
-\newcommand{\0}{{\boldsymbol 0}} %
-\newcommand{\1}{{\boldsymbol 1}} %
-\newcommand{\ubeta}{{\boldsymbol \beta}} %
-\newcommand{\ueta}{{\boldsymbol \eta}} %
-\newcommand{\umu}{{\boldsymbol \mu}} %
-\newcommand{\bg}{{\boldsymbol \gamma}} %
-\newcommand{\uepsilon}{{\boldsymbol \epsilon}} %
-\newcommand{\uSigma}{{\boldsymbol \Sigma}} %
-\newcommand{\diag}{{\rm diag}} %
 % \newcommand{}{}
@@
 % Insert the name of "your journal" with
-\journalname{Computational Statistics}
+% \journalname{myjournal}
 %
@@
 
-\institute{Shiqiang Jin \at Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.\\
+\institute{S. Jin \at
+              Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A. \\
               \email{jinsq@ksu.edu}           %  \\
+%             \emph{Present address:} of F. Author  %  if needed
            \and
-Gyuhyeong Goh \at Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.\\
+           G. Goh \at
+              Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.\\
               \email{ggoh@ksu.edu} 
@@
 
-\date{Received: date / Accepted: date}
+% \date{Received: date / Accepted: date}
 % The correct dates will be entered by the editor
@@
 \begin{abstract}
-Over the past decades, variable selection for high-dimensional data has drawn increasing attention.
+Over the decades, variable selection with high-dimensional data has drawn increasing attention.
 With a large number of predictors, there rises a big challenge for model fitting and prediction.
@@
 In addition, we establish model selection consistency for the proposed method in the high-dimensional setting in which the number of possible predictors can increase faster than the sample size.
-Simulation study and real data analysis are conducted to investigate the performance of the proposed method.
-\keywords{Bayesian variable selection \and  Best subset selection \and High-dimensional regression analysis \and Hybrid search algorithm}
+Simulation study and real data analysis are conducted to investigate the performance of the newly-developed method.
+\keywords{Bayesian variable selection\and Best subset selection\and High-dimensional regression analysis\and Hybrid search algorithm}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 \section{Introduction}\label{sec:1}
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
 Variable selection plays a key role in recent regression analysis.
-In many statistical applications, especially in genetics studies, researchers often face situations where the number of candidate predictors is extremely large but the sample size is relatively small, often referred to as high-dimensional regression problems.
+In many statistical applications, especially in genetics studies, researchers often face situations in which the number of candidate predictors is extremely large but the sample size is relatively small, often referred to as high-dimensional regression problems.
 The most pressing challenge in high-dimensional regression is to identify relevant predictor variables from a large pool of candidates.
-In an attempt to perform high-dimensional variable selection, a lot of effort has been put into the development of penalized likelihood methods (e.g., \citealt{tibshirani1996regression, fan2001variable, zou2005regularization, zhang2010nearly}).
+In an attempt to perform high-dimensional variable selection, a lot of effort has been put into the development of penalized likelihood methods (e.g., \cite{tibshirani1996regression}, \cite{fan2001variable}, \cite{zou2005regularization}, \cite{zhang2010nearly}).
 By adding a penalty function to the likelihood criterion, the penalized likelihood method produces sparse solutions that automatically eliminate the irrelevant predictors from the regression model using the zero-estimates.
 
-In this paper, we are interested in selecting the $k$ most important predictors out of $p$ candidates, called best subset selection \citep{hocking1967selection}.
-It is well known that best subset selection involves nonconvex optimization problems that are computationally intractable in high-dimensional settings.
-Although some penalized likelihood approaches such as Lasso, elastic net, and MCP provide a convex surrogate for nonconvex optimization, their applicability to best subset selection is still limited \citep{bertsimas2016best}.
-Meanwhile, a Bayesian approach to best subset selection, called Bayesian subset regression (BSR), has been proposed by \citet{liang:2013bayesian}.
-Using an adaptive Markov chain Monte Carlo (MCMC) algorithm, called the stochastic approximation Monte Carlo \citep{liang2007stochastic}, BSR finds the best subset by performing a stochastic search over the entire model space.
-However, the stochastic search with a large number of candidate predictors often raises computational challenges including extremely heavy computation and slow convergence.
+% For tables use
+
+In this paper, we are interested in selecting the $k$ most important predictors out of $p$ candidates, called best subset selection \cite{hocking1967selection}.
+It is well known that best subset selection involves non-convex optimization problems that are computationally intractable in high-dimensional settings.
+Although some penalized likelihood approaches such as Lasso, elastic net, and MCP provide a convex surrogate for non-convex optimization, their applicability to best subset selection is still limited \cite{bertsimas2016best}.
+Meanwhile, a Bayesian approach to best subset selection, called Bayesian subset regression (BSR), has been proposed by \cite{liang:2013bayesian}.
+Using an adaptive Markov chain Monte Carlo (MCMC) algorithm, called the stochastic approximation Monte Carlo \cite{liang2007stochastic}, BSR finds the best subset by performing a stochastic search over the entire model space.
+However, the global stochastic search with a large number of candidate predictors often raises computational challenges including heavy computation and slow convergence.
 To overcome this limitation, we introduce a hybrid best subset search algorithm that combines a deterministic local search and a stochastic global search in a Bayesian framework.
-The main attractive feature of our proposed method is that evaluating all possible candidate models for the next update, which is the most expensive part of computation, is simultaneously accomplished in a single computation.
+The main attractive feature of our proposed method is that evaluating all possible candidate models for the next update, which is the most expensive part of Bayesian computation, is simultaneously accomplished in a single computation.
 \section{Basic setup}\label{sec:2}
@@
 Using the kernels of normal density and inverse gamma density, the marginal likelihood can be calculated as
-\begin{eqnarray}
-\label{eq:2} m(\uy|\bg) &=&\int f(\uy|\ubeta_{\bg},\sigma^2)\pi(\ubeta_{\bg}|\sigma^2, \bg) \pi(\sigma^2) d\ubeta_\bg d\sigma^2 \nonumber \\
+\begin{eqnarray}\label{eq:2} 
+m(\uy|\bg) &=&\int f(\uy|\ubeta_{\bg},\sigma^2)\pi(\ubeta_{\bg}|\sigma^2, \bg) \pi(\sigma^2) d{\ubeta_{\bg}} d{\sigma^2} \nonumber \\
 &\propto& \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
     \uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
-	\uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } },
+  \uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}}},
 \end{eqnarray}
 where $f(\uy|\ubeta_{\bg},\sigma^2)$ denotes the reduced model likelihood function given $\bg$ and $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$.
-
 From Bayes' theorem, the posterior model probability of $\bg$ is proportional to $\pi(\bg|\uy)\propto m(\uy|\bg) \pi(\bg)\propto m(\uy|\bg) \mathbb{I}(|\bg|=k )$.
@@
 \begin{itemize}\itemsep=0pt
-\item[a)] Compute $\tilde{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)$;\\ \texttt{\# i.e., select the locally best subset of size k+1} 
-\item[b)] Compute $\hat{\bg}^{(t)}=  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$;\\ \texttt{\# i.e., select the locally best subset of size k} 
+\item[a)] Compute $\tilde{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)$; \quad \texttt{\# select the best subset of size $k+1$ in $ \mathcal{N}_+(\hat{\bg}^{(t-1)})$ }
+\item[b)] Compute $\hat{\bg}^{(t)}=  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$;\quad \texttt{\# select the best subset of size $k$ in $ \mathcal{N}_-(\tilde{\bg}^{(t)})$ } 
 \item[c)] Update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$; 
 \end{itemize}
-\item[] \textbf{until} $\hat{\bg}^{(t-1)}=\hat{\bg}^{(t)}$. \texttt{\# i.e., terminate immediately if no update is made}
+\item[] \textbf{until} $\hat{\bg}^{(t-1)}=\hat{\bg}^{(t)}$. \quad \texttt{\# terminate immediately if no update is made}
 \item[3.] Return $\hat{\bg}$.
@@
 \end{algorithm}
+
 The following theorem proves the convergence of the proposed deterministic search algorithm.
@@
 \begin{proof}[of Theorem \ref{thm:1}] Let $\hat{\bg}^{(t-1)}$ be the best subset of size $k$ updated by the ${t-1}$-th iteration.
-Then, $\hat{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$, where $$\tilde{\bg}^{(t)}=\arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)}  ) } m(\uy|\bg).$$ Since $\hat{\bg}^{(t-1)}$ also belongs to $ \mathcal{N}_-(\tilde{\bg}^{(t)} ) $, we thus have $m(\uy|\hat{\bg}^{(t-1)} ) \leq m(\uy|\hat{\bg}^{(t)}),$ which proves our first statement.
+Then, $\hat{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$, where $\tilde{\bg}^{(t)}=\arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)}  ) } m(\uy|\bg)$.
+Since $\hat{\bg}^{(t-1)}$ also belongs to $ \mathcal{N}_-(\tilde{\bg}^{(t)} ) $, we thus have $m(\uy|\hat{\bg}^{(t-1)} ) \leq m(\uy|\hat{\bg}^{(t)}),$ which proves our first statement.
 Since the number of all possible states of $\bg$ satisfying $|\bg|=k$ is finite, the algorithm terminates in a finite number of iterations.
@@
 \begin{itemize}\itemsep=0pt
-\item[a)] Update $\tilde{\bg}^{(t)}$ by selecting one from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probability $$\frac{m(\uy|\bg)}{\sum_{\bg' \in \mathcal{N}_+(\hat{\bg}^{(t-1)})} m(\uy|\bg')},~\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} );$$
-\item[b)] Update $\hat{\bg}^{(t)}$ by selecting one from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probability $$\frac{m(\uy|\bg)}{\sum_{\bg' \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg')},~\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) ;$$
+\item[a)] Sample $\tilde{\bg}^{(t)}$ from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probabilities proportional to ${m(\uy|\bg)}\mathbb{I}\{\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) \}$; 
+\item[b)] Sample $\hat{\bg}^{(t)}$ from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probabilities proportional to ${m(\uy|\bg)}\mathbb{I}\{\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) \}$;
 \item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$.
@@
 \end{algorithm}
+
 Note that the proposed stochastic search algorithm generates a Markov chain, $\{\hat{\bg}^{(t)},t=1,\ldots,T\}$, with the state space $\{\bg:|\bg|=k\}$.
@@
 
-Although the stochastic search algorithm eventually reaches the global optimum, it requires the large number of iterations, which is computationally inefficient.
+However, while the stochastic search algorithm eventually reaches the global optimum, it requires the large number of iterations, which is computationally inefficient.
 To develop a computationally efficient global optimization algorithm, we propose a hybrid best subset selection algorithm that combines the stochastic global search algorithm and the deterministic local search algorithm into one.
@@
 \item[2.] Set $\hat{\bg}^{(0)}=\hat{\bg}$.
-\item[\texttt{\#}] \texttt{deterministic search step}
-\item[3.] \textbf{Repeat} for $t=1,2,\ldots:$ 
+\item[3.] \textbf{Repeat} for $t=1,2,\ldots:$ \quad \texttt{\#deterministic search step}
 \begin{itemize}\itemsep=0pt
@@
 \item[4.] Set $\hat{\bg}^{(0)}=\hat{\bg}$ and choose a tuning parameter $\alpha \in (0,1]$.
-\item[\quad \texttt{\#}] \texttt{stochastic search step}
-\item[5.] \textbf{Repeat} for $t=1,\ldots,T$: 
+\item[5.] \textbf{Repeat} for $t=1,\ldots,T$: \quad \texttt{\#stochastic search step}
 \begin{itemize}
-\item[a)] Update $\tilde{\bg}^{(t)}$ by drawing one from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probability $$\frac{m(\uy|\bg)^\alpha}{\sum_{\bg\in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)^\alpha},~\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} );$$
-\item[b)] Update $\hat{\bg}^{(t)}$ by drawing one from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probability $$\frac{m(\uy|\bg)^\alpha}{\sum_{\bg' \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg')^\alpha },~\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} );$$
-\item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$ and immediately go to Step 2.
+\item[a)] Sample $\tilde{\bg}^{(t)}$ from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probabilities proportional to ${m(\uy|\bg)^\alpha}\mathbb{I}\{\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) \}$;
+\item[b)] Sample $\hat{\bg}^{(t)}$ from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probabilities proportional to ${m(\uy|\bg)^\alpha}\mathbb{I}\{\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) \}$;
+\item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$, break the loop, and go to Step 2.
 \end{itemize}
@@
 If we set $\alpha=1$, the stochastic search step is analogous to Algorithm \ref{alg:2}.
-In our simulation study and real data analysis, we set $\alpha=\min\{1,\log(2)/\log( m_{(1)} /  m_{(2)} )\}$, where $m_{(1)}$ and $m_{(2)}$ are, respectively, the first and second largest values of $\{m(\uy|\bg):\bg  \in \mathcal{N}_+(\hat{\bg})\}$.
+In our simulation study and real data analysis, we set $\alpha=\min\{1,\log(2)/\log( m_{(1)} /  m_{(2)} )\}$, where $m_{(1)}$ and $m_{(2)}$ denote the first and second largest values of $\{m(\uy|\bg)
+: \bg  \in \mathcal{N}_+(\hat{\bg}) \}$.
 
@@
 For any $i\notin \hat{\bg}$, it can be shown that
-\begin{eqnarray}
- \nonumber&& m(\uy|\hat{\bg}\cup\{i\}) \\
- \nonumber&&\propto \left\{\uy^{\T}\uH_{\hat{\bg}}\uy-\frac{(
+\begin{eqnarray}\label{eq:app:1}
+ m(\uy|\hat{\bg}\cup\{i\}) &\propto& \left\{\uy^{\T}\uH_{\hat{\bg}}\uy-\frac{(
   \ux_i^{\T}\uH_{\hat{\bg}}\uy)^2}{\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i }+b_{\sigma}\right\}^
- {-\frac{a_{\sigma}+n}{2}} \\
- \label{eq:app:1} & &\quad \times (\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i)^{-1/2},
+ {-\frac{a_{\sigma}+n}{2}}\times\nonumber\\
+ &&(\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i)^{-1/2},
 \end{eqnarray}
 where $\ux_i$ is the $i$-th column of $\uX$.
-The proof of \eqref{eq:app:1} is given in Appendix \ref{app:1}.
+The proof of \eqref{eq:app:1} is given in \ref{app:1}.
 Note that $\ux_i^{\T}\uH_{\hat{\bg}}\ux_i$ is the $i$-th diagonal element of $\uX^{\T}\uH_{\hat{\bg}}\uX$ and that $\ux_i^{\T}\uH_{\hat{\bg}}\uy$ is the $i$-th element of $\uX^{\T}\uH_{\hat{\bg}}\uy$.
@@
 \begin{eqnarray*}
-&&\um_+({\hat{\bg}})=\\
-&& \left\{(\uy^{\T}\uH_{\hat{\bg}}\uy+b_{\sigma}) \1_p-\frac{(\uX^{\T}\uH_{\hat{\bg}}\uy)^2}{\frac{1}{\tau}\1_p+\diag(\uX^{\T}\uH_{\hat{\bg}}\uX) } \right\}^
+\um_+({\hat{\bg}})&=& \left\{(\uy^{\T}\uH_{\hat{\bg}}\uy+b_{\sigma}) \1_p-\frac{(\uX^{\T}\uH_{\hat{\bg}}\uy)^2}{\tau^{-1}\1_p+\diag(\uX^{\T}\uH_{\hat{\bg}}\uX) } \right\}^
  {-\frac{a_{\sigma}+n}{2}}\\
- &&\quad \times\left\{\frac{1}{\tau} \1_p  +\diag(\uX^{\T}\uH_{\hat{\bg}}\uX) \right\}^{-1/2},
+ &&\times\left\{\tau^{-1} \1_p  +\diag(\uX^{\T}\uH_{\hat{\bg}}\uX) \right\}^{-1/2},
  \end{eqnarray*}
- where $\ua^x$ and $\ua/\ub$ indicate entrywise operations for generic vectors $\ua$ and $\ub$, accordingly.
-For example, $\ua^x=(a_1^x,\ldots, a_p^x)$ and $\ua/\ub=(a_1/b_1,\ldots,a_p/b_p)$.
-Note that $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{i\}:i\notin \hat{\bg} \}$.
-Therefore, evaluating $m(\uy|\bg)$ for all $\bg \in \mathcal{N}_+(\hat{\bg} )$ can be done simultaneously in a single computation by obtaining the sub-vector of $\um_+({\hat{\bg}})$ for $\{i:i\notin \hat{\bg} \}$.
+ where $\ua^x$ and $\ua/\ub$ denote entrywise operations for generic vectors $\ua$ and $\ub$, accordingly, i.e., $\ua^x=(a_1^x,\ldots, a_p^x)$ and $\ua/\ub=(a_1/b_1,\ldots,a_p/b_p)$.
+Since $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{i\}:i\notin \hat{\bg} \}$, evaluating $m(\uy|\bg)$ for all $\bg \in \mathcal{N}_+(\hat{\bg} )$ can be done simultaneously in a single computation by obtaining the sub-vector of $\um_+({\hat{\bg}})$ for $\{i:i\notin \hat{\bg} \}$.
 Similarly, for any $j \in\tilde{\bg}$, we can show that
- \begin{eqnarray}
- \nonumber&&m(\uy|\tilde{\bg}\setminus \{j\}) \\
- \nonumber &&\propto \left\{\uy^{\T}\uH_{\tilde{\bg}}\uy+\frac{(
+ \begin{eqnarray}\label{eq:app:2}
+ m(\uy|\tilde{\bg}\setminus \{j\})  &\propto& \left\{\uy^{\T}\uH_{\tilde{\bg}}\uy+\frac{(
   \ux_j^{\T}\uH_{\tilde{\bg}}\uy)^2}{\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j }+b_{\sigma}\right\}^
- {-\frac{a_{\sigma}+n}{2}}\\
-\label{eq:app:2}&&\quad \times (\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j)^{-1/2}.
+ {-\frac{a_{\sigma}+n}{2}}\times\nonumber\\
+ &&(\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j)^{-1/2}.
 \end{eqnarray} The proof of \eqref{eq:app:2} is given in \ref{app:2}. Define
 \begin{eqnarray*}
-&&\um_-({\tilde{\bg}}) =\\
-&& \left\{(\uy^{\T}\uH_{\tilde{\bg}}\uy+b_{\sigma}) \1_p+\frac{(\uX^{\T}\uH_{\tilde{\bg}}\uy)^2}{\frac{1}{\tau}\1_p-\diag(\uX^{\T}\uH_{\tilde{\bg}}\uX) } \right\}^
+\um_-({\tilde{\bg}}) &=& \left\{(\uy^{\T}\uH_{\tilde{\bg}}\uy+b_{\sigma}) \1_p+\frac{(\uX^{\T}\uH_{\tilde{\bg}}\uy)^2}{\tau^{-1}\1_p-\diag(\uX^{\T}\uH_{\tilde{\bg}}\uX) } \right\}^
  {-\frac{a_{\sigma}+n}{2}}\\
- &&\quad \times\left\{\frac{1}{\tau} \1_p  -\diag(\uX^{\T}\uH_{\tilde{\bg}}\uX) \right\}^{-1/2}.
+ &&\times\left\{\tau^{-1} \1_p  -\diag(\uX^{\T}\uH_{\tilde{\bg}}\uX) \right\}^{-1/2}.
  \end{eqnarray*}
@@
 In this section, we extend the proposed method to handle the case of varying $k \leq K$, where $K$ is a prespecified upper bound.
-This is a common setting for high-dimensional best subset selection problems (e.g., \citealt{bertsimas2016best, liang:2013bayesian}).
+This is a common setting for high-dimensional best subset selection problems (e.g., \cite{bertsimas2016best}, \cite{liang:2013bayesian}).
 In a Bayesian framework, this extension can be easily done by assigning an appropriate prior for unknown $k$.
@@
 However, the uniform prior tends to assign larger probability to a larger subset due to the fact that the total number of subsets of size $k$ is $\binom{p}{k}$, which tends to increase exponentially as $k$ increases.
-To resolve this issue, using a similar idea of \citet{chen2008extended}, we consider
+To resolve this issue, using a similar idea of \cite{chen2008extended}, we consider
 \begin{eqnarray*}
@@
  \end{eqnarray*}
-Therefore, the optimization problem in Eq. \eqref{joint:opt} can be solved by proceeding the following steps:
+Hence, the optimization problem in Eq. \eqref{joint:opt} can be solved by proceeding the following steps:
 \begin{enumerate}
-\item For $k=1,\ldots,K$, compute $$\hat{\bg}_k= \arg\max_{\bg:|\bg|=k} m(\uy|\bg)$$ using Algorithm \ref{alg:3}.
-\item Compute $$ \hat{k}=\arg\max_{1\leq k \leq K} \left\{\log m(\uy|\hat{\bg}_k)-\log \binom{p}{k} \right\}.$$
+\item For $k=1,\ldots,K$, compute $\hat{\bg}_k= \arg\max_{\bg}\left\{m(\uy|\bg)\mathbb{I}(|\bg|=k)\right\}$ using Algorithm \ref{alg:3}.
+\item Compute $ \hat{k}=\arg\max_{1\leq k \leq K} \left\{\log m(\uy|\hat{\bg}_k)-\log \binom{p}{k} \right\}$.
 \item Return $\hat{\bg}=\hat{\bg}_{\hat{k}}$.
@@
 
-\begin{theorem}\label{thm:2} Define $\Gamma=\{\bg:|\bg|\leq K,\bg\neq \bg_*\}$, where $\bg_*$ is the true model.
+\begin{theorem}\label{thm:2} Let $\bg_*$ indicate the true model.
+Define $\Gamma=\{\bg:|\bg|\leq K,\bg\neq \bg_*\}$.
 Assume that $p=O(n^\xi)$ for $\xi\geq 1$.
-Under the asymptotic identifiability condition of \citet{chen2008extended}, if $\tau\to \infty$ as $n\to \infty$ but $\tau=o(n)$, then the proposed Bayesian subset selection possesses the Bayesian model selection consistency, that is,
+Under the asymptotic identifiability condition of \cite{chen2008extended}, if $\tau\to \infty$ as $n\to \infty$ but $\tau=o(n)$, then the proposed Bayesian subset selection possesses the Bayesian model selection consistency, that is,
 \begin{eqnarray}\label{thm:2:eq}
@@
 \end{theorem}
-\begin{proof}[of Theorem \ref{thm:2}]  From the Laplace approximation of \citet{kass1995}, we have
+\begin{proof}[of Theorem \ref{thm:2}]  From the Laplace approximation of \cite{kass1995}, we have
 \begin{eqnarray*}
-\log m(\uy|\bg) = \log f(\uy|\hat{\ubeta}_\bg, \hat{\sigma}^2)-\frac{|\bg|}{2}\log n+o_p(\log n ),
+\log m(\uy|\bg) = \log f(\uy|\hat{\ubeta}_{\bg}, \hat{\sigma}^2)-\frac{|\bg|}{2}\log n+o_p(\log n ),
 \end{eqnarray*}
-where  $\hat{\ubeta}_\bg= (\uX_\bg^\T \uX_{\bg})^{-1} \uX_{\bg}^\T \uy$ and $\hat{\sigma}^2=\|\uH_{\bg}\uy\|^2/n$.
+where  $\hat{\ubeta}_{\bg}= (\uX_{\bg}^{\T} \uX_{\bg})^{-1} \uX_{\bg}^{\T} \uy$ and $\hat{\sigma}^2=\|\uH_{\bg}\uy\|^2/n$.
 Ignoring a smaller order term than $\log n$, our posterior criterion \eqref{joint:opt} can be approximated as
-\begin{eqnarray}
-\nonumber -2 \log \pi(\bg |\uy) &\approx& -2 \log f(\uy|\hat{\ubeta}_\bg,\hat{\sigma}^2)\\
-\label{ebic}&&+{|\bg|}\log n+2\log \binom{p}{k},
+\begin{eqnarray}\label{ebic}
+-2 \log \pi(\bg |\uy) \approx -2 \log f(\uy|\hat{\ubeta}_{\bg},\hat{\sigma}^2)+{|\bg|}\log n+2\log \binom{p}{k},
 \end{eqnarray}
-which is equivalent to the extended Bayesian information criterion \citep{chen2008extended}.
-Therefore, it follows from Theorem 1 of \citet{chen2008extended} that Eq.
+which is equivalent to the extended Bayesian information criterion \cite{chen2008extended}.
+Therefore, it follows from Theorem 1 of \cite{chen2008extended} that Eq.
 \eqref{thm:2:eq} holds in probability.
@@
 \begin{eqnarray*}
-y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},\sigma^2_y\right),
+y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},1\right),
 \end{eqnarray*}
-where $(x_{i1},\ldots,x_{ip})$ follows $\text{Normal}(\0_p,\uV)$ with $\uV=(v_{ij})_{p\times p}$ and $v_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$, and $\sigma^2_y$ is variance of error item.
+where $(x_{i1},\ldots,x_{ip})^\T \overset{iid}{\sim}\text{Normal}(\0_p,\uSigma)$ with $\uSigma=(\Sigma_{ij})_{p\times p}$ and $\Sigma_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$.
 
-We consider four different cases: 
-\begin{itemize}
-	\item [(i)] $p=200$, $\rho=0.1$, $\sigma^2_y = 1$,
-	\item [(ii)] $p=200$, $\rho=0.9$, $\sigma^2_y = 1$,
-	\item [(iii)] $p=1000$, $\rho=0.1$, $\sigma^2_y = 1$,
-	\item [(iv)] $p=1000$, $\rho=0.9$, $\sigma^2_y = 1$,
-	\item [(v)] $p=200$, $\rho=0.1$, $\sigma^2_y = 2$,
-	\item [(vi)] $p=200$, $\rho=0.9$, $\sigma^2_y = 2$,
-	\item [(vii)] $p=1000$, $\rho=0.1$, $\sigma^2_y = 2$,
-	\item [(viii)] $p=1000$, $\rho=0.9$, $\sigma^2_y = 2$.
-\end{itemize}
+We consider four different scenarios: (i) $p=200$, $\rho=0.1$, (ii) $p=200$, $\rho=0.9$, (iii) $p=1000$, $\rho=0.1$, and (iv) $p=1000$, $\rho=0.9$.
 We assume that there is no prior information.
@@
 We further assume that the true number of active predictors is unknown.
-Hence, we employ the proposed method in Section \ref{sec:4} for varying $k$ with $K=\lceil n^{2/3} \rceil =22$.
-For the hybrid search algorithm given in Algorithm \ref{alg:3}, we set $T=100$, which is a remarkably small number of iterations compared to existing stochastic search algorithms (e.g., \citealt{kirkpatrick1983optimization, george1993variable, hans2007shotgun}), and marginal correlations between the response and each predictor are used to define the initial value of $\hat{\bg}$.
-For comparison purposes, we also employ four popular penalized likelihood methods: LASSO \citep{tibshirani1996regression}, the elastic net \citep{zou2005regularization}, SCAD \citep{fan2001variable}, and MCP \citep{zhang2010nearly}, where the regularization parameters or tuning parameters are determined by the extended BIC in \eqref{ebic} to achieve a fair comparison with the proposed method.
-In this simulation study, LASSO and ENET are implemented by R package \texttt{glmnet} and  MCP and SCAD are performed by R package \texttt{ncvreg}.
+Hence, we employ the proposed method with unknown $k$ in Section \ref{sec:4} with $K=\lceil n^{2/3} \rceil =22$.
+For the hybrid search algorithm given in Algorithm \ref{alg:3}, we set $T=100$, which is a remarkably small number of iterations compared to existing stochastic search algorithms (e.g., \cite{kirkpatrick1983optimization, \cite{george1993variable}, \cite{hans2007shotgun}), and marginal correlations between the response and each predictor are used to define the initial value of $\hat{\bg}$.
+For comparison purposes, we also employ four popular penalized likelihood methods: LASSO \cite{tibshirani1996regression}, the elastic net \cite{zou2005regularization}, SCAD \cite{fan2001variable}, and MCP \cite{zhang2010nearly}, where the regularization parameters or tuning parameters are determined by the extended BIC in \eqref{ebic} to achieve a fair comparison with the proposed method.\textcolor{red}{We use R package ``glmnet'' to implement LASSO and ENET , and use ``ncvreg'' for MCP and SCAD}.
 To evaluate the variable selection performance, we calculate false discovery rate, percentage of selecting the exact true model, average size of the selected model, and mean of Hamming distance based on $2,000$ Monte Carlo replications.
 False discovery rate is defined as $|\hat{\bg}\setminus \bg_*|/|\hat{\bg}|$ and Hamming distance is defined as $|\hat{\bg}\setminus \bg_* |+|\bg_* \setminus  \hat{\bg}|$, where $\bg_*$ denotes the index set of the true model.
-
-\begin{table}[h]
+\begin{table}[H]
 \centering
-  \caption{Simulation study results based on $2,000$ Monte Carlo replications for cases i--iv.
-Notation: FDR---false discovery rate; TRUE---percentage of the true model detected; SIZE---selected model size; HAM---Hamming distance; s.e.--- standard error.}\label{T:sim1}
-\begin{tabular}{c|ccccc}
+  \caption{Simulation study results based on $2,000$ Monte Carlo replications for scenarios i--iv.
+Notation: FDR---false discovery rate; TRUE\%---percentage of the true model detected; SIZE---selected model size; HAM---Hamming distance; s.e.--- standard error.}\label{T:sim1}
+%\scalebox{0.8}{
+\begin{tabular}{cccccc}
 \hline
- & &FDR& TRUE & SIZE & HAM   \\
-Case &Method& (s.e.) & (s.e.)   & (s.e.)     & (s.e.)    \\
+  Scenario & Method                         & FDR  (s.e.)    & TRUE\% (s.e.)   & SIZE (s.e.)     & HAM (s.e.)    \\
 \hline
-    i      & Proposed & 0.006   & 96.900  & 4.032   & 0.032  \\
-          & & (0.001)  & (0.388)  & (0.004)    & (0.004) \\
-           & SCAD                           & 0.034 & 85.200  & 4.188  & 0.188 \\
-           &                         & (0.002)  & (0.794)  &(0.011)   & (0.011) \\
-           & MCP                            & 0.035  & 84.750 & 4.191  & 0.191  \\
-           &                             &  (0.002)  &  (0.804)  & (0.011)   & (0.011) \\
-           & ENET                           & 0.016  & 92.700  & 4.087  & 0.087  \\
-           &                            &(0.001)  & (0.582)  &  (0.007)   & (0.007) \\
-           & LASSO                          & 0.020  & 91.350  & 4.109   & 0.109\\
-           &                          & (0.002)  &  (0.629)  & (0.009)   & (0.009) \\
-           \hline
-  ii         & Proposed & 0.023 & 88.750& 3.985  & 0.203\\
-           &  & (0.002) & (0.707) & (0.006)  & (0.014) \\
-
-           & SCAD                           & 0.059& 74.150  & 4.107   & 0.480  \\
-           &                        & (0.003)  & (0.979)  & (0.015)   & (0.022) \\
-           & MCP                            & 0.137  & 55.400  & 4.264   & 1.098  \\
-           &                        & (0.004)  &  (1.112)  &(0.020)   &  (0.034) \\
-           & ENET                           & 0.501   & 0.300   & 7.716  & 5.018  \\
-           &                        & (0.004)  &  (0.122)   & (0.072)   &  (0.052) \\
-           & LASSO                          & 0.276  & 15.550 & 5.308  & 2.038  \\
-           &                          & (0.004)  & (0.811)  & (0.033)   & (0.034) \\
-             \hline
-  iii         & Proposed & 0.004  & 98.100 & 4.020 & 0.020 \\
-          &  &(0.001)   & (0.305)  & (0.003)    & (0.003) \\
-           & SCAD                           & 0.027 & 87.900& 4.145   & 0.145\\
-           &                           & (0.002)  & (0.729)  &(0.010)   & (0.010) \\
-           & MCP                            & 0.031  & 86.550 & 4.172  & 0.172\\
-           &                            & (0.002)  & (0.763)  & (0.013)   & (0.013) \\
-           & ENET                           & 0.035 & 84.850& 4.181 & 0.206\\
-           &                           & (0.002)  & (0.802)  & (0.013)   & (0.012) \\
-           & LASSO                          & 0.014 & 93.850 & 4.073 & 0.073\\
-           &                          &(0.001)  &(0.537)  &(0.007)   &(0.007) \\
-             \hline
-   iv      & Proposed & 0.023  & 89.850& 4.005& 0.190 \\
-         & & (0.002)   & (0.675)  & (0.005) &(0.013) \\
-           & SCAD                           & 0.068 & 74.250& 4.196 & 0.493\\
-           &                            & (0.003)  & (0.978)  & (0.014)   & (0.023) \\
-           & MCP                            & 0.152 & 53.750 & 4.226 & 1.202 \\
-           &                           & (0.004)  & (1.115)  & (0.017)   & (0.035) \\
-           & ENET                           & 0.417 & 0.150& 6.228& 4.089 \\
-           &                           & (0.005)  & (0.087)   & (0.068)   & (0.043) \\
-           & LASSO                          & 0.265& 19.500 & 5.139 & 1.909 \\
-           &                          & (0.004)  &(0.886)  &(0.029)   & (0.035) \\
+    i       & Proposed & 0.006 (0.001)  & 96.900 (0.388)  & 4.032 (0.004)    & 0.032 (0.004) \\
+           & SCAD                           & 0.034 (0.002)  & 85.200 (0.794)  & 4.188 (0.011)   & 0.188 (0.011) \\
+           & MCP                            & 0.035 (0.002)  & 84.750 (0.804)  & 4.191 (0.011)   & 0.191 (0.011) \\
+           & ENET                           & 0.016 (0.001)  & 92.700 (0.582)  & 4.087 (0.007)   & 0.087 (0.007) \\
+           & LASSO                          & 0.020 (0.002)  & 91.350 (0.629)  & 4.109 (0.009)   & 0.109 (0.009) \\
+  ii         & Proposed & 0.023 (0.002) & 88.750 (0.707) & 3.985 (0.006)  & 0.203 (0.014) \\
+           & SCAD                           & 0.059 (0.003)  & 74.150 (0.979)  & 4.107 (0.015)   & 0.480 (0.022) \\
+           & MCP                            & 0.137 (0.004)  & 55.400 (1.112)  & 4.264 (0.020)   & 1.098 (0.034) \\
+           & ENET                           & 0.501 (0.004)  & 0.300 (0.122)   & 7.716 (0.072)   & 5.018 (0.052) \\
+           & LASSO                          & 0.276 (0.004)  & 15.550 (0.811)  & 5.308 (0.033)   & 2.038 (0.034) \\
+  iii         & Proposed & 0.004 (0.001)   & 98.100 (0.305)  & 4.020 (0.003)    & 0.020 (0.003) \\
+           & SCAD                           & 0.027 (0.002)  & 87.900 (0.729)  & 4.145 (0.010)   & 0.145 (0.010) \\
+           & MCP                            & 0.031 (0.002)  & 86.550 (0.763)  & 4.172 (0.013)   & 0.172 (0.013) \\
+           & ENET                           & 0.035 (0.002)  & 84.850 (0.802)  & 4.181 (0.013)   & 0.206 (0.012) \\
+           & LASSO                          & 0.014 (0.001)  & 93.850 (0.537)  & 4.073 (0.007)   & 0.073 (0.007) \\
+   iv      & Proposed & 0.023 (0.002)   & 89.850 (0.675)  & 4.005 (0.005) & 0.190 (0.013) \\
+           & SCAD                           & 0.068 (0.003)  & 74.250 (0.978)  & 4.196 (0.014)   & 0.493 (0.023) \\
+           & MCP                            & 0.152 (0.004)  & 53.750 (1.115)  & 4.226 (0.017)   & 1.202 (0.035) \\
+           & ENET                           & 0.417 (0.005)  & 0.150 (0.087)   & 6.228 (0.068)   & 4.089 (0.043) \\
+           & LASSO                          & 0.265 (0.004)  & 19.500 (0.886)  & 5.139 (0.029)   & 1.909 (0.035) \\
 \hline
@@
 \end{table}
-
 The results are shown in Table \ref{T:sim1}.
-For every case, the proposed method outperforms all the penalized likelihood methods.
+For every scenario, the proposed method outperforms all the penalized likelihood methods.
 The proposed method always achieves the smallest false discovery rate and this implies that the proposed method provides the minimum proportion of incorrectly identifying the true active predictors as inactive.
@@
 Hence, this finite sample performance supports our theoretical result in Theorem \ref{thm:2}.
-
 \section{Real data application}
-In this section, we apply the proposed method to Breast invasive carcinoma (BRCA) data, which are generated by The Cancer Genome Atlas (TCGA) Research Network: \url{http://cancergenome.nih.gov}.
+In this section, we apply the proposed method to Breast invasive carcinoma (BRCA) data generated by The Cancer Genome Atlas (TCGA) Research Network: \url{http://cancergenome.nih.gov}.
 We download BRCA data using \texttt{R} package \texttt{curatedTCGAData}.
 The data set contains $17,814$ gene expression measurements (recorded on the log scale) of $526$ patients with primary solid tumor in TCGA project.
-BRCA1 is a well-known tumor suppressor gene and its mutations predispose women to breast cancer \citep{findlay2018accurate}.
+BRCA1 is a well-known tumor suppressor gene and its mutations predispose women to breast cancer \cite{findlay2018accurate}.
 Our goal here is to identify the best fitting model for estimating an association between BRCA1 (response variable) and the other genes (independent variables).
@@
 Then, the proposed method and the penalized likelihood methods as in Section \ref{sec:5} are applied to the reduced data with $n=526$ and $p=5,000$.
-To assess model fitting, for each method, we compute BIC \citep{schwarz1978}, extended BIC, and mean squared prediction error (MSPE) for the ordinary least squares (OLS) estimate that are obtained by using the selected predictors, where MSPE is estimated by Monte Carlo cross-validation over $500$ replications based on $70\%$ of training set and $30\%$ of testing set.
+To assess model fitting, for each method, we compute BIC \cite{schwarz1978}, extended BIC, and mean squared prediction error (MSPE) using the ordinary least square (OLS) estimate with the selected predictors, where MSPE is estimated by Monte Carlo cross-validation over $500$ replications using $70\%$ of training set and $30\%$ of testing set.
 
@@
 
+% \begin{figure}[t]
+% \centerline{\includegraphics[width=300pt]{Heatmap.eps}}
+% \caption{A heatmap of OLS coefficient estimates with p-values for the selected predictors.\label{Fig:heatmap}}
+% \end{figure}
+
+% For one-column wide figures use
 \begin{figure}
-\centering
-\includegraphics[width=0.48\textwidth]{heatmap.eps}
-\caption{A heatmap of OLS coefficient estimates for the selected predictors with p-values.\label{Fig:heatmap}}
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+\includegraphics[width=0.5\textwidth]{Heatmap.eps}
+% figure caption is below the figure
+\caption{A heatmap of OLS coefficient estimates with p-values for the selected predictors}
+\label{Fig:heatmap}       % Give a unique label
 \end{figure}
+% \begin{figure*}
+% % Use the relevant command to insert your figure file.
+% % For example, with the graphicx package use
+%   \includegraphics[width=0.75\textwidth]{example.eps}
+% % figure caption is below the figure
+% \caption{Please write your figure caption here}
+% \label{fig:2}       % Give a unique label
+% \end{figure*}
 
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{rrrrr}
-		\hline
-		& NSP & MSE\_Pred & BIC & EBIC \\ 
-		\hline
-		Proposed & 8.00 & 0.60 & 985.93 & 1120.87 \\ 
-		SCAD & 4.00 & 0.68 & 1104.69 & 1176.42 \\ 
-		MCP & 4.00 & 0.68 & 1104.69 & 1176.42 \\ 
-		ENET & 5.00 & 0.68 & 1110.65 & 1198.68 \\ 
-		LASSO & 4.00 & 0.68 & 1104.69 & 1176.42 \\ 
-		\hline
-	\end{tabular}
-\end{table}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.48\textwidth]{heatmap1.pdf}
-	\caption{A heatmap of OLS coefficient estimates for the selected predictors with p-values without screening.\label{Fig:heatmap1}}
-\end{figure}
-
+% For one-column wide figures use
+% \begin{figure}
+% % Use the relevant command to insert your figure file.
+% % For example, with the graphicx package use
+%   \includegraphics{example.eps}
+% % figure caption is below the figure
+% \caption{Please write your figure caption here}
+% \label{fig:1}       % Give a unique label
+% \end{figure}
+%
+% For two-column wide figures use
+% \begin{figure*}
+% % Use the relevant command to insert your figure file.
+% % For example, with the graphicx package use
+%   \includegraphics[width=0.75\textwidth]{example.eps}
+% % figure caption is below the figure
+% \caption{Please write your figure caption here}
+% \label{fig:2}       % Give a unique label
+% \end{figure*}
+%
 \section{Discussion}
-The proposed hybrid search approach is computationally beneficial and practically effective compared with traditional stochastic search algorithms that are commonly used in Bayesian variable selection.
-Although the idea of searching over the neighborhood is somewhat similar to that of the MCMC model composition (MC$^3$) algorithm \citep{madigan1995bayesian} and the shotgun stochastic search (SSS) algorithm \citep{hans2007shotgun}, our search strategy is completely different from the existing methods.
+The proposed hybrid search approach is computationally attractive compared with traditional stochastic search algorithms that are commonly used in Bayesian variable selection.
+Although the idea of searching over the neighborhood is somewhat similar to that of the MCMC model composition (MC$^3$) algorithm \cite{madigan1995bayesian} and the shotgun stochastic search (SSS) algorithm \cite{hans2007shotgun}, our search strategy is completely different from the existing methods.
 While MC$^3$ and SSS perform a stochastic search over the model space of all possible candidates, we implement a hybrid search over the sub-model space of size $k$.
@@
 
-In addition, as mentioned in Section \ref{sec:4}, parallel computing, which executes many calculations simultaneously using multiple nodes or multiple processors, can be employed in the proposed framework.
+As mentioned in Section \ref{sec:4}, parallel computing, which executes many calculations simultaneously using multiple nodes or multiple processors, can be employed in the proposed framework.
 Our hybrid search algorithm can be also extended to multivariate regression and binary regression in a Bayesian framework.
 Such works are in progress by the authors.
+% \begin{table}
+% % table caption is above the table
+% \caption{Please write your table caption here}
+% \label{tab:1}       % Give a unique label
+% % For LaTeX tables use
+% \begin{tabular}{lll}
+% \hline\noalign{\smallskip}
+% first & second & third  \\
+% \noalign{\smallskip}\hline\noalign{\smallskip}
+% number & number & number \\
+% number & number & number \\
+% \noalign{\smallskip}\hline
+% \end{tabular}
+% \end{table}
+
+%\begin{acknowledgements}
+%If you'd like to thank anyone, place your comments here
+%and remove the percent signs.
+%\end{acknowledgements}
+
+% Authors must disclose all relationships or interests that 
+% could have direct or potential influence or impart bias on 
+% the work: 
+%
+% \section*{Conflict of interest}
+%
+% The authors declare that they have no conflict of interest.
+
+% BibTeX users please use one of
+%\bibliographystyle{spbasic}      % basic style, author-year citations
+%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+%\bibliography{}   % name your BibTeX data base
+\bibliographystyle{plainnat} 
+\bibliography{plainnat}
 
@@
 For any $i \notin \hat{\bg}$, from Eq. \eqref{eq:2}, we have
-\begin{eqnarray}
-\nonumber m(\uy|\hat{\bg}\cup\{i\})&\propto& |\uX_{\hat{\bg}\cup\{i\} }^{\T}\uX_{\hat{\bg}\cup\{i\} }+\tau^{-1}\uI_{k+1} |^{-1/2} \\
- \label{fact:0}&&\times \left(\uy^{\T}\uH_{\hat{\bg}\cup\{i\}}\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2} }.
+\begin{eqnarray} \label{fact:0}
+m(\uy|\hat{\bg}\cup\{i\})&\propto& |\uX_{\hat{\bg}\cup\{i\} }^{\T}\uX_{\hat{\bg}\cup\{i\} }+\tau^{-1}\uI_{k+1} |^{-1/2}\times\nonumber\\
+&&\left(\uy^{\T}\uH_{\hat{\bg}\cup\{i\}} \uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2} }.
 \end{eqnarray}
@@
 Using the Sylvester's determinant identity and the Sherman-Morrison formula, we obtain 
-\begin{eqnarray}
-	\nonumber &&|\uX_{\hat{\bg}\cup\{i\} }^{\T}\uX_{\hat{\bg}\cup\{i\} }+\tau^{-1}\uI_{k+1}   | \\
-	\nonumber &&= \tau^{-(k+1)}|\tau \uX_{\hat{\bg}\cup\{i\} }\uX_{\hat{\bg}\cup\{i\} }^{\T}+\uI_n |\nonumber\\
-	\nonumber &&= \tau^{-(k+1)}|\tau \uX_{\hat{\bg}}\uX_{\hat{\bg}}^{\T}+\uI_n+\tau \ux_i \ux_i^{\T} |\nonumber\\
-	\nonumber &&=  \tau^{-(k+1)} |\tau \uX_{\hat{\bg}}\uX_{\hat{\bg}}^{\T}+\uI_n| \{1+ \tau \ux_i^{\T}
+\begin{eqnarray}\label{fact:2}
+&&|\uX_{\hat{\bg}\cup\{i\} }^{\T}\uX_{\hat{\bg}\cup\{i\} }+\tau^{-1}\uI_{k+1}   |\\
+ &=& \tau^{-(k+1)}|\tau \uX_{\hat{\bg}\cup\{i\} }\uX_{\hat{\bg}\cup\{i\} }^{\T}+\uI_n |\nonumber\\
+  &=& \tau^{-(k+1)}|\tau \uX_{\hat{\bg}}\uX_{\hat{\bg}}^{\T}+\uI_n+\tau \ux_i \ux_i^{\T} |\nonumber\\
+  &=&  \tau^{-(k+1)} |\tau \uX_{\hat{\bg}}\uX_{\hat{\bg}}^{\T}+\uI_n| \{1+ \tau \ux_i^{\T}
   (\tau \uX_{\hat{\bg}}\uX_{\hat{\bg}}^{\T}+\uI_n)^{-1}\ux_i\}\nonumber\\
-	\label{fact:2} &&=| \uX_{\hat{\bg}}^{\T}\uX_{\hat{\bg}}+\tau^{-1}\uI_{k}| (\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i).
+  &=&| \uX_{\hat{\bg}}^{\T}\uX_{\hat{\bg}}+\tau^{-1}\uI_{k}| (\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i).
 \end{eqnarray}
@@
  m(\uy|\hat{\bg}\cup\{i\}) &\propto& \left\{\uy^{\T}\uH_{\hat{\bg}}\uy-\frac{(
- 	\ux_i^{\T}\uH_{\hat{\bg}}\uy)^2}{\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i }+b_{\sigma}\right\}^
- {-\frac{a_{\sigma}+n}{2}}\\
- &&\times (\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i)^{-1/2}
+  \ux_i^{\T}\uH_{\hat{\bg}}\uy)^2}{\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i }+b_{\sigma}\right\}^{-\frac{a_{\sigma}+n}{2}}\times\\
+ &&(\tau^{-1}+\ux_i^{\T}\uH_{\hat{\bg}} \ux_i)^{-1/2}
 \end{eqnarray*}
@@
 For any $j \in \tilde{\bg}$, Eq. \eqref{eq:2} leads to
-\begin{eqnarray}
-\nonumber m(\uy|\tilde{\bg}\setminus\{j\})&\propto& |\uX_{\tilde{\bg}\setminus\{j\} }^{\T}\uX_{\tilde{\bg}\setminus\{j\}}+\tau^{-1}\uI_{k} |^{-1/2} \\
- \label{fact:0-1}&&\times  \left(\uy^{\T}\uH_{\tilde{\bg}\setminus\{j\}}\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2} }.
+\begin{eqnarray} \label{fact:0-1}
+m(\uy|\tilde{\bg}\setminus\{j\})&\propto& |\uX_{\tilde{\bg}\setminus\{j\} }^{\T}\uX_{\tilde{\bg}\setminus\{j\}}+\tau^{-1}\uI_{k} |^{-1/2}\times\nonumber\\  
+&&\left(\uy^{\T}\uH_{\tilde{\bg}\setminus\{j\}}\uy+b_{\sigma}\right)^{-\frac{a_{\sigma}+n}{2} }.
 \end{eqnarray}
@@
 From the Sylvester's determinant identity and the Sherman-Morrison formula, we obtain 
-\begin{eqnarray}
-	\nonumber &&|\uX_{\tilde{\bg}\setminus\{j\}}^{\T}\uX_{\tilde{\bg}\setminus\{j\} }+\tau^{-1}\uI_{k}   | \\
-	&&= \tau^{-k}|\tau \uX_{\tilde{\bg}\setminus\{j\} }\uX_{\tilde{\bg}\setminus\{j\} }^{\T}+\uI_n |\nonumber\\
-	&&= \tau^{-k}|\tau \uX_{\tilde{\bg}}\uX_{\tilde{\bg}}^{\T}+\uI_n-\tau \ux_j \ux_j^{\T} |\nonumber\\
-	&&=  \tau^{-k} |\tau \uX_{\tilde{\bg}}\uX_{\tilde{\bg}}^{\T}+\uI_n| \{1- \tau \ux_j^{\T}
+\begin{eqnarray}\label{fact:2-1}
+&&|\uX_{\tilde{\bg}\setminus\{j\}}^{\T}\uX_{\tilde{\bg}\setminus\{j\} }+\tau^{-1}\uI_{k}   | \\
+&=& \tau^{-k}|\tau \uX_{\tilde{\bg}\setminus\{j\} }\uX_{\tilde{\bg}\setminus\{j\} }^{\T}+\uI_n |\nonumber\\
+  &=& \tau^{-k}|\tau \uX_{\tilde{\bg}}\uX_{\tilde{\bg}}^{\T}+\uI_n-\tau \ux_j \ux_j^{\T} |\nonumber\\
+  &=&  \tau^{-k} |\tau \uX_{\tilde{\bg}}\uX_{\tilde{\bg}}^{\T}+\uI_n| \{1- \tau \ux_j^{\T}
   (\tau \uX_{\tilde{\bg}}\uX_{\tilde{\bg}}^{\T}+\uI_n)^{-1}\ux_j\}\nonumber\\
-	\label{fact:2-1} &&=\tau^2 | \uX_{\tilde{\bg}}^{\T}\uX_{\tilde{\bg}}+\tau^{-1}\uI_{k+1}| (\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j).
+  &=&\tau^2 | \uX_{\tilde{\bg}}^{\T}\uX_{\tilde{\bg}}+\tau^{-1}\uI_{k+1}| (\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j).
 \end{eqnarray}
@@
 \begin{eqnarray*}
-&&m(\uy|\tilde{\bg}\setminus \{j\})  \propto \left\{\uy^{\T}\uH_{\tilde{\bg}}\uy+\frac{(
+m(\uy|\tilde{\bg}\setminus \{j\})  &\propto& \left\{\uy^{\T}\uH_{\tilde{\bg}}\uy+\frac{(
   \ux_j^{\T}\uH_{\tilde{\bg}}\uy)^2}{\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j }+b_{\sigma}\right\}^
- {-\frac{a_{\sigma}+n}{2}}\\
- &&\times (\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j)^{-1/2}
+ {-\frac{a_{\sigma}+n}{2}}\times\\
+ &&(\tau^{-1}-\ux_j^{\T}\uH_{\tilde{\bg}} \ux_j)^{-1/2}
 \end{eqnarray*}
 for any $j \in \tilde{\bg}$.
+% Non-BibTeX users please use
+\begin{thebibliography}{00}
+%
+% and use \bibitem to create references. Consult the Instructions
+% for authors for reference list style.
+%
+% \bibitem{RefJ}
+% % Format for Journal Reference
+% Author, Article title, Journal, Volume, page numbers (year)
+% % Format for books
+% \bibitem{RefB}
+% Author, Book title, page numbers. Publisher, place (year)
+\bibitem{bertsimas2016best}
+Bertsimas, D., King, A., Mazumder, R.: Best subset selection via a modern optimization lens,The Annals of Statistics,~{44(2)}, 813--852 (2016)
 
-\bibliographystyle{spbasic} 
-\bibliography{Ref_Bayes_Subset}
+\bibitem{chen2008extended}
+Chen, J., Chen, Z.: Extended Bayesian information criteria for model selection with large model spaces. Biometrika. ~{95(3)}, 759--771(2008).
+
+\bibitem{fan2001variable}
+Fan, J., Li, R. 
+Variable selection via nonconcave penalized likelihood and its oracle properties.
+Journal of the American statistical Association.~{96(456)}, 1348--1360(2001).
+
+\bibitem{findlay2018accurate}
+Findlay, G. M., Daza, R. M., Martin, B., Zhang, M. D., Leith, A. P., Gasperini, M., ... Shendure, J.: Accurate classification of BRCA1 variants with saturation genome editing
+Nature.~{562(7726)}, 217--222(2018).
+
+\bibitem{george1993variable}
+George, E. I., McCulloch, R. E.: Variable selection via Gibbs sampling. Journal of the American statistical Association,~{88(423)}, 881--889(1993).
+
+\bibitem{hans2007shotgun}
+Hans, C., Dobra, A., West, M.:Shotgun stochastic search for ``large p'' regression. 
+Journal of the American statistical Association.~{102(478)}, 507--516(2007).
+
+\bibitem{hocking1967selection}
+Hocking, R. R., Leslie, R. N.: Selection of the best subset in regression analysis. 
+Technometrics.~{9(4)}, 531--540(1967).
+
+\bibitem{kass1995}
+Kass, R. E., Raftery, A. E.:Bayes factors. Journal of the American Statistical Association.~{90(430)}, 773--795 (1995).
+
+\bibitem{kirkpatrick1983optimization}
+Kirkpatrick, S., Gelatt, C. D.,Vecchi, M. P.:Optimization by simulated annealing. 
+American Association for the Advancement of Science.~{220(4598)}, 671--680 (1983).
+
+\bibitem{liang2007stochastic}
+Liang, F., Liu, C., Carroll, R. J.:
+Stochastic approximation in Monte Carlo computation. 
+Journal of the American Statistical Association.~{102(477)}, 305--320 (2007)
+
+\bibitem{liang:2013bayesian}
+Liang, F., Song, Q., Yu, K.:Bayesian subset modeling for high-dimensional generalized linear models.Journal of the American Statistical Association.~{108(502)}, 589--606(2013).
+
+\bibitem{madigan1995bayesian}
+Madigan, D., York, J.:
+Bayesian graphical models for discrete data. 
+International Statistical Review.~{63(2)}, 215--232(1995).
+
+\bibitem{schwarz1978}
+Schwarz, G.: 
+Estimating the dimension of a model. 
+The Annals of Statistics.~{6(2)}, 461--464(1978).
+
+\bibitem{tibshirani1996regression}
+Tibshirani, R.: 
+Regression shrinkage and selection via the lasso. 
+Journal of the Royal Statistical Society. Series B (Statistical Methodology).~{58(1)}, 267--288(1996).
+
+\bibitem{zhang2010nearly}
+Zhang, C.-H.: 
+Nearly unbiased variable selection under minimax concave penalty. 
+The Annals of Statistics.~{38(2)}, 894--942(2010).
+
+\bibitem{zou2005regularization}
+Zou, H., Hastie, T.: 
+Regularization and variable selection via the elastic net. 
+Journal of the Royal Statistical Society: Series B (Statistical Methodology).~{67(2)}, 301--320(2005). 
+\end{thebibliography}
 

### 2020-02-07 Slide_Goh/Bayesian subset.tex
major revision 1

\documentclass[citecolor=blue,10pt]{beamer}
\usepackage{graphicx, color, booktabs}
\usepackage{lmodern}
\usepackage{natbib}
\usepackage{fancybox}
\usepackage{marvosym}
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage{bbding}
%\usepackage[citecolor=blue]{hyperref}
\usepackage{textpos}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=black
}

%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)

%\addtobeamertemplate{frametitle}{}{%
%\begin{textblock*}{200mm}(.8\textwidth,-0.5cm)
%\includegraphics[height=1cm,width=3cm]{ksu}
%\end{textblock*}}

\def\I{\mathbb{I}}

\def\bg{{\boldsymbol \gamma}}
\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\def\R{\mathbb{R}}
\def\T{{ \mathrm{\scriptscriptstyle T} }}
\def\v{{\varepsilon}}
\def\uSigma{{\boldsymbol \Sigma}}
\newcommand{\uone} {\mbox{\boldmath$1$}}
\newcommand{\0} {\mbox{\boldmath$0$}}
\newcommand{\uV} {{\boldsymbol V}}
\newcommand{\uv} {\mbox{\boldmath$v$}}
\newcommand{\uu} {\mbox{\boldmath$u$}}
\newcommand{\uH} {{\boldsymbol H}}
\newcommand{\uB} {{\boldsymbol B}}
\newcommand{\uD} {{\boldsymbol D}}
\newcommand{\uU} {{\boldsymbol U}}
\newcommand{\uC} {\mbox{\boldmath$C$}}
\newcommand{\uE} {\mbox{\boldmath$E$}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}} 
\newcommand{\uA}{{\boldsymbol A}}
\newcommand{\ua}{{\boldsymbol a}}
\newcommand{\uz}{{\boldsymbol z}}
\newcommand{\ub}{{\boldsymbol b}}
\newcommand{\uy}{{\boldsymbol y}}
\newcommand{\uo}{{\boldsymbol o}}
\newcommand{\uc}{{\boldsymbol c}}
\newcommand{\uY}{{\boldsymbol Y}}
\newcommand{\ux}{{\boldsymbol x}}
\newcommand{\uh}{{\boldsymbol h}}

\newcommand{\uX}{{\boldsymbol X}}
\newcommand{\uw} {\mbox{\boldmath$w$}}

\newcommand{\ug} {\mbox{\boldmath$g$}}
\newcommand{\uW} {\mbox{\boldmath$W$}}
\newcommand{\us} {\mbox{\boldmath$s$}}
\newcommand{\um} {\mbox{\boldmath$m$}}
\newcommand{\uF} {\mbox{\boldmath$F$}}
\newcommand{\uf} {\mbox{\boldmath$f$}}
\newcommand{\udelta} {\mbox{\boldmath$\delta$}}
\newcommand{\uDelta} {\mbox{\boldmath$\Delta$}}
\newcommand{\up} {{\boldsymbol p}}
\newcommand{\uP} {\mbox{\boldmath$P$}}
\newcommand{\uQ} {\mbox{\boldmath$Q$}}

\newcommand{\uK} {\mbox{\boldmath$K$}}
\newcommand{\uZ} {\mbox{\boldmath$Z$}}
\newcommand{\uI} {\mbox{\boldmath$I$}}
\newcommand{\utheta}{{\boldsymbol \theta}}

\newcommand{\uTheta} {\mbox{\boldmath $\Theta$}}
\newcommand{\umu} {{\boldsymbol \mu}}
\newcommand{\usig} {\mbox{\boldmath $\Sigma$}}
\newcommand{\ualpha} {\mbox{\boldmath $\alpha$}}
\newcommand{\ulambda}{{\boldsymbol \lambda}}
\newcommand{\ubeta}{{\boldsymbol \beta}}
\newcommand{\ueta} {\mbox{\boldmath $\eta$}}
\newcommand{\utau} {\mbox{\boldmath $\tau$}}
\newcommand{\ukappa} {\mbox{\boldmath $\kappa$}}
\newcommand{\uepsilon} {\mbox{\boldmath $\epsilon$}}
\newcommand{\uOmega} {\mbox{\boldmath $\Omega$}}
\renewcommand{\bibsection}{\vskip 5mm\centering{REFERENCES}}
\newcommand{\red}{\textcolor{red}}
\newcommand{\card}{{\rm card}}
\newcommand{\rank}{{\rm rank}}
\def\Sup{\operatornamewithlimits{sup\vphantom{p}}}
\def\mis{{\rm mis}}
\def\obs{{\rm obs}}
\def\full{{\rm full}}
\newcommand{\Nor}{\mathcal{N}}
\newcommand{\To}{\rightarrow}
\newcommand{\Car}{\mathds{1}}
\newcommand{\Inte}{\mathds{N}}
\newcommand{\LL}{\mathds{L}}
\newcommand{\Real}{\mathds{R}}
\newcommand{\Inter}{\mathds{Z}}
\newcommand{\Esp}{\mathds{E}}
\newcommand{\Var}{\mbox{Var}}
\newcommand{\Cov}{\mbox{Cov}}
\newcommand{\Probability}{\mathbb{P}}
\newcommand{\Loi}{\mathcal{L}}
\newcommand{\Dist}{\mathcal{D}}
%\newcommand{\bfS}{\mathbf{S}}
\newcommand{\bgamma}{\mbox{\boldmath $\gamma$}}
\newcommand{\bGamma}{\mbox{\boldmath $\Gamma$}}
\newcommand{\dint}{\displaystyle\int}
%\renewcommand{\thesection}{\arabic{section}}
%\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
%\renewcommand{\thetheorem}{\arabic{section}.\arabic{theorem}}
%\renewcommand{\theassumption}{\arabic{section}.\arabic{assumption}}
%\renewcommand{\theproposition}{\arabic{section}.\arabic{proposition}}
%\renewcommand{\thecorollary}{\arabic{section}.\arabic{corollary}}
%\renewcommand{\thelemma}{\arabic{section}.\arabic{lemma}}
%\renewcommand{\theexample}{\arabic{section}.\arabic{example}}
%\renewcommand{\theremark}{\arabic{section}.\arabic{remark}}
%\renewcommand{\thealgorithm}{\arabic{section}.\arabic{algorithm}}

\usepackage{framed}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{definition1}{What is BIG DATA?}
\newtheorem{remark1}{Big Data Challenge I}
\newtheorem{remark7}{Big Data Challenge II}
\newtheorem{remark2}{Bayesian perspective}
\newtheorem{remark3}{Data}
\newtheorem{remark4}{\textcolor{red}{Generalized} Bregman divergence clustering}
\newtheorem{remark5}{Bayesian clustering with high-dimensional covariates}
\newtheorem{remark6}{Bayesian functional clustering with high-dimensional covariates}
\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}

\usepackage{alltt}
\mode<presentation>
\setbeamercovered{dynamic}
\usetheme{Boadilla}

\begin{document}
\title{Bayesian Approaches for High-Dimensional
Data Analysis}
\author{\bf Gyuhyeong Goh}

\institute{Department of Statistics\\
Kansas State University, Manhattan, KS\\
\quad\\
\quad\\
{\color{blue} Joint work with} \\
\quad\\
{ Shiqiang Jin}\\ \quad\\ Kansas State University, Manhattan, KS
}

\date{}

\begin{frame}
\titlepage
\end{frame}

%\begin{frame}<beamer>
%\frametitle{Outline}
%\tableofcontents
%\end{frame}

\section{Introduction}

\begin{frame}{Introduction}{Data structure}
\begin{itemize}
\item In practice, we frequently observe the following data structure: 
\end{itemize}

\begin{eqnarray*}
\begin{array}{c|c|c|c|c}
Y&X_1&X_2&\cdots &X_p\\
\hline
y_1& x_{11} & x_{12}&\cdots & x_{1p}  \\
y_2& x_{21} & x_{22}&\cdots & x_{2p} \\
\vdots& \vdots & \vdots&\ddots & \vdots \\
y_n& x_{n1} & x_{n2}&\cdots & x_{np} \\
\end{array}
\end{eqnarray*}
\begin{itemize}
\item[]\quad where $Y$ is the response and $X_1,X_2,\ldots, X_p$ are the predictors.
\item We are interested in modeling the relationship between $X_1,\ldots, X_p$ and $Y$.  
\end{itemize}
\end{frame}

\begin{frame}{Introduction}{Statistical models}
\begin{itemize}
\item Regression models play an important role in many application domains for analyzing or predicting a response based on multiple predictors.
\vspace{5mm}

\begin{itemize}
\item Linear regression:
$$Y=\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p +\epsilon$$
\item Logistic regression:
$$P(Y=1)=\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)} $$
\item Cox regression:
$$h(Y)= h_0(Y)\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)$$
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Introduction}{Variable selection}
\begin{itemize}
\item \emph{Variable selection} is the process of selecting a subset of relevant predictors in regression analysis. (e.g., BIC, AIC, CV, $R^2_a$, $C_p$, ...)
\end{itemize}
\begin{figure}
\includegraphics[width=0.8\textwidth]{Figure1.pdf}
\end{figure}
\end{frame}

\begin{frame}{Introduction}{Challenges of high-dimensional variable selection}
\begin{itemize}\itemsep=3mm
\item There are $2^p$ candidate models\\
\item[] e.g., for $p=3$
{\footnotesize
\begin{eqnarray*}
\texttt{Model 1}:\quad Y&=&\beta_0+\epsilon\\
\texttt{Model 2}:\quad Y&=&\beta_0+\beta_1X_1+\epsilon\\
\texttt{Model 3}:\quad Y&=&\beta_0+\beta_2X_2+\epsilon\\
\texttt{Model 4}:\quad Y&=&\beta_0+\beta_3X_3+\epsilon\\
\texttt{Model 5}:\quad Y&=&\beta_0+\beta_1X_1+\beta_2X_2+\epsilon\\
\texttt{Model 6}:\quad Y&=&\beta_0+\beta_1X_1+\beta_3X_3+\epsilon\\
\texttt{Model 7}:\quad Y&=&\beta_0+\beta_2X_2+\beta_3X_3+\epsilon\\
\texttt{Model 8}:\quad Y&=&\beta_0+\beta_1X_1+\beta_2X_2+\beta_3X_3+\epsilon
\end{eqnarray*}}\pause
\item When \textcolor{red}{$p$ is large}, it is \textcolor{red}{challenging to find the best subset}.
\item[]  e.g., $2^{40}\approx 1,000,000,000,000$.
\end{itemize}
\end{frame}

\begin{frame}{Introduction}{Connection between sparse estimation and variable selection}
\begin{itemize}
\item Variable selection is equivalent to estimating sparse coefficients.
\begin{itemize}
\item Linear regression:
{\footnotesize
\begin{eqnarray*}
Y&=&\beta_0+\beta_1 X_1+\beta_2 X_2 +\epsilon\\
&\Updownarrow&\\
 Y&=&\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p +\epsilon
\end{eqnarray*}}
\item Logistic regression:
{\footnotesize
\begin{eqnarray*}
P(Y=1)&=&\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2)} \\
&\Updownarrow&\\
P(Y=1)&=&\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p)} 
\end{eqnarray*}}

\end{itemize}
\item Hence, variable selection can be done by producing \textcolor{red}{sparse} estimator of coefficients.
\end{itemize}

\end{frame}
\begin{frame}{High-dimensional linear regression models}
\begin{itemize}\itemsep=5mm
\item Define
\begin{eqnarray*}
\left[\begin{array}{c|cccc}
y_1& x_{11} & x_{12}&\cdots & x_{1p}  \\
y_2& x_{21} & x_{22}&\cdots & x_{2p} \\
\vdots& \vdots & \vdots&\ddots & \vdots \\
y_n& x_{n1} & x_{n2}&\cdots & x_{np} \\
\end{array}\right]=\left[\begin{array}{c|cccc}
\uy& \ux_{1} & \ux_{2}&\cdots & \ux_{p}  \\
\end{array}\right]
\end{eqnarray*}
\item Consider 
$$ \uy=\uX\ubeta +\uepsilon,$$
where $\uX=(\ux_1,\ldots,\ux_p)$, $\ubeta=(\beta_1,\ldots, \beta_p)^\T$, and $\uepsilon \sim N(0,\sigma^2 I_n)$.
 \item Assume that $p>n$.
 \item Our aim is to obtain a sparse estimator for $\ubeta$.
\end{itemize}
\end{frame}

\begin{frame}{Sparse estimation with $L_0$-penalty}
\begin{itemize}\itemsep=6mm

 \item The sparse  estimator can be obtained by minimizing 
 $$ \|\uy-\uX\ubeta\|^2 +\lambda \|\ubeta\|_0,$$
 where $\|\ubeta\|_0=\sum_{j=1}^p \mathbb{I}(\beta_j\neq 0)$ and $\lambda \geq 0$ controls degrees of sparsity.
 \item e.g., $\lambda=2$ (AIC), $\lambda=\log n$ (BIC), $\lambda =\log p $ (RIC), \ldots
 \pause \item However, the use of $L_0$-penalty leads to a \textcolor{red}{non-convex optimization} problem, which is computationally intractable in high-dimensional settings.
\end{itemize}
\end{frame}

\begin{frame}{Sparse estimation with convex penalties}
\begin{itemize}\itemsep=5mm
\item Many convex penalty functions have been proposed. 
\\e.g., lasso, adaptive lasso, elastic net, MCP, ... 
\item The lasso estimator \citep{tibshirani1996regression} can be obtained by minimizing 
 $$ \|\uy-\uX\ubeta\|^2 +\lambda \|\ubeta\|_1,$$
 where $\|\ubeta\|_1=\sum_{j=1}^p |\beta_j|$.
\pause \item However, optimal $\lambda$ selection is required. (CV, GCV, BIC, ...)

 \item In addition, convex penalties generate the shrinkage bias on the resulting estimator of $\ubeta$. 
\end{itemize}
\end{frame}
\begin{frame}{$L_0$-penalty vs Convex penalties} 
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 &$L_0$-penalty & Convex penalties \\ 
  \hline
Computation & \textcolor{red}{hard} &easy \\
Bias & unbiased & \textcolor{red}{biased} \\
$\lambda$ selection & easy & \textcolor{red}{hard} \\
$var(\hat{\beta})$& available& \textcolor{red}{mostly n/a} \\
   \hline
\end{tabular}
\end{table}
\vspace{5mm}
\begin{itemize}
 \item We propose a Bayesian method to overcome challenges in non-convex optimization.
\end{itemize}
\end{frame}

\begin{frame}{Reduced models}
\begin{itemize}\itemsep=5mm
\item Let $\bg$ be an index set, $\bg \subset \{1,\ldots,p\}$.
\item Let $\uX_{\bg}$ be a sub-matrix of $\uX$ containing $\ux_j$ $j\in \bg$.\\
e.g. $\bg=\{1,2,3\} \Rightarrow \uX_{\bg}=(\ux_1,\ux_2,\ux_3)$.
\item Given $\bg$, our model reduces to
\begin{eqnarray*}
 \uy = \uX_{\bg} \ubeta_{\bg} + \uepsilon,
\end{eqnarray*}
where $\ubeta_{\bg}$ is a sub-vector of $\ubeta$ corresponding to $\bg$. 
\end{itemize}
\end{frame}

\begin{frame}{Bayesian best subset selection}
\begin{itemize}\itemsep=3mm
\item Suppose that we are interested in finding a best subset of size $k$.
\item In a Bayesian framework, best subset selection can be done by estimating $\bg$.
\item The Bayesian estimator of $\bg $ is obtained by maximizing
$$\pi(\bg | \uy) \propto \int f(\uy |\ubeta_\bg ,\bg,\sigma^2)\pi(\ubeta_\bg ,\bg,\sigma^2) d (\ubeta_\bg, \sigma^2) , $$
 where $f(\uy |\ubeta_\bg ,\bg,\sigma^2)$ is the likelihood and $\pi(\ubeta_\bg ,\bg,\sigma^2)$ is the prior.
\end{itemize}
\end{frame}

\begin{frame}{Prior specification \& posterior distribution}
\begin{itemize}\itemsep=3mm
\item For computational convenience, we consider
\begin{eqnarray*}
 \ubeta_{\bg}|\sigma^2,\bg &\sim&\text{Normal}(0,\tau \sigma^2 \uI_{|\bg|} ),\\
 \sigma^2 &\sim& \text{Inverse-Gamma}(a_{\sigma}/2,b_{\sigma}/2),\\
 \pi(\bg)&\propto&\mathbb{I}(|\bg|=k ),
\end{eqnarray*}
where $|\bg|$ denotes the number of elements in $\bg$.
\item Given $k$, it can be shown that 
$$\pi(\bg|\uy)\propto  \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
 \uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
 \uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } } \mathbb{I}(|\bg|=k ),$$
 where $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$.
\end{itemize}
\end{frame}

\begin{frame}{Stochastic search via MCMC}
\begin{itemize}\itemsep=3mm
\item A simplest way is to generate a random sample from $\pi(\bg|\uy)$:\\
$$\bg^{(1)},\bg^{(2)},\ldots,\bg^{(T)} \overset{iid}{\sim} \pi(\bg|\uy) \quad \Rightarrow \quad  \hat{\bg}=\arg \max_{1\leq t\leq T}\pi(\bg^{(t)}|\uy),$$
 but this is impossible due to the complexity of $\pi(\bg|\uy)$.
\item As an alternative, we can generate a Markov chain using Markov chain Monte Carlo (MCMC) computation.
\item However, MCMC algorithms are too slow and often fail when $p$ is large.
\end{itemize}
\end{frame}

\begin{frame}{Shotgun Stochastic Search (SSS)}
\begin{itemize}\itemsep=3mm
\item \citet{hans2007shotgun} propose SSS using the idea of parallel computation.
\item Let $\bg^{(t)}$ be a current state of $\bg$ and $\hat{\bg}$ be a current best subset.
\item Define a neighborhood of $\bg^{(t)}$ as
$$\mathcal{N}(\bg^{(t)})=\{ \bg^{(t)} \}\cup \{\bg^{(t)} \cup \{j\}: j\notin \bg^{(t)}\}\cup \{\bg^{(t)} \setminus \{j'\}: j'\in \bg^{(t)}\}.$$
\end{itemize}
\end{frame}

\begin{frame}{SSS algorithm}
\begin{itemize}\itemsep=3mm
\item Update $\hat{\bg}$ by iterating the following steps:
\item[] \textcolor{blue}{Step1.} Compute $\pi(\bg|\uy)$ for each $\bg \in \mathcal{N}(\bg^{(t)})$ \textcolor{red}{in parallel} (parallel computing).
\item[] \textcolor{blue}{Step2.} If $\pi(\hat{\bg}|\uy)< \max_{\bg \in \mathcal{N}(\bg^{(t)}) }\pi(\bg|\uy)$, then update $$\hat{\bg}= \arg\max_{\bg \in \mathcal{N}(\bg^{(t)}) }\pi(\bg|\uy)$$
\item[] \textcolor{blue}{Step3.} Update $\bg^{(t+1)}$ by generating a sample from $ \mathcal{N}(\bg^{(t)})$ with probabilities proportional to $\pi(\bg|\uy)  \mathbb{I}\{\bg \in \mathcal{N}(\bg^{(t)})\}$.
\end{itemize}
\end{frame}

\begin{frame}{Limitations of SSS}
\begin{itemize}\itemsep=3mm
\item When $k$ is fixed, SSS is not applicable.
\item When parallel computing is not available, SSS is inefficient.
\item Stochastic search algorithm requires a ``burn-in'' period.
\end{itemize}
\end{frame}

\begin{frame}{Hybrid best subset search with a fixed $k$}
\begin{itemize}
  \item[1.] Initialize $\hat{\bg}$ s.t. $|\hat{\bg}|=k$.
  \item[2.] \textbf{Repeat} \quad  \texttt{\textcolor{blue}{\#deterministic search}}
        \begin{itemize}\itemsep=2mm
         \item[] Update $\tilde{\bg }\leftarrow \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg} ) } \pi(\bg|\uy)$ ;\quad  \texttt{\textcolor{blue}{\# $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{j\}: j\notin \hat{\bg} \}$}}
         \item[] Update $\hat{\bg}\leftarrow  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg} ) } \pi(\bg|\uy);$ \quad \texttt{\textcolor{blue}{\# $\mathcal{N}_-(\tilde{\bg })= \{\tilde{\bg } \setminus \{j\}: j\in \tilde{\bg } \}$}}
        \end{itemize}
  \item[] \textbf{until} convergence.
 \pause \item[3.] Set $\bg^{(0)}=\hat{\bg}$.
  \item[4.] \textbf{Repeat} for $t=1,\ldots,T$:  \quad  \texttt{\textcolor{blue}{\#stochastic search}}
        \begin{itemize}\itemsep=2mm
         \item[] Generate $\bg^* \sim\pi_\alpha (\bg |\uy)\propto  \{\pi(\bg |\uy)\}^\alpha \mathbb{I}\{\bg\in \mathcal{N}_+({\bg^{(t-1)}} ) \}$;  \quad  \texttt{\textcolor{blue}{\# $\alpha \in [0,1]$}}
         \item[] Generate $\bg^{(t)}\sim \pi_\alpha (\bg |\uy)\propto \{\pi(\bg |\uy)\}^\alpha \mathbb{I}\{\bg\in \mathcal{N}_-({\bg^{*}} ) \}$;
         \item[] \textbf{If} $\pi(\hat{\bg} |\uy)<\pi({\bg}^{(t)} |\uy)$, \textbf{then} update $\hat{\bg}=\bg^{(t)}$, break the loop, and go to 2.
        \end{itemize}
  \item[5.] Return $\hat{\bg}$.
 \end{itemize}
\end{frame}

\begin{frame}{Key features of proposed algorithm}
\begin{itemize}\itemsep=5mm
\item In Steps 2, computing $\pi(\bg|\uy)$ for all $\bg  \in \mathcal{N}_+(\hat{\bg} )$ (or all $\bg  \in \mathcal{N}_-(\tilde{\bg} ) )$ can be done \textcolor{red}{simultaneously} in a single computation.
\item In Step 4, the idea of escort distribution (used in statistical physics and thermodynamics) is introduced to stimulate the movement of Markov chain.
\item An escort distribution of $p(x)$ is given as 
$$ p_\alpha(x)=\frac{\{p(x)\}^\alpha}{\sum_{x \in \mathcal{X} } \{p(x)\}^\alpha}.$$

\end{itemize}
\end{frame}
\begin{frame}{Escort distributions}
Let $$p(x)=\begin{cases} 0.1\quad &x=1 \\ 0.85~\quad &x=2 \\0.05~\quad &x=3 \end{cases}.$$
\begin{figure}
\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig1.pdf}
\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig2.pdf}
\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig3.pdf}
\caption{Escort distributions of $p(x)$.}
\end{figure}
\end{frame}
\begin{frame}{Best subset selection with unknown $k$}
\begin{itemize}\itemsep=3mm
\item We extend the proposed method to best subset selection with varying $k (<K)$, where $K$ is a pre-specified upper bound, $K<n$.
\item In our Bayesian framework, this extension can be easily done by assigning a prior for $k$.
\item Note that the uniform prior, $k \sim \text{Uniform}\{1,\ldots,K\}$, tends to assign larger probability to a larger subset. 
\item We define
$$\pi(k)\propto 1/\binom{p}{k} \mathbb{I}(k\leq K).$$
\end{itemize}
\end{frame}

\begin{frame}{Hybrid best subset search with varying $k$}
\begin{itemize}\itemsep=3mm
\item Bayesian best subset selection can be done by maximizing
$$ \pi(\bg,k|\uy) \propto f(\uy|\bg, k)\pi(\bg| k) \pi(k)$$
over $(\bg,k)$.
\item Our algorithm proceeds as follows:\\

 \begin{itemize}\itemsep=3mm
  \item[1.] \textbf{Repeat} for $k=1,\ldots,K$:
        \begin{itemize}
         \item[a.] Given $k$, implement the hybrid search algorithm.
         \item[b.] Set $\hat{\bg}_k=\hat{\bg}$.
        \end{itemize}
  \item[2.] Find $\hat{\bg}_{k_*}$ such that $$ \log f(\uy|\hat{\bg}_{k_*},{k_*})-\log \binom{p}{{k_*}} \geq \log f(\uy|\hat{\bg}_k,k)-\log \binom{p}{k},\quad \text{any $k\leq K$}.$$
 \end{itemize}

\end{itemize}
\end{frame}

\begin{frame}{Connection to extended BIC}

\begin{itemize}\itemsep=3mm
\item It can be shown that our posterior criterion is asymptotically equivalent to the extended BIC (EBIC) of \citet{chen2008extended}.
\item EBIC corresponds to the $L_0$-penalty sparse estimation with 
$$\lambda = \log (n)+ \frac{2}{k}\log \binom{p}{k}.$$
\end{itemize}
\end{frame}

\begin{frame}{Model selection consistency}

\begin{itemize}\itemsep=3mm
\item The proposed Bayesian approach possesses the model selection consistency in the high-dimensional setting with $p=p_n=O(n^\xi)$ for $\xi\geq 1$.
\item Hence, as $n\to \infty$, our variable selection procedure identifies the true model with probability tending to one.
\end{itemize}
\end{frame}

\begin{frame}{Simulation study}{Setup}
\begin{itemize}\itemsep=3mm
\item For given $n=100$, we generate the data from 
$$y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},1\right),$$
where 
\begin{itemize}\itemsep=3mm
\item $(x_{i1},\ldots,x_{ip})^\T \overset{iid}{\sim}\text{Normal}(\0_p,\uSigma)$ with $\uSigma=(\Sigma_{ij})_{p\times p}$ and $\Sigma_{ij}=\rho^{|i-j|}$,
\item $\beta_j \overset{iid}{\sim} \text{Uniform}\{-1,-2,1,2\}$ if $j\in \bg$ and $\beta_j=0$ if $j\notin \bg$. 
\item $\bg$ is an index set of size $4$ randomly selected from $\{1,2,\ldots,p\}$.
\item We consider four scenarios for $p$ and $\rho$: \\
(i) $p=200$, $\rho=0.1$, (ii) $p=200$, $\rho=0.9$,\\
 (iii) $p=1000$, $\rho=0.1$, (iv) $p=1000$, $\rho=0.9$. 
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Simulation study}{Results (high-dimensional scenarios)}
{\footnotesize
\begin{table}[H]
 \centering 
 \caption{MC size=$2,000$; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance).}\label{T:sim1}
 \begin{tabular}{cc|c|c|c|c}
  \hline
  Scenario & Method                         & FDR  (s.e.)    & TRUE\% (s.e.)   & SIZE (s.e.)     & HAM (s.e.)    \\
  \hline
i           & Proposed & 0.006 (0.001)  & 96.900 (0.388)  & 4.032 (0.004)    & 0.032 (0.004) \\
           & SCAD                           & 0.034 (0.002)  & 85.200 (0.794)  & 4.188 (0.011)   & 0.188 (0.011) \\
           & MCP                            & 0.035 (0.002)  & 84.750 (0.804)  & 4.191 (0.011)   & 0.191 (0.011) \\
           & ENET                           & 0.016 (0.001)  & 92.700 (0.582)  & 4.087 (0.007)   & 0.087 (0.007) \\
           & LASSO                          & 0.020 (0.002)  & 91.350 (0.629)  & 4.109 (0.009)   & 0.109 (0.009) \\
  \hline
ii           & Proposed & 0.023  (0.002) & 88.750  (0.707) & 3.985 (0.006)  & 0.203 (0.014) \\
           & SCAD                           & 0.059 (0.003)  & 74.150 (0.979)  & 4.107 (0.015)   & 0.480 (0.022) \\
           & MCP                            & 0.137 (0.004)  & 55.400 (1.112)  & 4.264 (0.020)   & 1.098 (0.034) \\
           & ENET                           & 0.501 (0.004)  & 0.300 (0.122)   & 7.716 (0.072)   & 5.018 (0.052) \\
           & LASSO                          & 0.276 (0.004)  & 15.550 (0.811)  & 5.308 (0.033)   & 2.038 (0.034) \\
  \hline
 \end{tabular}
\end{table}}
\end{frame}

\begin{frame}{Simulation study}{Results (ultra high-dimensional scenarios)}
{\footnotesize
\begin{table}[H]
 \centering 
 \caption{MC size=$2,000$; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance).}\label{T:sim2}
 \begin{tabular}{cc|c|c|c|c}
  \hline
  Scenario & Method                         & FDR  (s.e.)    & TRUE\% (s.e.)   & SIZE (s.e.)     & HAM (s.e.)    \\
  \hline
   iii        & Proposed & 0.004 (0.001)   & 98.100 (0.305)  & 4.020 (0.003)    & 0.020 (0.003) \\
           & SCAD                           & 0.027 (0.002)  & 87.900 (0.729)  & 4.145 (0.010)   & 0.145 (0.010) \\
           & MCP                            & 0.031 (0.002)  & 86.550 (0.763)  & 4.172 (0.013)   & 0.172 (0.013) \\
           & ENET                           & 0.035 (0.002)  & 84.850 (0.802)  & 4.181 (0.013)   & 0.206 (0.012) \\
           & LASSO                          & 0.014 (0.001)  & 93.850 (0.537)  & 4.073 (0.007)   & 0.073 (0.007) \\
  \hline
    iv       & Proposed & 0.023(0.002)   & 89.850 (0.675)  & 4.005 (0.005) & 0.190 (0.013) \\
           & SCAD                           & 0.068 (0.003)  & 74.250 (0.978)  & 4.196 (0.014)   & 0.493 (0.023) \\
           & MCP                            & 0.152 (0.004)  & 53.750 (1.115)  & 4.226 (0.017)   & 1.202 (0.035) \\
           & ENET                           & 0.417 (0.005)  & 0.150 (0.087)   & 6.228 (0.068)   & 4.089 (0.043) \\
           & LASSO                          & 0.265 (0.004)  & 19.500 (0.886)  & 5.139 (0.029)   & 1.909 (0.035) \\
  \hline
 \end{tabular}
\end{table}}
\end{frame}

\begin{frame}{Real data application}{Data description}
\begin{itemize}\itemsep=4mm
\item We apply the proposed method to Breast Invasive Carcinoma (BRCA) data generated by The Cancer Genome Atlas (TCGA) Research Network \url{http://cancergenome.nih.gov}. 
\item The data set is available at the \texttt{R} package \texttt{curatedTCGAData}. 
\item The data set contains $17,814$ gene expression measurements (recorded on the log scale) of $526$ patients with primary solid tumor. 
\item BRCA1 is a tumor suppressor gene and its mutations predispose women to breast cancer \citep{findlay2018accurate}. 
\item Our goal here is to identify the best fitting model for estimating an association between BRCA1 (response variable) and the other genes (independent variables).

\end{itemize}
\end{frame}

\begin{frame}{Real data application}{Results (based on $4,000$ genes)}
\begin{table}[ht]
 \centering
 \caption{Model comparison}\label{T:realdata}
 \begin{tabular}{rrrrr}
  \hline
           & \# of selected  & PMSE & BIC     & EBIC    \\
  \hline
  Proposed & 8 & 0.60      & 984.45  & 1099.50 \\
  SCAD     & 4 & 0.68      & 1104.69 & 1166.47 \\
  MCP      & 4 & 0.68      & 1104.69 & 1166.47 \\
  ENET     & 5 & 0.68      & 1110.65 & 1186.25 \\
  LASSO    & 4 & 0.68      & 1104.69 & 1166.47 \\
  \hline
 \end{tabular}
\end{table}
\end{frame}
\begin{frame}{Real data application}{Results (cont.)}
\begin{figure}
 \centering
 \includegraphics[width=0.6\textwidth,height=0.55\textwidth]{Heatmap.pdf}
 \caption{Except C10orf76, 7 genes are documented as \emph{diseases-related genes} }
\end{figure}

\end{frame}

\begin{frame}{Concluding remarks}
\begin{itemize}\itemsep=4mm
\item Parallel computing is applicable to our algorithm with varying $k$. 
\item The proposed method can be extended to multivariate linear regression models, binary regression models, and multivariate mixed responses models (in progress).
\end{itemize}

\end{frame}

\begin{frame}\footnotesize
%\bibliographystyle{biom}
%\bibliography{thesis_Goh}
\begin{thebibliography}{}
%\bibitem[\protect\citeauthoryear{Berg et al.}{Berg et al.}{2016}]{Berg:2016}
%Berg, E., Kim, J. K. and Skinner, C. (2016).
%\newblock Imputation under informative sampling
%\newblock {\em Journal of Survey Statistics and Methodology} {\bf }
%(In Press).

%\bibitem[\protect\citeauthoryear{Yin}{Yin}{2009}]{Yin:2009}
%Yin, G. (2009).
%\newblock Bayesian Generalized Method of Moments
%\newblock {\em Bayesian Analysis} {\bf 4,}
% 191--208.

%\bibitem[\protect\citeauthoryear{Xu, Chen and Mantel}{Xu, Chen and Mantel}{2013}]{Xu:2013}
%Xu, C., Chen, J., and Mantel, H. (2013).
%\newblock Pseudo-likelihood-based Bayesian information criterion for variable selection in survey data
%\newblock {\em Survey Methodology} {\bf 39,}
% 303--321.

%\bibitem[\protect\citeauthoryear{Li and Jiang}{Li and Jiang}{2014}]{Lin-Jiang:2014}
%Li, C. and Jiang, W. (2014).
%\newblock Model Selection for Likelihood-free Bayesian Methods Based on Moment Conditions: Theory and Numerical Examples
%\newblock {\em arXiv e-prints}.

%\bibitem[\protect\citeauthoryear{Schwarz}{Schwarz}{1978}]{Schwarz:1978}
%Schwarz, G. (1978).
%\newblock Estimating the dimension of a model.
%\newblock {\em The Annals of Statistics} {\bf 6,} 461--464.

\bibitem[\protect\citeauthoryear{Tibshirani}{Tibshirani}{1996}]{tibshirani1996regression}
Tibshirani, R. (1996).
\newblock Regression shrinkage and selection via the lasso.
\newblock {\em Journal of the Royal Statistical Society. Series B
  (Methodological)\/}, 267--288.

\bibitem[\protect\citeauthoryear{Hans, Dobra, and West}{Hans
  et~al.}{2007}]{hans2007shotgun}
Hans, C., A.~Dobra, and M.~West (2007).
\newblock Shotgun stochastic search for ``large p'' regression.
\newblock {\em Journal of the American Statistical Association\/}~{\em
  102\/}(478), 507--516.

\bibitem[\protect\citeauthoryear{Chen and Chen}{Chen and
  Chen}{2008}]{chen2008extended}
Chen, J. and Z.~Chen (2008).
\newblock Extended bayesian information criteria for model selection with large
  model spaces.
\newblock {\em Biometrika\/}~{\em 95\/}(3), 759--771.

\bibitem[\protect\citeauthoryear{Findlay, Daza, Martin, Zhang, Leith,
  Gasperini, Janizek, Huang, Starita, and Shendure}{Findlay
  et~al.}{2018}]{findlay2018accurate}
Findlay, G.~M., R.~M. Daza, B.~Martin, M.~D. Zhang, A.~P. Leith, M.~Gasperini,
  J.~D. Janizek, X.~Huang, L.~M. Starita, and J.~Shendure (2018).
\newblock Accurate classification of brca1 variants with saturation genome
  editing.
\newblock {\em Nature\/}~{\em 562\/}(7726), 217.

\end{thebibliography}
\end{frame}
%\bibliography{thesis_Goh}

\begin{frame}{Q/A}\vspace{2mm}
\centering \huge THANK YOU
\end{frame}

\end{document}

### 2020-02-07 Slide_JSM2019/Jin_JSM2019.tex
major revision 1

--- 2020-02-07 Slide_Goh/Bayesian subset.tex
@@
 \usepackage{graphicx, color, booktabs}
+\usepackage{ulem}
+\usepackage{cancel}
 \usepackage{lmodern}
@@
 \newcommand{\0} {\mbox{\boldmath$0$}}
+\def\1{{\boldsymbol 1}}
+\def\diag{{\rm diag}}
 \newcommand{\uV} {{\boldsymbol V}}
@@
 \begin{document}
-\title{Bayesian Approaches for High-Dimensional
-Data Analysis}
-\author{\bf Gyuhyeong Goh}
+
+\title{Bayesian selection of best subsets in high-dimensional regression}
+\author{\bf Shiqiang Jin}
 
@@
 \quad\\
-{ Shiqiang Jin}\\ \quad\\ Kansas State University, Manhattan, KS
+{\bf Gyuhyeong Goh}\\ \quad\\ Kansas State University, Manhattan, KS
 }
 
-\date{}
+\date{July 31, 2019}
 
@@
 
-\section{Introduction}
-
-\begin{frame}{Introduction}{Data structure}
-\begin{itemize}
-\item In practice, we frequently observe the following data structure: 
-\end{itemize}
-
-\begin{eqnarray*}
-\begin{array}{c|c|c|c|c}
-Y&X_1&X_2&\cdots &X_p\\
-\hline
-y_1& x_{11} & x_{12}&\cdots & x_{1p}  \\
-y_2& x_{21} & x_{22}&\cdots & x_{2p} \\
-\vdots& \vdots & \vdots&\ddots & \vdots \\
-y_n& x_{n1} & x_{n2}&\cdots & x_{np} \\
-\end{array}
-\end{eqnarray*}
-\begin{itemize}
-\item[]\quad where $Y$ is the response and $X_1,X_2,\ldots, X_p$ are the predictors.
-\item We are interested in modeling the relationship between $X_1,\ldots, X_p$ and $Y$.  
+\section{Bayesian linear regression model in High-dimensional Data}
+\begin{frame}{Bayesian linear regression model in High-dimensional Data}
+\begin{itemize}\itemsep=5mm
+\item Consider a linear regression model
+\begin{eqnarray} \label{eq:1}
+\uy=\uX\ubeta +\uepsilon,
+\end{eqnarray}
+where $\uy=(y_1,\ldots,y_n)^{\T}$ is a response vector, $\uX=(\ux_1,\ldots,\ux_p)\in\mathbb{R}^{n\times p}$ is a model matrix, $\ubeta=(\beta_1,\ldots, \beta_p)^\T$ is a coefficient vector and $\uepsilon \sim N(0,\sigma^2 I_n)$.
+ \item We assume {\color{red}{$p>n$}}, i.e. High-dimensional data. 
+ \item We assume only a few number of predictors are associated with the response, i.e. $\ubeta$ is {\color{red}{sparse}}.
  \end{itemize}
@@
 
-\begin{frame}{Introduction}{Statistical models}
-\begin{itemize}
-\item Regression models play an important role in many application domains for analyzing or predicting a response based on multiple predictors.
-\vspace{5mm}
-
-\begin{itemize}
-\item Linear regression:
-$$Y=\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p +\epsilon$$
-\item Logistic regression:
-$$P(Y=1)=\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)} $$
-\item Cox regression:
-$$h(Y)= h_0(Y)\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)$$
-\end{itemize}
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Introduction}{Variable selection}
-\begin{itemize}
-\item \emph{Variable selection} is the process of selecting a subset of relevant predictors in regression analysis. (e.g., BIC, AIC, CV, $R^2_a$, $C_p$, ...)
-\end{itemize}
-\begin{figure}
-\includegraphics[width=0.8\textwidth]{Figure1.pdf}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Introduction}{Challenges of high-dimensional variable selection}
-\begin{itemize}\itemsep=3mm
-\item There are $2^p$ candidate models\\
-\item[] e.g., for $p=3$
-{\footnotesize
-\begin{eqnarray*}
-\texttt{Model 1}:\quad Y&=&\beta_0+\epsilon\\
-\texttt{Model 2}:\quad Y&=&\beta_0+\beta_1X_1+\epsilon\\
-\texttt{Model 3}:\quad Y&=&\beta_0+\beta_2X_2+\epsilon\\
-\texttt{Model 4}:\quad Y&=&\beta_0+\beta_3X_3+\epsilon\\
-\texttt{Model 5}:\quad Y&=&\beta_0+\beta_1X_1+\beta_2X_2+\epsilon\\
-\texttt{Model 6}:\quad Y&=&\beta_0+\beta_1X_1+\beta_3X_3+\epsilon\\
-\texttt{Model 7}:\quad Y&=&\beta_0+\beta_2X_2+\beta_3X_3+\epsilon\\
-\texttt{Model 8}:\quad Y&=&\beta_0+\beta_1X_1+\beta_2X_2+\beta_3X_3+\epsilon
-\end{eqnarray*}}\pause
-\item When \textcolor{red}{$p$ is large}, it is \textcolor{red}{challenging to find the best subset}.
-\item[]  e.g., $2^{40}\approx 1,000,000,000,000$.
+ \begin{frame}{Bayesian linear regression model in High-dimensional Data}
+\begin{itemize}\itemsep=5mm
+\item To better explain the {\color{red}{sparsity}} of $\ubeta$, we introduce a latent index set $\bg \subset \{1,\ldots,p\}$ so that $\uX_{\bg}$ represents a sub-matrix of $\uX$ containing $\ux_j$, $j\in\bg$.
+ \item e.g. $\bg=\{1,3,4\} \Rightarrow \uX_{\bg}=(\ux_1,\ux_3,\ux_4)$.
+\item The full model in (\ref{eq:1}) can be reduced to
+\begin{eqnarray}\label{eq:2}
+\uy=\uX_{\bg}\ubeta_{\bg} +\uepsilon.
+\end{eqnarray}
 \end{itemize}
@@
 
-\begin{frame}{Introduction}{Connection between sparse estimation and variable selection}
-\begin{itemize}
-\item Variable selection is equivalent to estimating sparse coefficients.
-\begin{itemize}
-\item Linear regression:
-{\footnotesize
+\begin{frame}{Priors and marginal posterior distribution}
+
+\begin{itemize}\itemsep=5mm
+\item Our {\color{blue}{Research Goals}} are to obtain: 
+\item [(i)] $k$ most important predictors out of $\binom{p}{k}$ candidate models; 
+\item [(ii)] a single best model from among $2^p$ candidate models.
+\pause
+\item We consider 
 \begin{eqnarray*}
-Y&=&\beta_0+\beta_1 X_1+\beta_2 X_2 +\epsilon\\
-&\Updownarrow&\\
- Y&=&\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p +\epsilon
-\end{eqnarray*}}
-\item Logistic regression:
-{\footnotesize
-\begin{eqnarray*}
-P(Y=1)&=&\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2)} \\
-&\Updownarrow&\\
-P(Y=1)&=&\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p)}
-\end{eqnarray*}}
-
-\end{itemize}
-\item Hence, variable selection can be done by producing \textcolor{red}{sparse} estimator of coefficients.
-\end{itemize}
-
-\end{frame}
-\begin{frame}{High-dimensional linear regression models}
-\begin{itemize}\itemsep=5mm
-\item Define
-\begin{eqnarray*}
-\left[\begin{array}{c|cccc}
-y_1& x_{11} & x_{12}&\cdots & x_{1p}  \\
-y_2& x_{21} & x_{22}&\cdots & x_{2p} \\
-\vdots& \vdots & \vdots&\ddots & \vdots \\
-y_n& x_{n1} & x_{n2}&\cdots & x_{np} \\
-\end{array}\right]=\left[\begin{array}{c|cccc}
-\uy& \ux_{1} & \ux_{2}&\cdots & \ux_{p}  \\
-\end{array}\right]
+ \ubeta_{\bg}|\sigma^2,\bg &\sim&\text{Normal}(0,\tau \sigma^2 \uI_{|\bg|} ),\\
+ \sigma^2 &\sim& \text{Inverse-Gamma}(a_{\sigma}/2,b_{\sigma}/2),\\
+ \pi(\bg) &\propto& \mathbb{I}(|\bg|=k),
 \end{eqnarray*}
-\item Consider 
-$$ \uy=\uX\ubeta +\uepsilon,$$
-where $\uX=(\ux_1,\ldots,\ux_p)$, $\ubeta=(\beta_1,\ldots, \beta_p)^\T$, and $\uepsilon \sim N(0,\sigma^2 I_n)$.
- \item Assume that $p>n$.
- \item Our aim is to obtain a sparse estimator for $\ubeta$.
+where $|\bg|$ is number of elements in $\bg$.
 \end{itemize}
@@
 
-\begin{frame}{Sparse estimation with $L_0$-penalty}
-\begin{itemize}\itemsep=6mm
+\begin{frame}{Priors and marginal posterior distribution }
+\begin{itemize}\itemsep=5mm
 
- \item The sparse  estimator can be obtained by minimizing 
- $$ \|\uy-\uX\ubeta\|^2 +\lambda \|\ubeta\|_0,$$
- where $\|\ubeta\|_0=\sum_{j=1}^p \mathbb{I}(\beta_j\neq 0)$ and $\lambda \geq 0$ controls degrees of sparsity.
- \item e.g., $\lambda=2$ (AIC), $\lambda=\log n$ (BIC), $\lambda =\log p $ (RIC), \ldots
- \pause \item However, the use of $L_0$-penalty leads to a \textcolor{red}{non-convex optimization} problem, which is computationally intractable in high-dimensional settings.
+\item Given $k$, it can be shown that 
+\begin{eqnarray*}
+\pi(\bg|\uy)&\propto&  \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
+ \uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
+ \uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } }\mathbb{I}(|\bg|=k)\\
+ &\equiv& {\color{red}{g(\bg)}}\mathbb{I}(|\bg|=k),
+ \end{eqnarray*}
+  where $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$.
+\item Hence, ${\color{red}{\Large g(\bg)}}$ is our {\color{red}{model selection criterion}}.
+
 \end{itemize}
@@
 
-\begin{frame}{Sparse estimation with convex penalties}
+\begin{frame}{Best subset selection Algorithm}
 \begin{itemize}\itemsep=5mm
-\item Many convex penalty functions have been proposed. 
-\\e.g., lasso, adaptive lasso, elastic net, MCP, ... 
-\item The lasso estimator \citep{tibshirani1996regression} can be obtained by minimizing 
- $$ \|\uy-\uX\ubeta\|^2 +\lambda \|\ubeta\|_1,$$
- where $\|\ubeta\|_1=\sum_{j=1}^p |\beta_j|$.
-\pause \item However, optimal $\lambda$ selection is required. (CV, GCV, BIC, ...)
+\item Note that our {\color{red}{goals}} are to obtain {\color{red}{(i)}} $k$ most important predictors out of $\binom{p}{k}$ models; {\color{red}{(ii)}} a single best model from among $2^p$ candidate models.
 
- \item In addition, convex penalties generate the shrinkage bias on the resulting estimator of $\ubeta$. 
+\item Hence, this can be fallen into the description of {\color{red}{best subset selection}} as follows:
+\end{itemize}
+\begin{itemize}\itemsep=5mm
+\pause
+\item[(i)] Fixed size: for $k = 1,2,\ldots,p$,  select the best subset model by
+  $$\mathcal{M}_k = \arg_{\bg}\max_{|\bg|=k}g(\bg)$$
+from $\binom{p}{k}$ candidate models.
+\item [(ii)] Varying size: Pick the single best model from $\mathcal{M}_1,\ldots,\mathcal{M}_p$.
+\pause \item Challenge of best subset selection:\\
+e.g. (i) $p=1000,k=5$, {\color{red}{$\binom{1000}{5}\approx8\times 10^{12}$}}; (ii) $p=40$, {\color{red}{$2^{40}\approx 10^{12}$}}.
 \end{itemize}
 \end{frame}
-\begin{frame}{$L_0$-penalty vs Convex penalties} 
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrr}
-  \hline
- &$L_0$-penalty & Convex penalties \\ 
-  \hline
-Computation & \textcolor{red}{hard} &easy \\
-Bias & unbiased & \textcolor{red}{biased} \\
-$\lambda$ selection & easy & \textcolor{red}{hard} \\
-$var(\hat{\beta})$& available& \textcolor{red}{mostly n/a} \\
-   \hline
-\end{tabular}
-\end{table}
-\vspace{5mm}
+\begin{frame}{Neighborhood Search}
 \begin{itemize}
- \item We propose a Bayesian method to overcome challenges in non-convex optimization.
+\item To avoid the exhaustive computation, we resort to the idea of {\color{red}{Neighborhood Search}} proposed by \citet{Madigan1995} and \citet{hans2007}.
+\item Let $\bg^{(t)}$ be a current state of $\bg$, $|\bg^{(t)}|=k$ is model size.
+\item {\color{red}{Addition}} neighbor: $\mathcal{N}_{{\color{red}{\boldsymbol{+}}}} (\bg^{(t)})=\{\bg^{(t)} \cup \{j\}: j\notin \bg^{(t)}\}$; {\color{red}{model size?}} \\ \vspace{3mm}
+\item {\color{red}{Deletion}} neighbor: $\mathcal{N}_{{\color{red}{\boldsymbol{-}}}}(\bg^{(t)})=\{\bg^{(t)} \setminus \{j'\}: j'\in \bg^{(t)}\}$; {\color{red}{model size?}}\vspace{3mm}
+
+\item e.g. Suppose $p=4,k=2$. Let $\bg^{(t)} =\{1,2\}$, then
+\begin{eqnarray*}
+\mathcal{N}_+(\bg^{(t)}) &=& \{\{1,2,3\},\{1,2,4\}\},\\
+\mathcal{N}_-(\bg^{(t)})&=& \{\{1\},\{2\}\}.
+\end{eqnarray*}
+\end{itemize}
+\end{frame}
+\begin{frame}{Hybrid best subset search with a fixed $k$}
+
+\begin{itemize}\itemsep=2mm
+  \item  Note our {\color{red}{Goal (i)}} is to find  $\hat\bg = \arg_{\bg}\max_{|\hat\bg|=k}g(\bg)$. 
+  \item[1.] Initialize $\hat{\bg}$ s.t. $|\hat{\bg}|=k$.
+  \item[2.] \textbf{Repeat} \quad  \texttt{\textcolor{blue}{\#deterministic search:local optimum}}
+        \begin{itemize}\itemsep=2mm
+         \item[] Update $\tilde{\bg }\leftarrow \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg} ) } g(\bg)$ ;\quad  \texttt{\textcolor{blue}{\# $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{j\}: j\notin \hat{\bg} \}$}}
+         \item[] Update $\hat{\bg}\leftarrow  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg} ) } g(\bg);$ \quad \texttt{\textcolor{blue}{\# $\mathcal{N}_-(\tilde{\bg })= \{\tilde{\bg } \setminus \{j\}: j\in \tilde{\bg } \}$}}
+        \end{itemize}
+  \item[] \textbf{until} convergence.
+  \pause
+\item In Step 2, we have $p+1$ many candidate models in all $\bg \in \mathcal{N}_+(\hat{\bg})$ and all $\bg \in \mathcal{N}_-(\tilde{\bg}))$ in each iteration.
+\item compute $g(\bg)$ $p+1$ times in each iteration. 
 \end{itemize}
@@
 
-\begin{frame}{Reduced models}
-\begin{itemize}\itemsep=5mm
-\item Let $\bg$ be an index set, $\bg \subset \{1,\ldots,p\}$.
-\item Let $\uX_{\bg}$ be a sub-matrix of $\uX$ containing $\ux_j$ $j\in \bg$.\\
-e.g. $\bg=\{1,2,3\} \Rightarrow \uX_{\bg}=(\ux_1,\ux_2,\ux_3)$.
-\item Given $\bg$, our model reduces to
+\begin{frame}{1st Key features of proposed algorithm}
 \begin{eqnarray*}
- \uy = \uX_{\bg} \ubeta_{\bg} + \uepsilon,
+g(\bg)=\frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{{\color{red}{|\uX_{\bg}^{\T}
+ \uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}}}  \left(\uy^{\T}\uH_{\bg}
+ \uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}}},
 \end{eqnarray*}
-where $\ubeta_{\bg}$ is a sub-vector of $\ubeta$ corresponding to $\bg$. 
+where $\uH_{\bg} = \uI_n-\uX_{\bg}{\color{red}{(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}}}\uX_{\bg}^{\T}$.
+\begin{itemize}
+\item compute inverse matrix and determinant $p+1$ times. 
+\item We propose the following formula and we can show that evaluating all candidate models in addition neighbor can be done \textcolor{red}{simultaneously} in this single computation. 
+\begin{eqnarray}
+\nonumber \ug({\mathcal{N}_+({\hat\bg})})&=& \left\{(\uy^{\T}\uH_{\hat{\bg}}\uy+b_{\sigma}) \1_p-\frac{(\uX^{\T}\uH_{\hat{\bg}}\uy)^2}{\tau^{-1}\1_p+\diag(\uX^{\T}\uH_{\hat{\bg}}\uX) } \right\}^
+ {-\frac{a_{\sigma}+n}{2}}\times\\
+ &&\left\{\tau^{-1} \1_p  +\diag(\uX^{\T}\uH_{\hat{\bg}}\uX) \right\}^{-1/2},
+ \end{eqnarray}
+ \item Similarly for $\ug({\mathcal{N}_-({\hat\bg})})$.
+\end{itemize}
+\end{frame}
+\begin{frame}{Hybrid best subset search with a fixed $k$}
+\begin{itemize}
+  \item  Note our {\color{red}{Goal (i)}} is to find  $\hat\bg = \arg_{\bg}\max_{|\hat\bg|=k}g(\bg)$. 
+  \item[1.] Initialize $\hat{\bg}$ s.t. $|\hat{\bg}|=k$.
+  \item[2.] \textbf{Repeat} \quad  \texttt{\textcolor{blue}{\#deterministic search:local optimum}}
+        \begin{itemize}\itemsep=2mm
+         \item[] Update $\tilde{\bg }\leftarrow \arg\max \ug(\mathcal{N}_+(\hat{\bg} ) )$ ;\quad  \texttt{\textcolor{blue}{\# $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{j\}: j\notin \hat{\bg} \}$}}
+         \item[] Update $\hat{\bg}\leftarrow  \arg\max \ug( \mathcal{N}_-(\tilde{\bg} ) );$ \quad \texttt{\textcolor{blue}{\# $\mathcal{N}_-(\tilde{\bg })= \{\tilde{\bg } \setminus \{j\}: j\in \tilde{\bg } \}$}}
+        \end{itemize}
+  \item[] \textbf{until} convergence.
+ \pause \item[3.] Set $\bg^{(0)}=\hat{\bg}$.
+  \item[4.] \textbf{Repeat} for $t=1,\ldots,T$:  \quad  \texttt{\textcolor{blue}{\#stochastic search:global optimum}}
+        \begin{itemize}\itemsep=2mm
+         \item[] Sample $\bg^{*} \sim\pi (\bg |\uy)=\frac{\{g(\bg)\}}{\sum_{\bg}\{g(\bg)\}}\mathbb{I}\{\bg\in \mathcal{N}_+({\bg^{(t-1)}} ) \}$; 
+         \item[] Sample $\bg^{(t)}\sim \pi (\bg |\uy)=\frac{\{g(\bg)\}}{\sum_{\bg}\{g(\bg)\}} \mathbb{I}\{\bg\in \mathcal{N}_-({\bg^{*}} ) \}$;
+         \item[] \textbf{If} $\pi(\hat{\bg} |\uy)<\pi({\bg}^{(t)} |\uy)$, \textbf{then} update $\hat{\bg}=\bg^{(t)}$, break the loop, and go to 2.
+        \end{itemize}
+  \item[5.] Return $\hat{\bg}$.
+  \item Note that all $g(\bg)$ are computed simultaneously in their neighbor space. 
  \end{itemize}
@@
 
-\begin{frame}{Bayesian best subset selection}
-\begin{itemize}\itemsep=3mm
-\item Suppose that we are interested in finding a best subset of size $k$.
-\item In a Bayesian framework, best subset selection can be done by estimating $\bg$.
-\item The Bayesian estimator of $\bg $ is obtained by maximizing
-$$\pi(\bg | \uy) \propto \int f(\uy |\ubeta_\bg ,\bg,\sigma^2)\pi(\ubeta_\bg ,\bg,\sigma^2) d (\ubeta_\bg, \sigma^2) , $$
- where $f(\uy |\ubeta_\bg ,\bg,\sigma^2)$ is the likelihood and $\pi(\ubeta_\bg ,\bg,\sigma^2)$ is the prior.
+\begin{frame}{2nd Key features of proposed algorithm}
+\begin{itemize}\itemsep=5mm
+\item To avoid staying in the local optimum for a long time in step 4, we use the {\color{red}{escort distribution}}.
+\item The idea of {\color{red}{escort distribution}} (used in statistical physics and thermodynamics) is introduced to stimulate the movement of Markov chain.
+\item An escort distribution of $g(\bg)$ is given as 
+$$  \frac{\{g(\bg)\}^\alpha}{\sum_{\bg}\{g(\bg)\}^\alpha}, \alpha\in[0,1]$$
 \end{itemize}
 \end{frame}
+\begin{frame}{Escort distributions}
+\begin{itemize}
 
-\begin{frame}{Prior specification \& posterior distribution}
-\begin{itemize}\itemsep=3mm
-\item For computational convenience, we consider
-\begin{eqnarray*}
- \ubeta_{\bg}|\sigma^2,\bg &\sim&\text{Normal}(0,\tau \sigma^2 \uI_{|\bg|} ),\\
- \sigma^2 &\sim& \text{Inverse-Gamma}(a_{\sigma}/2,b_{\sigma}/2),\\
- \pi(\bg)&\propto&\mathbb{I}(|\bg|=k ),
-\end{eqnarray*}
-where $|\bg|$ denotes the number of elements in $\bg$.
-\item Given $k$, it can be shown that 
-$$\pi(\bg|\uy)\propto  \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
- \uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
- \uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } } \mathbb{I}(|\bg|=k ),$$
- where $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$.
+\item e.g. Consider 3 candidate models with its probability: 
+\item If $\alpha=1,$
 \end{itemize}
-\end{frame}
-
-\begin{frame}{Stochastic search via MCMC}
-\begin{itemize}\itemsep=3mm
-\item A simplest way is to generate a random sample from $\pi(\bg|\uy)$:\\
-$$\bg^{(1)},\bg^{(2)},\ldots,\bg^{(T)} \overset{iid}{\sim} \pi(\bg|\uy) \quad \Rightarrow \quad  \hat{\bg}=\arg \max_{1\leq t\leq T}\pi(\bg^{(t)}|\uy),$$
- but this is impossible due to the complexity of $\pi(\bg|\uy)$.
-\item As an alternative, we can generate a Markov chain using Markov chain Monte Carlo (MCMC) computation.
-\item However, MCMC algorithms are too slow and often fail when $p$ is large.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Shotgun Stochastic Search (SSS)}
-\begin{itemize}\itemsep=3mm
-\item \citet{hans2007shotgun} propose SSS using the idea of parallel computation.
-\item Let $\bg^{(t)}$ be a current state of $\bg$ and $\hat{\bg}$ be a current best subset.
-\item Define a neighborhood of $\bg^{(t)}$ as
-$$\mathcal{N}(\bg^{(t)})=\{ \bg^{(t)} \}\cup \{\bg^{(t)} \cup \{j\}: j\notin \bg^{(t)}\}\cup \{\bg^{(t)} \setminus \{j'\}: j'\in \bg^{(t)}\}.$$
-\end{itemize}
-\end{frame}
-
-\begin{frame}{SSS algorithm}
-\begin{itemize}\itemsep=3mm
-\item Update $\hat{\bg}$ by iterating the following steps:
-\item[] \textcolor{blue}{Step1.} Compute $\pi(\bg|\uy)$ for each $\bg \in \mathcal{N}(\bg^{(t)})$ \textcolor{red}{in parallel} (parallel computing).
-\item[] \textcolor{blue}{Step2.} If $\pi(\hat{\bg}|\uy)< \max_{\bg \in \mathcal{N}(\bg^{(t)}) }\pi(\bg|\uy)$, then update $$\hat{\bg}= \arg\max_{\bg \in \mathcal{N}(\bg^{(t)}) }\pi(\bg|\uy)$$
-\item[] \textcolor{blue}{Step3.} Update $\bg^{(t+1)}$ by generating a sample from $ \mathcal{N}(\bg^{(t)})$ with probabilities proportional to $\pi(\bg|\uy)  \mathbb{I}\{\bg \in \mathcal{N}(\bg^{(t)})\}$.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Limitations of SSS}
-\begin{itemize}\itemsep=3mm
-\item When $k$ is fixed, SSS is not applicable.
-\item When parallel computing is not available, SSS is inefficient.
-\item Stochastic search algorithm requires a ``burn-in'' period.
-\end{itemize}
+$$\frac{\{g(\bg)\}^\alpha}{\sum_{\bg}\{g(\bg)\}^\alpha}=\begin{cases} 0.02\quad & \text{model 1} \\ 0.90~\quad &\text{model 2} \\0.08~\quad &\text{model 3} \end{cases}.$$
+\begin{figure}
+\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig1.pdf}
+\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig2.pdf}
+\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig3.pdf}
+\caption{Escort distributions of $\pi_\alpha (\bg |\uy)$.}
+\end{figure}
 \end{frame}
@@
 \begin{itemize}
+  \item  Note our {\color{red}{Goal (i)}} is to find  $\hat\bg = \arg_{\bg}\max_{|\hat\bg|=k}g(\bg)$. 
   \item[1.] Initialize $\hat{\bg}$ s.t. $|\hat{\bg}|=k$.
-  \item[2.] \textbf{Repeat} \quad  \texttt{\textcolor{blue}{\#deterministic search}}
+  \item[2.] \textbf{Repeat} \quad  \texttt{\textcolor{blue}{\#deterministic search:local optimum}}
         \begin{itemize}\itemsep=2mm
-         \item[] Update $\tilde{\bg }\leftarrow \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg} ) } \pi(\bg|\uy)$ ;\quad  \texttt{\textcolor{blue}{\# $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{j\}: j\notin \hat{\bg} \}$}}
-         \item[] Update $\hat{\bg}\leftarrow  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg} ) } \pi(\bg|\uy);$ \quad \texttt{\textcolor{blue}{\# $\mathcal{N}_-(\tilde{\bg })= \{\tilde{\bg } \setminus \{j\}: j\in \tilde{\bg } \}$}}
+         \item[] Update $\tilde{\bg }\leftarrow \arg\max \ug(\mathcal{N}_+(\hat{\bg} ) )$ ;\quad  \texttt{\textcolor{blue}{\# $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{j\}: j\notin \hat{\bg} \}$}}
+         \item[] Update $\hat{\bg}\leftarrow  \arg\max \ug( \mathcal{N}_-(\tilde{\bg} ) );$ \quad \texttt{\textcolor{blue}{\# $\mathcal{N}_-(\tilde{\bg })= \{\tilde{\bg } \setminus \{j\}: j\in \tilde{\bg } \}$}}
         \end{itemize}
+
   \item[] \textbf{until} convergence.
- \pause \item[3.] Set $\bg^{(0)}=\hat{\bg}$.
-  \item[4.] \textbf{Repeat} for $t=1,\ldots,T$:  \quad  \texttt{\textcolor{blue}{\#stochastic search}}
+ \item[3.] Set $\bg^{(0)}=\hat{\bg}$.
+  \item[4.] \textbf{Repeat} for $t=1,\ldots,T$:  \quad  \texttt{\textcolor{blue}{\#stochastic search:global optimum}}
         \begin{itemize}\itemsep=2mm
-         \item[] Generate $\bg^* \sim\pi_\alpha (\bg |\uy)\propto  \{\pi(\bg |\uy)\}^\alpha \mathbb{I}\{\bg\in \mathcal{N}_+({\bg^{(t-1)}} ) \}$;  \quad  \texttt{\textcolor{blue}{\# $\alpha \in [0,1]$}}
-         \item[] Generate $\bg^{(t)}\sim \pi_\alpha (\bg |\uy)\propto \{\pi(\bg |\uy)\}^\alpha \mathbb{I}\{\bg\in \mathcal{N}_-({\bg^{*}} ) \}$;
+         \item[] Sample $\bg^{*} \sim\pi_\alpha (\bg |\uy)={\color{red}{\frac{\{g(\bg)\}^\alpha}{\sum_{\bg}\{g(\bg)\}^\alpha}}}\mathbb{I}\{\bg\in \mathcal{N}_+({\bg^{(t-1)}} ) \}$;  \quad  \texttt{\textcolor{blue}{\# $\alpha \in [0,1]$}}
+         \item[] Sample $\bg^{(t)}\sim \pi_\alpha (\bg |\uy)={\color{red}{\frac{\{g(\bg)\}^\alpha}{\sum_{\bg}\{g(\bg)\}^\alpha}}} \mathbb{I}\{\bg\in \mathcal{N}_-({\bg^{*}} ) \}$;
          \item[] \textbf{If} $\pi(\hat{\bg} |\uy)<\pi({\bg}^{(t)} |\uy)$, \textbf{then} update $\hat{\bg}=\bg^{(t)}$, break the loop, and go to 2.
@@
   \item[5.] Return $\hat{\bg}$.
+  \item Note that all $g(\bg)$ are computed simultaneously in their neighbor space. 
  \end{itemize}
 \end{frame}
-
-\begin{frame}{Key features of proposed algorithm}
-\begin{itemize}\itemsep=5mm
-\item In Steps 2, computing $\pi(\bg|\uy)$ for all $\bg  \in \mathcal{N}_+(\hat{\bg} )$ (or all $\bg  \in \mathcal{N}_-(\tilde{\bg} ) )$ can be done \textcolor{red}{simultaneously} in a single computation.
-\item In Step 4, the idea of escort distribution (used in statistical physics and thermodynamics) is introduced to stimulate the movement of Markov chain.
-\item An escort distribution of $p(x)$ is given as 
-$$ p_\alpha(x)=\frac{\{p(x)\}^\alpha}{\sum_{x \in \mathcal{X} } \{p(x)\}^\alpha}.$$
-
-\end{itemize}
-\end{frame}
-\begin{frame}{Escort distributions}
-Let $$p(x)=\begin{cases} 0.1\quad &x=1 \\ 0.85~\quad &x=2 \\0.05~\quad &x=3 \end{cases}.$$
-\begin{figure}
-\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig1.pdf}
-\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig2.pdf}
-\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig3.pdf}
-\caption{Escort distributions of $p(x)$.}
-\end{figure}
-\end{frame}
-\begin{frame}{Best subset selection with unknown $k$}
-\begin{itemize}\itemsep=3mm
-\item We extend the proposed method to best subset selection with varying $k (<K)$, where $K$ is a pre-specified upper bound, $K<n$.
-\item In our Bayesian framework, this extension can be easily done by assigning a prior for $k$.
-\item Note that the uniform prior, $k \sim \text{Uniform}\{1,\ldots,K\}$, tends to assign larger probability to a larger subset. 
+\begin{frame}{Best subset selection with varying $k$}
+Note that {\color{red}{Goal (ii)}}: a single best model from among $2^p$ candidate models.
+\begin{itemize}\itemsep=8mm
+\item We extend "fixed" $k$ to varying $k$ by assigning a prior on $k$.
+\item Note that the uniform prior, $k \sim \text{Uniform}\{1,\ldots,K\}$, tends to assign larger probability to a larger subset (see \citet{chen2008extended}). 
 \item We define
@@
 \item Bayesian best subset selection can be done by maximizing
-$$ \pi(\bg,k|\uy) \propto f(\uy|\bg, k)\pi(\bg| k) \pi(k)$$
+\begin{eqnarray} 
+\pi(\bg,k|\uy) \propto {\color{red}{g(\bg)/\binom{p}{k}}}
+\end{eqnarray}
 over $(\bg,k)$.
@@
   \item[1.] \textbf{Repeat} for $k=1,\ldots,K$:
-        \begin{itemize}
-         \item[a.] Given $k$, implement the hybrid search algorithm.
-         \item[b.] Set $\hat{\bg}_k=\hat{\bg}$.
-        \end{itemize}
-  \item[2.] Find $\hat{\bg}_{k_*}$ such that $$ \log f(\uy|\hat{\bg}_{k_*},{k_*})-\log \binom{p}{{k_*}} \geq \log f(\uy|\hat{\bg}_k,k)-\log \binom{p}{k},\quad \text{any $k\leq K$}.$$
+
+ Given $k$, implement the hybrid search algorithm to obtain best subset model $\hat\bg_k$.
+
+  \item[2.] Find the best model $\hat\bg^*$ obtained by 
+\begin{eqnarray} 
+\hat\bg^*=\arg\max_{k\in\{1,\ldots,K \}}\left({\color{red}{g(\hat\bg_k)/\binom{p}{k}}}\right).
+\end{eqnarray}
 \end{itemize}
@@
 
-\begin{frame}{Connection to extended BIC}
-
-\begin{itemize}\itemsep=3mm
-\item It can be shown that our posterior criterion is asymptotically equivalent to the extended BIC (EBIC) of \citet{chen2008extended}.
-\item EBIC corresponds to the $L_0$-penalty sparse estimation with 
-$$\lambda = \log (n)+ \frac{2}{k}\log \binom{p}{k}.$$
+\begin{frame}{Consistency of model selection criterion}
+\begin{theorem}\label{thm:2} Let $\bg_*$ indicate the true model.
+Define $\Gamma=\{\bg:|\bg|\leq K,\bg\neq \bg_*\}$.
+Assume that $p=O(n^\xi)$ for $\xi\geq 1$.
+Under the asymptotic identifiability condition of \citet{chen2008extended}, if $\tau\to \infty$ as $n\to \infty$ but $\tau=o(n)$, then the proposed Bayesian subset selection possesses the Bayesian model selection consistency, that is,
+\begin{eqnarray}\label{thm:2:eq}
+\pi(\bg_*|\uy) > \max_{ \bg \in \Gamma }\pi(\bg|\uy)
+\end{eqnarray}
+in probability as $n\to \infty$.
+\end{theorem}
+\begin{itemize}
+  \item As $n\to \infty$, the maximizer of $\pi(\bg|\uy)$ is the true model based on our model selection criterion.
 \end{itemize}
 \end{frame}
-
-\begin{frame}{Model selection consistency}
-
-\begin{itemize}\itemsep=3mm
-\item The proposed Bayesian approach possesses the model selection consistency in the high-dimensional setting with $p=p_n=O(n^\xi)$ for $\xi\geq 1$.
-\item Hence, as $n\to \infty$, our variable selection procedure identifies the true model with probability tending to one.
-\end{itemize}
-\end{frame}
-
 \begin{frame}{Simulation study}{Setup}
@@
  \centering 
- \caption{MC size=$2,000$; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance).}\label{T:sim1}
+ \caption{$2,000$ replications; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance).}\label{T:sim1}
  \begin{tabular}{cc|c|c|c|c}
@@
   \hline
-i           & Proposed & 0.006 (0.001)  & 96.900 (0.388)  & 4.032 (0.004)    & 0.032 (0.004) \\
-           & SCAD                           & 0.034 (0.002)  & 85.200 (0.794)  & 4.188 (0.011)   & 0.188 (0.011) \\
+$p=200$ & {\color{red}{Proposed}} & 0.006 (0.001)  & 96.900 (0.388)  & 4.032 (0.004)    & 0.032 (0.004) \\
+$\&\rho=0.1$& SCAD                           & 0.034 (0.002)  & 85.200 (0.794)  & 4.188 (0.011)   & 0.188 (0.011) \\
            & MCP                            & 0.035 (0.002)  & 84.750 (0.804)  & 4.191 (0.011)   & 0.191 (0.011) \\
@@
   \hline
-ii           & Proposed & 0.023  (0.002) & 88.750  (0.707) & 3.985 (0.006)  & 0.203 (0.014) \\
-           & SCAD                           & 0.059 (0.003)  & 74.150 (0.979)  & 4.107 (0.015)   & 0.480 (0.022) \\
+$p=200$           & {\color{red}{Proposed}} & 0.023  (0.002) & 88.750  (0.707) & 3.985 (0.006)  & 0.203 (0.014) \\
+$\&\rho=0.9$ & SCAD                           & 0.059 (0.003)  & 74.150 (0.979)  & 4.107 (0.015)   & 0.480 (0.022) \\
            & MCP                            & 0.137 (0.004)  & 55.400 (1.112)  & 4.264 (0.020)   & 1.098 (0.034) \\
@@
  \centering 
- \caption{MC size=$2,000$; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance).}\label{T:sim2}
+ \caption{$2,000$ replications; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance).}\label{T:sim2}
  \begin{tabular}{cc|c|c|c|c}
@@
   \hline
-   iii        & Proposed & 0.004 (0.001)   & 98.100 (0.305)  & 4.020 (0.003)    & 0.020 (0.003) \\
-           & SCAD                           & 0.027 (0.002)  & 87.900 (0.729)  & 4.145 (0.010)   & 0.145 (0.010) \\
+   $p=1000$        & {\color{red}{Proposed}} & 0.004 (0.001)   & 98.100 (0.305)  & 4.020 (0.003)    & 0.020 (0.003) \\
+   $\&\rho=0.1$& SCAD                           & 0.027 (0.002)  & 87.900 (0.729)  & 4.145 (0.010)   & 0.145 (0.010) \\
            & MCP                            & 0.031 (0.002)  & 86.550 (0.763)  & 4.172 (0.013)   & 0.172 (0.013) \\
@@
   \hline
-    iv       & Proposed & 0.023(0.002)   & 89.850 (0.675)  & 4.005 (0.005) & 0.190 (0.013) \\
-           & SCAD                           & 0.068 (0.003)  & 74.250 (0.978)  & 4.196 (0.014)   & 0.493 (0.023) \\
+    $p=1000$       & {\color{red}{Proposed}} & 0.023(0.002)   & 89.850 (0.675)  & 4.005 (0.005) & 0.190 (0.013) \\
+    $\&\rho=0.9$& SCAD                           & 0.068 (0.003)  & 74.250 (0.978)  & 4.196 (0.014)   & 0.493 (0.023) \\
            & MCP                            & 0.152 (0.004)  & 53.750 (1.115)  & 4.226 (0.017)   & 1.202 (0.035) \\
@@
 \item We apply the proposed method to Breast Invasive Carcinoma (BRCA) data generated by The Cancer Genome Atlas (TCGA) Research Network \url{http://cancergenome.nih.gov}. 
-\item The data set is available at the \texttt{R} package \texttt{curatedTCGAData}. 
 \item The data set contains $17,814$ gene expression measurements (recorded on the log scale) of $526$ patients with primary solid tumor. 
-\item BRCA1 is a tumor suppressor gene and its mutations predispose women to breast cancer \citep{findlay2018accurate}. 
-\item Our goal here is to identify the best fitting model for estimating an association between BRCA1 (response variable) and the other genes (independent variables).
+\item {\color{red}{BRCA1}} is a tumor suppressor gene and its mutations predispose women to breast cancer \citep{findlay2018accurate}.
 
@@
 \begin{frame}{Real data application}{Results (based on $4,000$ genes)}
+\begin{itemize}
+\item Our {\color{red}{goal}} here is to identify the best fitting model for estimating an association between BRCA1 (response variable) and the other genes (independent variables).
+
+$$\text{BRCA1} = \beta_1*\text{NBR2} + \beta_2*\text{DTL} + \ldots + \beta_p*\text{VPS25}+\uepsilon.$$
+\item Results: 
+\end{itemize}
 \begin{table}[ht]
@@
   \hline
-  Proposed & 8 & 0.60      & 984.45  & 1099.50 \\
+  {\color{red}{Proposed}} & 8 & 0.60      & 984.45  & 1099.50 \\
   SCAD     & 4 & 0.68      & 1104.69 & 1166.47 \\
@@
  \includegraphics[width=0.6\textwidth,height=0.55\textwidth]{Heatmap.pdf}
- \caption{Except C10orf76, 7 genes are documented as \emph{diseases-related genes} }
+ \caption{Except C10orf76, {\color{red}{7 genes}} are documented as {\color{red}{diseases-related genes}}}
 \end{figure}
@@
 
-\bibitem[\protect\citeauthoryear{Tibshirani}{Tibshirani}{1996}]{tibshirani1996regression}
-Tibshirani, R. (1996).
-\newblock Regression shrinkage and selection via the lasso.
-\newblock {\em Journal of the Royal Statistical Society. Series B
-  (Methodological)\/}, 267--288.
+%\bibitem[\protect\citeauthoryear{Tibshirani}{Tibshirani}{1996}]{tibshirani1996regression}
+%Tibshirani, R. (1996).
+%\newblock Regression shrinkage and selection via the lasso.
+%\newblock {\em Journal of the Royal Statistical Society. Series B
+%  (Methodological)\/}, 267--288.
 
-\bibitem[\protect\citeauthoryear{Hans, Dobra, and West}{Hans
-  et~al.}{2007}]{hans2007shotgun}
+\bibitem[\protect\citeauthoryear{Hans, Dobra, and West}{Hans et~al.}{2007}]{hans2007}
 Hans, C., A.~Dobra, and M.~West (2007).
@@
 
+\bibitem[\protect\citeauthoryear{Madigan, David, Jeremy York, and Denis Allard}{Madigan et~al.}{1995}]{Madigan1995}
+Madigan, David, Jeremy York, and Denis Allard (1995).
+\newblock Bayesian Graphical Models for Discrete Data.
+\newblock {\em  International Statistical Review / Revue Internationale De Statistique\/}~{\em 63\/}(2), 215-232.
+
 \end{thebibliography}
@@
 
-\begin{frame}{Q/A}\vspace{2mm}
+\begin{frame}{Contact: \url{jinsq@ksu.edu}}
+\vspace{2mm}
 \centering \huge THANK YOU

### 2020-02-07 Rcode/BRCA_analysis.R

@@ -1,512 +1,0 @@
-library(MASS)
-library(invgamma)
-library(mvtnorm)
-library(xtable)
-library(ggplot2)
-library(reshape2)
-library(glmnet)
-library(ncvreg)
-rm(list=ls())
-###################
-# Data processing #
-###################
-# load('~/Dropbox/Goh/BRCA.RData')
-load('~/BRCA.RData')
-## data processing
-BRCA.stu <- scale(BRCA,center = TRUE, scale = TRUE)
-name.genes <- colnames(BRCA)
-ham.genes <- c('BRCA2','NBR1','NBR2','XRCC2',
-               'ATM','CHEK2','BRIP1','PALB2','RAD51C',
-               'CDH1','TP53','LDLRAD1', 'SLC19A1', 
-               'FGFBP3', 'CASP5', 'MMAB', 'SLC16A6',
-               'NBS1','RAD50','RAD51D','BARD1',
-               'CASP8', 'CTLA4', 'CYP19A1', 'FGFR2',
-               'H19', 'LSP1', 'MAP3K1', 'MRE11A',
-               'NBN', 'RAD51','TERT','MSH6','PMS2',
-               'SEC23B','NF1')
-BRCA1 <- which(name.genes=='BRCA1')
-y1 <- BRCA.stu[,BRCA1]
-X0 <- BRCA.stu[,-BRCA1]
-name.genes <- name.genes[-BRCA1] # update symbols of genes. 
-mcsize = 1000
-p=5000
-abs.cor <- abs(cor(y1,X0))
-g=sort(abs.cor,decreasing = TRUE)[p]
-X1 <- X0[,which(abs.cor>=g)]
-name.genes.X1 <- colnames(X1)
-sum(ham.genes%in%name.genes.X1)
-n = length(y1)
-k0 <- ceiling(n^(2/3))
-rep0 <- rep(0,p)
-seq.p <- c(1:p)
-I_n <- diag(1,n)
-a.sigma = b.sigma = 1
-G1.FNVS <- list()
-G1.hy <- list()
-tau = (log(p))^2
-beta.ini= as.numeric(cor(y1,X1))/diag(var(X1))
-marginal.FNVS <- rep(NA,k0)
-marginal.hy <- rep(NA,k0)
-G1.hy <- list()
-tXX <-  crossprod(X1)
-d.tXX<-diag(tXX)
-sum.y2<-sum(y1^2)
[…]

### 2020-02-07 Rcode/Jin/realdata/BRCA_analysis.R

@@ -1,0 +1,519 @@
+library(MASS)
+library(invgamma)
+library(mvtnorm)
+library(xtable)
+library(ggplot2)
+library(reshape2)
+library(glmnet)
+library(ncvreg)
+rm(list=ls())
+###################
+# Data processing #
+###################
+# load('~/Dropbox/Goh/BRCA.RData')
+load('~/BRCA.RData')
+## data processing
+BRCA.stu <- scale(BRCA,center = TRUE, scale = TRUE)
+name.genes <- colnames(BRCA)
+ham.genes <- c('BRCA2','NBR1','NBR2','XRCC2',
+               'ATM','CHEK2','BRIP1','PALB2','RAD51C',
+               'CDH1','TP53','LDLRAD1', 'SLC19A1', 
+               'FGFBP3', 'CASP5', 'MMAB', 'SLC16A6',
+               'NBS1','RAD50','RAD51D','BARD1',
+               'CASP8', 'CTLA4', 'CYP19A1', 'FGFR2',
+               'H19', 'LSP1', 'MAP3K1', 'MRE11A',
+               'NBN', 'RAD51','TERT','MSH6','PMS2',
+               'SEC23B','NF1')
+BRCA1 <- which(name.genes=='BRCA1')
+y1 <- BRCA.stu[,BRCA1]
+X0 <- BRCA.stu[,-BRCA1]
+name.genes <- name.genes[-BRCA1] # update symbols of genes. 
+mcsize = 1000
+p = 17326 # 5000
+abs.cor <- abs(cor(y1,X0))
+g=sort(abs.cor,decreasing = TRUE)[p]
+X1 <- X0[,which(abs.cor>=g)]
+name.genes.X1 <- colnames(X1)
+sum(ham.genes%in%name.genes.X1)
+n = length(y1)
+k0 <- ceiling(n^(2/3))
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+a.sigma = b.sigma = 1
+G1.FNVS <- list()
+G1.hy <- list()
+tau = (log(p))^2
+beta.ini= as.numeric(cor(y1,X1))
+marginal.FNVS <- rep(NA,k0)
+marginal.hy <- rep(NA,k0)
+G1.hy <- list()
+tXX <-  crossprod(X1)
+d.tXX<-diag(tXX)
+sum.y2<-sum(y1^2)
+tXy<-t(X1)%*%y1
+for (k in 1:k0) { #For loop for k<=k0
+  #k<-1
[…]

### 2020-02-07 Slide_Goh/escort.R

@@ -1,0 +1,23 @@
+p
+P_alpha<-p^10/sum(p^10)
+pdf("D:/Dropbox/Shiqiang_share/Project1/manuscript/v9-Goh/escort_fig1.pdf")
+a<-1
+P_alpha<-p^a/sum(p^a)
+names(P_alpha)<-c(1,2,3)
+barplot(P_alpha,ylim=c(0,1), ylab="Escort probability")
+legend("topright",expression(paste(alpha,"=1")))
+dev.off()
+a<-0.5
+pdf("D:/Dropbox/Shiqiang_share/Project1/manuscript/v9-Goh/escort_fig2.pdf")
+P_alpha<-p^a/sum(p^a)
+names(P_alpha)<-c(1,2,3)
+barplot(P_alpha,ylim=c(0,1), ylab="Escort probability")
+legend("topright",expression(paste(alpha,"=0.5")))
+dev.off()
+a<-0.1
+pdf("D:/Dropbox/Shiqiang_share/Project1/manuscript/v9-Goh/escort_fig3.pdf")
+P_alpha<-p^a/sum(p^a)
+names(P_alpha)<-c(1,2,3)
+barplot(P_alpha,ylim=c(0,1), ylab="Escort probability")
+legend("topright",expression(paste(alpha,"=0.1")))
+dev.off()

### 2020-02-07 Slide_JSM2019/escort.R

@@ -1,0 +1,27 @@
+setwd("/home/jin/Dropbox/Goh/Project_1/Slide_Jin")
+p=c(0.02,0.9,0.08)
+P_alpha<-p^10/sum(p^10)
+pdf("escort_fig1.pdf")
+a<-1
+P_alpha<-round(p^a/sum(p^a),2)
+names(P_alpha)<-c(1,2,3)
+bar1=barplot(P_alpha,ylim=c(0,1), ylab="Escort probability",cex.axis = 2.5, cex.lab=1.5,cex.names=3)
+legend("topright",expression(paste(alpha,"=1")),cex=4,box.col = 'transparent')
+text(x = bar1, y = P_alpha, label = P_alpha, pos = 3, cex = 2, col = "red")
+dev.off()
+a<-0.5
+pdf("escort_fig2.pdf")
+P_alpha<-round(p^a/sum(p^a),2)
+names(P_alpha)<-c(1,2,3)
+bar2=barplot(P_alpha,ylim=c(0,1), ylab="Escort probability",cex.axis = 2.5, cex.lab=1.5,cex.names=3)
+legend("topright",expression(paste(alpha,"=0.5")),cex=4,box.col = 'transparent')
+text(x = bar2, y = P_alpha, label = P_alpha, pos = 3, cex = 2, col = "red")
+dev.off()
+a<-0.05
+pdf("escort_fig3.pdf")
+P_alpha<-round(p^a/sum(p^a),2)
+names(P_alpha)<-c(1,2,3)
+bar3 = barplot(P_alpha,ylim=c(0,1), ylab="Escort probability",cex.axis = 2.5, cex.lab=1.5,cex.names=3)
+legend("topright",expression(paste(alpha,"=0.05")),cex=4,box.col = 'transparent')
+text(x = bar3, y = P_alpha, label = P_alpha, pos = 3, cex = 2, col = "red")
+dev.off()

### 2020-02-09 Manuscript/computational statistics/major_revision_1/BayesSubset_SC.tex
additional simulation, modeling setting,  Sig2_y <- 1 + 0.5*sqrt(abs(X1[,1])), and Sig <- riwish(p+p,(p-1)*Psi) #​ mean is Psi and variance of Sig is small.

@@
 \newcommand{\uSigma}{{\boldsymbol \Sigma}} %
+\newcommand{\uPsi}{{\boldsymbol \Psi}}
 \newcommand{\diag}{{\rm diag}} %
@@
 In this section, we investigate the variable selection performance of our best subset selection algorithm on simulated high-dimensional data.
-For $n=100$, we generate the data $\{(y_i,x_{i1},\ldots,x_{ip}):i=1,\ldots,n\}$ from the following linear regression model:
+We consider two cases.
+In case I, for $n=100$, we generate the data $\{(y_i,x_{i1},\ldots,x_{ip}):i=1,\ldots,n\}$ from the following linear regression model:
 \begin{eqnarray*}
-y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},\sigma^2_y\right),
+	y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},1\right),
 \end{eqnarray*}
-where $(x_{i1},\ldots,x_{ip})$ follows $\text{Normal}(\0_p,\uV)$ with $\uV=(v_{ij})_{p\times p}$ and $v_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$, and $\sigma^2_y$ is variance of error item.
+where $(x_{i1},\ldots,x_{ip})^\T \overset{iid}{\sim}\text{Normal}(\0_p,\uSigma)$ with $\uSigma=(\Sigma_{ij})_{p\times p}$ and $\Sigma_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$.
+In case II, for $n=100$, we generate the data $\{(y_i,x_{i1},\ldots,x_{ip}):i=1,\ldots,n\}$ from the following linear regression model:
+\begin{eqnarray*}
+	y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},\sigma^2_{y}\right),
+\end{eqnarray*}
+where $\sigma^2_{y_i} = 1+0.01\sqrt{x_{i1}}$, $(x_{i1},\ldots,x_{ip})^\T \overset{iid}{\sim}\text{Normal}(\0_p,\uSigma)$ with $\uSigma\sim \mathcal{IW}(\uPsi, p+2)$, $\uPsi,=(\psi_{ij})_{p\times p}$ and $\psi_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$.
 
-We consider four different cases: 
-\begin{itemize}
-	\item [(i)] $p=200$, $\rho=0.1$, $\sigma^2_y = 1$,
-	\item [(ii)] $p=200$, $\rho=0.9$, $\sigma^2_y = 1$,
-	\item [(iii)] $p=1000$, $\rho=0.1$, $\sigma^2_y = 1$,
-	\item [(iv)] $p=1000$, $\rho=0.9$, $\sigma^2_y = 1$,
-	\item [(v)] $p=200$, $\rho=0.1$, $\sigma^2_y = 2$,
-	\item [(vi)] $p=200$, $\rho=0.9$, $\sigma^2_y = 2$,
-	\item [(vii)] $p=1000$, $\rho=0.1$, $\sigma^2_y = 2$,
-	\item [(viii)] $p=1000$, $\rho=0.9$, $\sigma^2_y = 2$.
-\end{itemize}
+For both cases, we consider four different scenarios: (i) $p=200$, $\rho=0.1$, (ii) $p=200$, $\rho=0.9$, (iii) $p=1000$, $\rho=0.1$, and (iv) $p=1000$, $\rho=0.9$.
 We assume that there is no prior information.

### 2020-02-09 Rcode/Jin/Proposed methods_sim1.R

@@ -1,0 +1,284 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+library(MCMCpack)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-200
+rho0 <- 0.1
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Psi<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+g.tau <- function(tau0) {
+  SVD <- svd(X.r.star)
+  d.j <- as.vector(SVD$d)
+  z.j <- as.vector(t(SVD$u)%*%y1)
+  log.g.tau <- dim(X.r.star)[2]/2*log(tau0) + 0.5*sum(log(1/tau0+d.j^2)) + 
+    0.5*(a.sigma+n)*log(sum(y1^2)- sum((d.j*z.j)^2/(d.j^2+1/tau0))+b.sigma)
+  return(log.g.tau)
+}
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  Sig <- riwish(p+2, Psi)
+  diag(Sig) = 1
+  X1<-rmvnorm(n,rep(0,p),Sig,method="chol") #By Goh
+  Sig2_y <- 1 + sqrt(abs(X1[,1]))
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2_y))
+  ###############################
[…]

### 2020-02-09 Rcode/Jin/simulation/Proposed1.R

@@ -1,0 +1,316 @@
+library(mvtnorm)
+#library('latex2exp')
+library(xtable)
+library(invgamma)
+library(MCMCpack)
+rm(list=ls())
+##############
+## initial  ##
+## settings ##
+##############
+p<-200
+rho0 <- 0.9
+mcsize = 200
+REP<-2000
+n<-100
+rep0 <- rep(0,p)
+seq.p <- c(1:p)
+I_n <- diag(1,n)
+Psi<-rho0^(abs(matrix(1:p,p,p)-t(matrix(1:p,p,p))));
+k0<-ceiling(n^(2/3))
+a.sigma = b.sigma = 1
+##############
+## function ##
+##############
+
+################
+## simulation ##
+################
+G1.FNVS <- list()
+G1.hy <- list()
+FDR<-rep(0,REP)
+FOR<-rep(0,REP)
+t2 <- rep(NA,REP)
+n.var <- rep(0,REP)
+n.true <- rep(0,REP)
+hat.gamma <- matrix(0,p,REP)
+ham <- rep(0,REP)
+localvshy <- rep(0,REP)
+tau = (log(p))^2
+for(i in 1:REP){
+  #i=1
+  set.seed(1314+i)
+  beta.s <- sample(c(-2,-1,1,2), size = 4, prob = rep(0.25,4), replace = TRUE)
+  true.var <- sort(sample(seq.p,4))
+  beta = rep0
+  beta[true.var] = beta.s
+  false.var <- setdiff(seq.p,true.var)
+  gamma.true <- rep0
+  gamma.true[true.var] <- 1
+  Sig <- riwish(p+p,(p-1)*Psi)
+  X1<-rmvnorm(n,rep(0,p),sigma = Sig,method="chol") #By Goh
+  Sig2_y <- 1 + 0.5*sqrt(abs(X1[,1]))
+  max(Sig2_y)
+  y1<-as.numeric(X1%*%beta)+rnorm(n,mean=0,sd=sqrt(Sig2_y))
+  
+  # lm.sm <- summary(lm(y1~X1[,true.var]-1))
+  # plot(lm.sm$residuals,X1[,1])
+  ###############################
+  #Step 1: Set initial values
+  ###############################
+  beta.ini= as.numeric(cor(y1,X1))/diag(var(X1))
+  marginal.FNVS <- rep(NA,k0)
[…]
